### 2016-07-07 submission/manuscript.Rnw
Start Sweaving

\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{cite}
\usepackage{nameref,hyperref}
\usepackage[right]{lineno}
\usepackage{multirow}
\usepackage{adjustbox}
\usepackage[toc,page]{appendix}
\usepackage[table]{xcolor} 
\usepackage{pbox}

\bibliographystyle{../bibliography/plos2015}

\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

\providecommand{\keywords}[1]{\textbf{\textit{Keywords:}} #1}

% Leave date blank
% \date{}

\title{Too good to be false: Nonsignificant results revisited}
\author{CHJ Hartgerink\textsuperscript{1}, JM Wicherts\textsuperscript{1}, MALM van Assen\textsuperscript{1}\\ \\
\textsuperscript{1}Tilburg University, the Netherlands}

\begin{document}
\SweaveOpts{concordance=TRUE}
\maketitle

\begin{abstract}
Statistically significant research results in psychology have sometimes been considered "too good to be true", reflecting false positive findings. In this paper, we examine nonsignificant research results and whether they are "too good to be false", i.e., false negatives, which are also a threat to scientific progress. We inspected three applications of detecting false negatives. In Application 1, eight flagship psychological journals during 1985-2013 (30,710 papers) are investigated for false negatives. Across 54,595 nonsignificant statistical test results extracted with statcheck, evidence for false negatives was abound. We applied the Fisher test, which has high power to detect false negatives when there are at least three nonsignificant results and the population effect size is medium. All eight journals and 66.7\% of papers reporting nonsignificant results show evidence of at least one false negative. In Application 2, we manually investigated whether evidential value of (non)significant gender results depended on explicit expectations, but found that expectations are hardly clear in research results. Moreover, in Application 3, we reanalysed the nonsignificant replications from the Reproducibility Project Psychology and conclude that these nonsignificant results do not warrant conclusions about the validity of individual effects. We conclude from our findings that concern for statistical power and false negatives in psychological science is still warranted.
\end{abstract}

\keywords{nonsignificant, underpowered, effect size, Fisher test}
\newpage

<<Dependencies, echo=FALSE, print=FALSE>>=
# Running in Sweave or running the code in Rstudio project
# If you want to run in sweave, comment out the line with run <- ''
run <- '../'
# run <- ''

# Set the cran mirror
r <- getOption("repos")
r["CRAN"] <- "http://cran.cnr.berkeley.edu/"
options(repos = r)
# Download and load dependencies
if(!require(httr)){install.packages('httr')}
library(httr)
if(!require(latex2exp)){install.packages('latex2exp')}
library(latex2exp)
if(!require(plyr)){install.packages('plyr')}
library(plyr)
if(!require(ggplot2)){install.packages('ggplot2')}
library(ggplot2)
if(!require(stringr)){install.packages('stringr')}
library(stringr)
if(!require(car)){install.packages('car')}
library(car)
if(!require(xtable)){install.packages('xtable')}
library(xtable)

# custom functions
source(sprintf("%sfunctions/functions.R", run))
@

Popper’s \cite{Popper2005-xu} falsifiability serves as one of the main demarcating criteria in the social sciences, which stipulates that a hypothesis is required to have the possibility of being proven false to be considered scientific. Within the theoretical framework of scientific hypothesis testing, accepting or rejecting a hypothesis is unequivocal, because the hypothesis is either true or false. Statistical hypothesis testing, on the other hand, is a probabilistic operationalization of scientific hypothesis testing and, in lieu of its probabilistic nature, is subject to decision errors. Such decision errors are the topic of this paper.

Null Hypothesis Significance Testing (NHST) is the most prevalent paradigm for statistical hypothesis testing in the social sciences \cite{American_Psychological_Association2010-qe}. In NHST the hypothesis $H_0$ is tested, where $H_0$ most often regards the absence of an effect. If deemed false, an alternative, mutually exclusive hypothesis $H_1$ is accepted. These decisions are based on the $p$-value; the probability of the sample data, or more extreme data, given $H_0$ is true. If the $p$-value is smaller than the decision criterion (i.e., $\alpha$; typically .05 \cite{Nuijten2015-od}), $H_0$ is rejected and $H_1$ is accepted.

Table \ref{tab:tab1} summarizes the four possible situations that can occur in NHST. The columns indicate which hypothesis is true in the population and the rows indicate what is decided based on the sample data. When there is discordance between the true- and decided hypothesis, a decision error is made. More specifically, when $H_0$ is true in the population, but $H_1$ is accepted ('$H_1$'), a Type I error is made ($\alpha$); a false positive (lower left cell). When $H_1$ is true in the population and $H_0$ is accepted ('$H_0$'), a Type II error is made ($\beta$); a false negative (upper right cell). However, when the null hypothesis is true in the population and $H_0$ is accepted ('$H_0$'), this is a true negative (upper left cell; $1-\alpha$). The true negative rate is also called specificity of the test. Conversely, when the alternative hypothesis is true in the population and $H_1$ is accepted ('$H_1$'), this is a true positive (lower right cell). The probability of finding a positive if $H_1$ is true is the power ($1-\beta$), which is also called the sensitivity of the test. Power is a positive function of the population effect size, the sample size, and the alpha of the study, such that higher power can always be achieved by altering either the sample size or the alpha level \cite{Aberson2010-xa}.

\begin{table}[htbp]
% \rowcolors{2}{gray!25}{white}
\begin{adjustbox}{width=\textwidth,totalheight=\textheight,keepaspectratio,angle=0}
\centering
\begin{tabular}{llll}
&    & Population                        &                                    \\ \hline
&    & $H_0$                                & $H_1$                                 \\
Decision & '$H_0$' & $1-\alpha$                           & $\beta$                               \\
&    & True negative                     & False negative {[}Type II error{]} \\
& '$H_1$' & $\alpha$                             & $1-\beta$                             \\
&    & False positive {[}Type I error{]} & True positive                   \\  \hline
\end{tabular}
\end{adjustbox}
\caption{Summary table of possible NHST results. Columns indicate the true situation in the population, rows indicate the decision based on a statistical test. The true positive probability is called power and sensitivity, whereas the true negative rate is also called specificity.}
\label{tab:tab1}
\end{table}

Recent debate about false positives has overtaken science and psychological science in particular. The Reproducibility Project Psychology (RPP), which replicated 100 effects reported in prominent psychology journals in 2008, found that only 36\% of these effects were statistically significant in the replication \cite{Open_Science_Collaboration2015-zs}. Besides psychology, reproducibility problems have also been indicated in economics \cite{Camerer2016-zz} and medicine \cite{Begley2012-uc}. Although these studies provide substantial evidence of false positives in these fields, replications show considerable variability \cite{Klein2014-jb, Stanley2014-pd}, therefore caution is warranted when wishing to draw conclusions on the presence of an effect in individual studies \cite{Open_Science_Collaboration2015-zs,Gilbert2016-mi,Anderson2016-bv}.

The debate about false positives is driven by the current overemphasis on statistical significance of research results \cite{Giner-Sorolla2012-wn}. This overemphasis is substantiated by the finding that >90\% of results in the psychology literature are statistically significant \cite{Open_Science_Collaboration2015-zs,Sterling1995-fe,Sterling1959-pf} despite low power due to small sample sizes \cite{Cohen1962-jc,Sedlmeier1989-yc,Marszalek2011-rf,Bakker2012-tf}. Consequently, publications have become biased by overrepresenting statistically significant results \cite{Greenwald1975-ck}, which generally results in effect size overestimation in individual studies \cite{Nuijten2015-od} and in meta-analyses \cite{Van_Assen2015-gg}. The overemphasis on statistically significant effects has been accompanied by questionable research practices (QRPs, \cite{John2012-uj}) such as erroneously rounding p-values towards significance, which occurred for at least 13.81\% of all $p$-values reported as "$p =.05$" in articles from eight major psychology journals in the period 1985-2013 \cite{Hartgerink2016-mm}.

The concern for false positives has overshadowed the concern for false negatives in the recent debate, which seems unwarranted. Cohen \cite{Cohen1962-jc} was the first to indicate that psychological science was (severely) underpowered, which is defined as the chance of finding an effect in the sample is lower than 50\% when there is truly an effect in the population. This has not changed throughout the subsequent fifty years \cite{Bakker2012-tf,Fraley2014-xs}. In other words, the problem of false negatives has no empirical evidence of being resolved in psychology. Fiedler, Kutzner, and Krueger \cite{Fiedler2012-gx} worry that an increased focus on false positives is too shortsighted, arguing that false negatives are more difficult to detect than false positives. They also argue that, because of the focus on statistically significant results, negative results are less likely to be the subject of replications than positive results, decreasing the probability of detecting a false negative.

The research objective of the current paper is to examine evidence for false negative results in the published psychology literature. To this end, we inspected a large number of nonsignificant results from eight flagship psychology journals. First, we compared the observed effect distributions for eight journals (combined and separately) to the expected null distribution based on simulations, where a discrepancy between observed and expected distribution was anticipated (i.e., presence of false negatives). Second, we propose to use the Fisher test to test the hypothesis that $H_0$ is true for all nonsignificant results in a paper, which we show to have high power to detect false negatives in a simulation study. Third, we applied the Fisher test to the nonsignificant results in 14,765 psychology papers from these eight flagship psychology journals to inspect how many papers show evidence of at least one false negative result. Fourth, we examined evidence of false negatives in reported gender effects. Gender effects are particularly interesting, because gender is typically a control variable and not the primary focus of studies. Hence we expect little $p$-hacking and substantial evidence of false negatives in reported gender effects in psychology. Finally, as another application, we applied the Fisher test to the 64 nonsignificant results of the RPP \cite{Open_Science_Collaboration2015-zs} to examine whether at least one of these nonsignificant results may actually be a false negative.

\section*{Theoretical framework}

We begin by reviewing how individual- and sets of nonsignificant $p$-values are distributed. Subsequently, we propose a way to test whether a collection of nonsignificant results across papers deviates from what would be expected under $H_0$. We also propose a way to test whether nonsignificant results deviate from $H_0$ within a paper. These methods will be used to test whether and to what extent there is evidence for false negatives in the psychology literature.

\subsection*{Distributions of \textit{p}-values}

The distribution of one $p$-value is a function of the population effect, the observed effect and the precision of the estimate. When the population effect is zero, the probability distribution of one $p$-value is uniform. When there is an effect, the probability distribution is right-skewed. More specifically, as sample size or true effect size increases, the probability distribution of one $p$-value becomes increasingly right skewed. These regularities also generalize to a set of $p$-values, which are uniformly distributed when there is no population effect and right skew distributed when there is a population effect, with more right skew as the population effect and/or precision increases.

Considering that the present paper focuses on false negatives, we primarily examine nonsignificant $p$-values and their distribution. Since the test we apply requires random variables distributed between 0 and 1, we apply the following transformation to each  nonsignificant $p$-value
\begin{equation}
\label{pistar}
p^*_i=\frac{p_i-\alpha}{1-\alpha}
\end{equation}
where $p_i$ an untransformed nonsignificant $p$-value and $\alpha$ is the selected significance cutoff (i.e., $\alpha=.05$). This transformation retains the distributional properties of the original $p$-values for the selected nonsignificant results.

\subsection*{Testing for false negatives: the Fisher test}

We applied the Fisher test to inspect whether observed nonsignificant results deviate from those expected under $H_0$. The Fisher test was initially introduced as a meta-analytic technique to synthesize results across studies \cite{Fisher1925-jl,Hedges1985-dy}, but when applied to transformed nonsignificant $p$-values (see Equation \ref{pistar}) the Fisher test tests for evidence against $H_0$ in a set of nonsignificant results. In other words, the null we test with the Fisher test is that all included nonsignificant results are true negatives. The Fisher test statistic is calculated as
\begin{equation}
\label{fishertest}
\chi^2_{2k}=-2\sum\limits^k_{i=1}ln(p_i)
\end{equation}
where $k$ is the number of nonsignificant $p$-values and $\chi^2$ has $2k$ degrees of freedom. A larger $\chi^2$ value indicates more evidence for at least one false negative in the set of $p$-values. We conclude that there is sufficient evidence of at least one false negative result, if the Fisher test is statistically significant at $\alpha=.10$, similar to tests of publication bias that also use $\alpha=.10$ \cite{Sterne2000-wh,Ioannidis2007-hh,Francis2012-kw}.

We estimated the power of detecting false negatives with the Fisher test as a function of sample size $N$, correlation effect size $\eta$, and $k$ nonsignificant test results (procedure described in Appendix A). The 25th, 50th (median) and 75th percentiles of the degrees of freedom in eight flagship psychology journals (see Application 1 below) were taken to represent sample size, given their direct relation to sample size (e.g., for a two-group comparison including 100 people, df = 98). Table \ref{tab:tab2} summarizes results for the simulations of the Fisher test when the nonsignificant $p$-values are generated by either small- or medium population effect sizes. Results for all 5,400 conditions can be found on the OSF (\url{osf.io/qpfnw}). The results indicate that the Fisher test is a powerful method to test for a false negative among nonsignificant results when there are not only small effects investigated in small samples. For example, for small effect sizes ($\eta=.1$), 50, 25, 7 nonsignificant results are required to obtain a power of 69\%, 85\%, 83\% for sample sizes 33, 62, and 119, respectively. For medium effects ($\eta=.25$), small samples ($N=33$) and three nonsignificant results already provide 89\% power for detecting a false negative with the Fisher test. For large effects ($\eta=.4$), small samples and 2 nonsignificant results already detects all false negatives (based on the simulations).

% IF YOU WANT TO RERUN SIMULATIONS, SEE CODE CHUNK "SIMULATIONS" IN APPLICATION 1
% Sorry, made this table manually so have to check manually with files data/N_33.csv etc.
\begin{table}[htbp]
\rowcolors{2}{gray!25}{white}
\begin{adjustbox}{width=\textwidth,totalheight=\textheight,keepaspectratio,angle=0}
\centering
\begin{tabular}{llllllll}
&        & $\eta=.1$ (small) &         &  &        & $\eta=.25$ (medium) &         \\
& $N=33$ & $N=62$         & $N=119$ &  & $N=33$ & $N=62$           & $N=119$ \\
\hline
$k=1$  & 0.1512 & 0.211          & 0.341   &  & 0.5752 & 0.8516           & 0.9833  \\
$k=2$  & 0.1746 & 0.2667         & 0.4591  &  & 0.7793 & 0.9778           & 1       \\
$k=3$  & 0.2008 & 0.3167         & 0.5717  &  & 0.8935 & 1                & 1       \\
$k=4$  & 0.2077 & 0.352          & 0.6587  &  & 0.9482 & 1                & 1       \\
$k=5$  & 0.2287 & 0.3897         & 0.7194  &  & 0.9748 & 1                & 1       \\
$k=6$  & 0.251  & 0.4336         & 0.7842  &  & 0.9899 & 1                & 1       \\
$k=7$  & 0.2585 & 0.471          & 0.8336  &  & 0.9953 & 1                & 1       \\
$k=8$  & 0.2801 & 0.5136         & 0.8709  &  & 0.9979 & 1                & 1       \\
$k=9$  & 0.2984 & 0.5298         & 0.8945  &  & 1      & 1                & 1       \\
$k=10$ & 0.3035 & 0.5702         & 0.9178  &  & 1      & 1                & 1       \\
$k=15$ & 0.3624 & 0.6912         & 0.9798  &  & 1      & 1                & 1       \\
$k=20$ & 0.4291 & 0.7804         & 0.9958  &  & 1      & 1                & 1       \\
$k=25$ & 0.4898 & 0.852          & 0.9995  &  & 1      & 1                & 1       \\
$k=30$ & 0.5308 & 0.8936         & 1       &  & 1      & 1                & 1       \\
$k=35$ & 0.578  & 0.9303         & 1       &  & 1      & 1                & 1       \\
$k=40$ & 0.6214 & 0.953          & 1       &  & 1      & 1                & 1       \\
$k=45$ & 0.6538 & 0.9661         & 1       &  & 1      & 1                & 1       \\
$k=50$ & 0.6855 & 0.9762         & 1       &  & 1      & 1                & 1   \\
\hline
\end{tabular}
\end{adjustbox}
\caption{Power of Fisher test to detect false negatives for small- and medium effect sizes (i.e., $\eta=.1$ and $\eta=.25$), for different sample sizes (i.e., $N$) and number of test results (i.e., $k$). Results of each condition are based on 10,000 iterations. Power was rounded to 1 whenever it was larger than .995.}
\label{tab:tab2}
\end{table}

\section*{Application 1: Evidence of false negatives in articles across eight major psychology journals}

To show that statistically nonsignificant results do not warrant the interpretation that there is truly no effect, we analyzed statistically nonsignificant results from eight major psychology journals. First, we investigate to what degree nonsignificant effect sizes reported in articles deviate from what is expected if there is truly no effect (i.e., $H_0$). Second, we investigate how many research articles report nonsignificant results and how many of those show evidence for at least one false negative using the Fisher test \cite{Fisher1925-jl}.

\subsection*{Method}

<<Download, echo=FALSE, results=hide>>=
# Downloads the data if not available locally

# The data from the Nuijten et al paper
if(!file.exists(sprintf('%sdata/statcheck_full_anonymized.csv', run)))
{
  GET('https://osf.io/gdr4q/?action=download',
      write_disk(sprintf('%sdata/statcheck_full_anonymized.csv', run), overwrite = TRUE))
}

if(!file.exists(sprintf('%sdata/datafilegender500_post.csv', run)))
{
  # the gender related results (ALL)
  GET('https://raw.githubusercontent.com/chartgerink/2014tgtbf/master/data/datafilegender500_post.csv',
      write_disk(sprintf('%sdata/datafilegender500_post.csv', run), overwrite = TRUE))
}

if(!file.exists(sprintf('%sdata/gendercoded cleaned and discussed.csv', run)))
{
  # the coded gender results
  GET('https://raw.githubusercontent.com/chartgerink/2014tgtbf/master/data/gendercoded%20cleaned%20and%20discussed.csv',
      write_disk(sprintf('%sdata/gendercoded cleaned and discussed.csv', run), overwrite = TRUE))
}
@

<<Read in data clean data, echo=FALSE, results=hide>>=
dat <- read.csv2(sprintf("%sdata/statcheck_full_anonymized.csv", run),
                 stringsAsFactors = F,
                 dec = ",",
                 sep = ";")[-1]

# There are two test statistic indicators that are NA
# Manually correct these
dat$Statistic[is.na(dat$Statistic)] <- "F"

# Computing unadjusted and adjusted effect sizes (OBSERVED)
dat <- cbind(dat, esComp.statcheck(dat))
dat$adjESComp[dat$adjESComp < 0] <- 0

# Turning df1 for t and r into 1.
dat$df1[dat$Statistic == "t" | dat$Statistic == "r"] <- 1

# Select out incorrectly exttracted r values
dat <- dat[!(dat$Statistic=="r" & dat$Value > 1),]

# Select out irrefutably wrong df reporting
dat <- dat[!dat$df1 == 0,]

# select out NA computed p-values
dat <- dat[!is.na(dat$Computed),]

# Selecting only the t, r and F values
dat <- dat[dat$Statistic == 't' | dat$Statistic == 'r' | dat$Statistic == 'F',]
nsig <- dat$Computed >= .05
esR <- c(.1, .25, .4)
alpha = .05
alphaF = .1
@

<<Simulations, echo=FALSE, results=hide, eval = FALSE>>=
# Statistical properties of the Fisher method -----------------------------

# condition setting
N <- c(as.numeric(summary(dat$df2)[2]), # 25th percentile
       as.numeric(summary(dat$df2)[3]), # 50th percentile
       as.numeric(summary(dat$df2)[5]) # 75th percentile
)

ES <- c(.00,
        seq(.01, .99, .01))

P <- c(seq(1, 10, 1), seq(15, 50, 5))

alpha <- .05
alphaF <- 0.10
n.iter <- 10000

# NOTE: runs if the results file (N_33.csv, N_62.csv, N_119.csv) are absent

if(!file.exists(sprintf('%sdata/N_33.csv', run)) &
   !file.exists(sprintf('%sdata/N_62.csv', run)) &
   !file.exists(sprintf('%sdata/N_119.csv', run)))
{
  set.seed(35438759)
  source(sprintf('%sfunctions/simCode.R', run))
}

# Load all results back in
files <- list.files()[grepl("N_", list.files())]

names <- str_sub(files,start=1L, end=-5L)
for(i in 1:length(files)){
  assign(x = names[i], read.csv(files[i]))
  assign(x = names[i], t(get(x = names[i])[ ,-1]))
}

# Data for table
# rows are k
# columns are effect size
# N = 33
t(get(x = names[2]))
# N = 62
t(get(x = names[3]))
# N = 119
t(get(x = names[1]))

# Table 3 power computations
ser <- 1/sqrt(c(33, 62, 119)-3)
rho <- .1
zcv <- 1.282
rcv <- (exp(2*(zcv*ser))-1)/(exp(2*(zcv*ser))+1)
zrcv <- .5*log((1+rcv)/(1-rcv))
zrho <- .5*log((1+rho)/(1-rho))
round(1-pnorm(zrcv, mean=zrho, sd=ser),4)

rho <- .25
rcv <- (exp(2*(zcv*ser))-1)/(exp(2*(zcv*ser))+1)
zrcv <- .5*log((1+rcv)/(1-rcv))
zrho <- .5*log((1+rho)/(1-rho))
round(1-pnorm(zrcv, mean=zrho, sd=ser),4)

# Agresti-Coull CI
.1 - qnorm(.95, 0, 1) * (sqrt((1/10000) * .1 * .9))
.1 + qnorm(.95, 0, 1) * (sqrt((1/10000) * .1 * .9))

@

APA style $t$, $r$, and $F$ test statistics were extracted from eight psychology journals with the \texttt{R} package \texttt{statcheck} \cite{Nuijten2015-od,Epskamp2015-ps}. APA style is defined as the format where the type of test statistic is reported, followed by the degrees of freedom (if applicable), the observed test value, and the $p$-value (e.g., $t(85)=2.86, p=.005$; \cite{American_Psychological_Association2010-qe}). The \texttt{statcheck} package also recalculates $p$-values; we used only these recalculated $p$-values to eliminate rounding errors \cite{Bakker2011-hg,Nuijten2015-od}. Table \ref{tab:tab3} depicts the journals, the timeframe and summaries of the results extracted. We reuse the data from Nuijten et al. (\url{osf.io/gdr4q};\cite{Nuijten2015-od}). The database also includes $\chi^2$ results, which we did not use in our analyses because effect sizes based on these results are not readily mapped on the correlation scale.

% Sorry, inserted table manually long time ago, need to check manually
<<prep table 3, echo = FALSE, results = hide>>=
# Descriptives dataset
journals <- sort(unique(dat$journals.jour.))
for(j in 1:length(journals)){
  selJournal <- dat$journals.jour. == journals[j]
  meanK <- mean(table(dat$Source[selJournal]))
  len <- length(dat$Computed[selJournal & !is.na(dat$Computed)])
  sigRes <- sum(dat$Computed[selJournal & !is.na(dat$Computed)] < .05)
  print(
    paste0(
      journals[j], "\t", len, "\t", round(meanK, 1), "\t", sigRes, "\t", len-sigRes
    )
  )
}
@

% Insert table 3
\begin{table}[htbp]
\rowcolors{2}{gray!25}{white}
\begin{adjustbox}{width=\textwidth,totalheight=\textheight,keepaspectratio,angle=0}
\centering
\begin{tabular}{lrrrrr}
Journal (Acronym)                                    & Time frame         & Results         & Mean results per article & Significant (\%)          & Nonsignificant (\%)      \\
\hline
Developmental Psychology (DP)                        & 1985-2013          & 30920           & 13.5                    & 24,584 (79.5\%)           & 6,336 (20.5\%)           \\
Frontiers in Psychology (FP)                         & 2010-2013          & 9172            & 14.9                    & 6,595 (71.9\%)            & 2,577 (28.1\%)           \\
Journal of Applied Psychology (JAP)                  & 1985-2013          & 11240           & 9.1                     & 8,455 (75.2\%)            & 2,785 (24.8\%)           \\
Journal of Consulting and Clinical Psychology (JCCP) & 1985-2013          & 20083           & 9.8                     & 15,672 (78.0\%)           & 4,411 (22.0\%)           \\
Journal of Experimental Psychology: General (JEPG)   & 1985-2013          & 17283           & 22.4                    & 12,706 (73.5\%)           & 4,577 (26.5\%)           \\
Journal of Personality and Social Psychology (JPSP)  & 1985-2013          & 91791           & 22.5                    & 69,836 (76.1\%)           & 21,955 (23.9\%)          \\
Public Library of Science (PLOS)                     & 2003-2013          & 28561           & 13.2                    & 19,696 (69.0\%)           & 8,865 (31.0\%)           \\
Psychological Science (PS)                           & 2003-2013          & 14032           & 9                       & 10,943 (78.0\%)           & 3,089 (22.0\%)           \\
\hline
\textit{Totals}                                      & \textit{1985-2013} & \textit{223082} & \textit{14.3}           & \textit{168,487 (75.5\%)} & \textit{54,595 (24.5\%)}\\
\hline
\end{tabular}
\end{adjustbox}
\caption{Summary table of articles downloaded per journal, their mean number of results, and proportion of (non)significant results. Statistical significance was determined using $\alpha=.05$, two-tailed}
\label{tab:tab3}
\end{table}

First, we compared the observed nonsignificant effect size distribution to the expected nonsignificant effect size distribution under $H_0$. The expected effect size distribution under $H_0$ was approximated using simulation. We first randomly drew an observed test result (with replacement) and subsequently drew a random nonsignificant $p$-value between 0.05 and 1. Based on the drawn $p$-value and the degrees of freedom of the test result, we computed the accompanying test statistic and the corresponding effect size (for details on effect size computation see Appendix B). This procedure was repeated 163,785 times, which is three times the number of observed nonsignificant test results (54,595). The collection of simulated results approximates the expected effect size distribution under $H_0$, assuming independence of test results. This expected effect size distribution is compared to the observed effect size distribution (i) across all journals and (ii) per journal. To test for differences between the expected and observed nonsignificant effect size distributions we applied the Kolmogorov-Smirnov test. This is a non-parametric goodness-of-fit test for equality of distributions, which is based on the maximum absolute deviation between the independent distributions being compared (denoted D; \cite{Massey1951-gj}).

Second, we applied the Fisher test to test how many research papers show evidence of at least one false negative statistical result. To recapitulate, the Fisher test tests whether the distribution of observed nonsignificant $p$-values deviates from the uniform distribution expected under $H_0$. In order to compute the result of the Fisher test, we applied equations \ref{pistar} and \ref{fishertest} to the recalculated nonsignificant $p$-values in each paper ($\alpha=.05$).

\subsection*{Results}

\subsubsection*{Observed effect size distribution.}

<<percentages, echo = FALSE, results = hide>>=
small <- sum(dat$esComp[!is.na(dat$esComp)] < .1) / length(dat$esComp[!is.na(dat$esComp)]) * 100
medium <- sum(dat$esComp[!is.na(dat$esComp)] >= .1 & dat$esComp[!is.na(dat$esComp)] < .25) / length(dat$esComp[!is.na(dat$esComp)]) * 100
large <- sum(dat$esComp[!is.na(dat$esComp)] >= .25 & dat$esComp[!is.na(dat$esComp)] < .4) / length(dat$esComp[!is.na(dat$esComp)]) * 100
larger <- sum(dat$esComp[!is.na(dat$esComp)] >= .4) / length(dat$esComp[!is.na(dat$esComp)]) * 100
@

Figure \ref{fig:fig1} shows the distribution of observed effect sizes (in $|\eta|$) across all articles and indicates that, of the 223,082 observed effects, \Sexpr{round(small, 0)}\% were zero to small (i.e., $0\leq|\eta|<.1$), \Sexpr{round(medium, 0)}\% were small to medium (i.e., $.1\leq|\eta|<.25$), \Sexpr{round(large, 0)}\% medium to large (i.e., $.25\leq|\eta|<.4$), and \Sexpr{round(larger, 0)}\% large or larger (i.e., $|\eta|\geq.4$; \cite{Cohen1988-wg}). This suggests that the majority of effects reported in psychology is medium or smaller (i.e., \Sexpr{round(medium+small,0)}\%). Of the full set of 223,082 test results, 54,595 (24.5\%) were nonsiginificant, which is the dataset for our main analyses.

\begin{figure}
\begin{center}
<<label=fig1,fig=TRUE,echo=FALSE>>=
# par(mai = c(1, 1, .2, .2))

plot(density(dat$esComp[!is.na(dat$esComp)]),
     lty = 1,
     frame.plot = T, 
     main = "",
     xlim = c(0, 1), ylim = c(0, 2),
     xaxs = "i",
     yaxs = 'i',
     xlab = TeX("Correlation (|$\\eta$|)"),
     ylab = "Density",
     cex.axis = .8,
     cex.lab = 1,
     col = "black", las = 1, bty = 'n')
abline(v = c(.1, .25, .4), lty = 2, col = "grey")
t1 <- sum(dat$esComp[!is.na(dat$esComp)] < .1) / length(dat$esComp[!is.na(dat$esComp)])
t2 <- sum(dat$esComp[!is.na(dat$esComp)] >= .1 & dat$esComp[!is.na(dat$esComp)] < .25) / length(dat$esComp[!is.na(dat$esComp)])
t3 <- sum(dat$esComp[!is.na(dat$esComp)] >= .25 & dat$esComp[!is.na(dat$esComp)] < .4) / length(dat$esComp[!is.na(dat$esComp)])
t4 <- sum(dat$esComp[!is.na(dat$esComp)] >= .4) / length(dat$esComp[!is.na(dat$esComp)])
text(x = .1 / 2, y = .15, labels = round(t1, 2), cex = 1)
text(x = ((.25 - .1) / 2) + .1, y = .15, labels = round(t2, 2), cex = 1)
text(x = ((.4 - .25) / 2) + .25, y = .15, labels = round(t3, 2), cex = 1)
text(x = ((1 - .4) / 2) + .4, y = .15, labels = round(t4, 2), cex = 1)
@
\end{center}
\caption{Density of observed effect sizes of results reported in eight psychology journals, with \Sexpr{round(small, 0)}\% of effects in the category none-small, \Sexpr{round(medium, 0)}\% small-medium, \Sexpr{round(large, 0)}\% medium-large, and \Sexpr{round(larger, 0)}\% beyond large.}
\label{fig:fig1}
\end{figure}

Our dataset indicated that more nonsignificant results are reported throughout the years, strengthening the case for inspecting potential false negatives. The proportion of nonsignificant results showed an upward trend, as depicted in Figure 4, from approximately 20\% to approximately 30\% of all reported APA results.

\begin{figure}
\begin{center}
<<label=fig2,fig=TRUE,echo=FALSE>>=
# par(mai = c(1, 1, .2, .2))
# nonsignificant proportion p/year
i <- 1
sig <- NULL
nsigtemp <- NULL
kval <- NULL

for(y in 1985:2013){
  sel <- dat$years.y. == y
  sig[i] <- sum(dat$Computed[sel] < alpha) / length(dat$Computed[sel])
  nsigtemp[i] <- sum(dat$Computed[sel] > alpha) / length(dat$Computed[sel])
  kval[i] <- median(table(dat$Source[sel])) / sum(table(dat$Source[sel]))
  i <- i + 1
}
par(mfrow = c(1, 1), mai = c(1, 1, .2, .2))
plot(x = 1985:2013,
     nsigtemp,
     ylim = c(0, .4),
     type = 'o',
     xlab = "Year", ylab = 'Proportion nonsignificant',
     yaxs = 'i',
     cex.axis = 1, las = 1, bty = 'n')
# abline(lm(nsigtemp ~ c(1985:2013)), lty = 2)

@
\end{center}
\caption{Observed proportion of nonsignificant test results per year.}
\label{fig:fig2}
\end{figure}

\subsubsection*{Expected effect size distribution.}

<<Simulating null distribution>>=
# takes some time to run these, have to simulate many values
# go get coffee
set.seed(1234)
simNullEs <- simNullDist(dat, n.iter = length(dat$esComp[nsig]) * 3, alpha = .05)
simNullEs$adjESComp[simNullEs$adjESComp < 0] <- 0

temp <- ks.test(simNullEs$esComp,
                dat$esComp[nsig],
                alternative="greater")
@

For the entire set of nonsignificant results across journals, Figure 5 indicates that there is substantial evidence of false negatives. Under $H_0$, 46\% of all observed effects is expected to be within the range $0\geq|\eta|<.1$, as can be seen in the left panel of Figure 5 highlighted by the lowest grey line. However, of the observed effects, only 26\% fall within this range, as highlighted by the lowest black line. Similarly, we would expect 85\% of all effect sizes to be within the range $0\geq|\eta|<.25$ (middle grey line), but we observed 14 percentage points less in this range (i.e., 71\%; middle black line); 96\% is expected for the range $0\geq|\eta|<.4$ (top grey line), but we observed 4 percentage points less (i.e., 92\%; top black line). These differences indicate that larger effects are observed in the nonsignificant results than expected under a null effect. This indicates the presence of false negatives, which is confirmed by the Kolmogorov-Smirnov test, $D=.23$, $p<.000000000000001$. Results were similar when the nonsignificant effects were considered separately for the eight journals, although deviations were smaller for the Journal of Applied Psychology (see Figure S1 for results per journal).

\section*{Application 2: Evidence of false negative gender effects in eight major psychology journals}

\section*{Application 3: Reproducibility Project Psychology}

\section*{General discussion}

\section*{Appendix A}
\subsection*{Examining statistical properties of the Fisher test}
The Fisher test to detect false negatives is only useful if it is powerful enough to detect evidence of at least one false negative result in papers with few nonsignificant results. Therefore we examined the specificity and sensitivity of the Fisher test to test for false negatives, with a simulation study of the one sample $t$-test. Throughout this paper, we apply the Fisher test with $\alpha_{Fisher}=0.10$, because tests that inspect whether results are "too good to be true" typically also use alpha levels of 10\% \cite{Sterne2000-wh,Ioannidis2007-hh,Francis2012-kw}. The simulation procedure was carried out for conditions in a three-factor design, where power of the Fisher test was simulated as a function of sample size $N$, effect size $\eta$, and $k$ test results. The three factor design was a 3 (sample size $N$: 33, 62, 119) by 100 (effect size $\eta$: .00, .01, .02, ..., .99) by 18 ($k$ test results: 1, 2, 3, ..., 10, 15, 20, ..., 50) design, resulting in 5,400 conditions. The levels for sample size were determined based on the 25th, 50th, and 75th percentile for the degrees of freedom ($df2$) in the observed dataset for Application 1. Each condition contained 10,000 simulations. The power of the Fisher test for one condition was calculated as the proportion of significant Fisher test results given $\alpha_{Fisher}=0.10$. If the power for a specific effect size $\eta$ was $\geq99.5\%$, power for larger effect sizes were set to 1.

We simulated false negative $p$-values according to the following six steps (see Figure \ref{fig:appendixa}). First, we determined the critical value under the null distribution. Second, we determined the alternative distribution by computing the non-centrality parameter ($\delta=(\eta^2/1-\eta^2)N$; \cite{Steiger1997-qq,Smithson2001-aw}). Third, we calculated the probability that a result under the alternative distribution was, in fact, nonsignificant (i.e., $\beta$). Fourth, we randomly sampled, uniformly, a value between $0-\beta$. Fifth, with this value we determined the accompanying $t$-value. Finally, we computed the $p$-value for this $t$-value under the null distribution.

\begin{figure}[!ht]
\centering
\includegraphics[width=0.75\textwidth]{../figures/appendix_a}
\caption{Visual aid for simulating one nonsignificant test result. The critical value from $H_0$ (left distribution) was used to determine $\beta$ under $H_1$ (right distribution). A value between 0 and $\beta$ was drawn, $t$-value computed, and $p$-value under $H_0$ determined.}
\label{fig:appendixa}
\end{figure}

We repeated the procedure to simulate a false negative $p$-value $k$ times and used the resulting $p$-values to compute the Fisher test. Before computing the Fisher test statistic, the nonsignificant $p$-values were transformed (see Equation \ref{pistar}). Subsequently, we computed the Fisher test statistic and the accompanying $p$-value according to Equation \ref{fishertest}.

\section*{Appendix B}
\subsection*{Effect computation}

The $t$, $F$, and $r$-values were all transformed into the effect size $\eta^2$, which is the explained variance for that test result and ranges between 0 and 1, for comparing observed to expected effect size distributions. For $r$-values, this only requires taking the square (i.e., $r^2$). $F$ and $t$-values were converted to effect sizes by
\begin{equation}
\eta^2=\frac{\frac{F\times df_1}{df_2}}{\frac{F\times df_1}{df_2}+1}
\label{eq:b1}
\end{equation}
where $F=t^2$ and $df_1=1$ for $t$-values. Adjusted effect sizes, which correct for positive bias due to sample size, were computed as
\begin{equation}
\eta^2_{adj}=\frac{\frac{F\times df_1}{df_2}-\frac{df_1}{df_2}}{\frac{F\times df_1}{df_2}+1}
\label{eq:b2}
\end{equation}
which shows that when $F=1$ the adjusted effect size is zero. For $r$-values the adjusted effect sizes were computed as \cite{Ivarsson2013-rm}
\begin{equation}
\eta^2_{adj}=\eta^2-([1-\eta^2]\times\frac{v}{N-v-1})
\label{eq:b3}
\end{equation}
where $v$ is the number of predictors. It was assumed that reported correlations concern simple bivariate correlations and concern only one predictor (i.e., $v=1$). This reduces the previous formula to
\begin{equation}
\eta^2_{adj}=\eta^2-\frac{1-\eta^2}{df}
\label{eq:b4}
\end{equation}
where $df=N-2$.
\bibliography{../bibliography/library}
\end{document}

### 2016-09-20 submission/manuscript.Rnw
Clean repo, make sure dling files and generating ms works: YES

@@
 \bibliographystyle{../bibliography/plos2015}
+
+% \setkeys{Gin}{width=1.2\textwidth}
 
@@
 
-Popper’s \cite{Popper2005-xu} falsifiability serves as one of the main demarcating criteria in the social sciences, which stipulates that a hypothesis is required to have the possibility of being proven false to be considered scientific.
+Popper's \cite{Popper2005-xu} falsifiability serves as one of the main demarcating criteria in the social sciences, which stipulates that a hypothesis is required to have the possibility of being proven false to be considered scientific.
 Within the theoretical framework of scientific hypothesis testing, accepting or rejecting a hypothesis is unequivocal, because the hypothesis is either true or false.
@@
 The probability of finding a positive if $H_1$ is true is the power ($1-\beta$), which is also called the sensitivity of the test.
-Power is a positive function of the population effect size, the sample size, and the alpha of the study, such that higher power can always be achieved by altering either the sample size or the alpha level \cite{Aberson2010-xa}.
+Power is a positive function of the (true) population effect size, the sample size, and the alpha of the study, such that higher power can always be achieved by altering either the sample size or the alpha level \cite{Aberson2010-xa}.
 
@@
 % \rowcolors{2}{gray!25}{white}
+\caption{Summary table of possible NHST results.
+Columns indicate the true situation in the population, rows indicate the decision based on a statistical test.
+The true positive probability is also called power and sensitivity, whereas the true negative rate is also called specificity.}
 \begin{adjustbox}{width=\textwidth,totalheight=\textheight,keepaspectratio,angle=0}
@@
 \end{adjustbox}
-\caption{Summary table of possible NHST results.
-Columns indicate the true situation in the population, rows indicate the decision based on a statistical test.
-The true positive probability is called power and sensitivity, whereas the true negative rate is also called specificity.}
 \label{tab:tab1}
@@
 Besides psychology, reproducibility problems have also been indicated in economics \cite{Camerer2016-zz} and medicine \cite{Begley2012-uc}.
-Although these studies provide substantial evidence of false positives in these fields, replications show considerable variability \cite{Klein2014-jb, Stanley2014-pd}, therefore caution is warranted when wishing to draw conclusions on the presence of an effect in individual studies \cite{Open_Science_Collaboration2015-zs,Gilbert2016-mi,Anderson2016-bv}.
+Although these studies suggest substantial evidence of false positives in these fields, replications show considerable variability in resulting effect size estimates \cite{Klein2014-jb, Stanley2014-pd}.
+Therefore caution is warranted when wishing to draw conclusions on the presence of an effect in individual studies (original or replication; \cite{Open_Science_Collaboration2015-zs,Gilbert2016-mi,Anderson2016-bv}).
 
 The debate about false positives is driven by the current overemphasis on statistical significance of research results \cite{Giner-Sorolla2012-wn}.
-This overemphasis is substantiated by the finding that >90\% of results in the psychology literature are statistically significant \cite{Open_Science_Collaboration2015-zs,Sterling1995-fe,Sterling1959-pf} despite low power due to small sample sizes \cite{Cohen1962-jc,Sedlmeier1989-yc,Marszalek2011-rf,Bakker2012-tf}.
-Consequently, publications have become biased by overrepresenting statistically significant results \cite{Greenwald1975-ck}, which generally results in effect size overestimation in individual studies \cite{Nuijten2015-od} and in meta-analyses \cite{Van_Assen2015-gg}.
-The overemphasis on statistically significant effects has been accompanied by questionable research practices (QRPs, \cite{John2012-uj}) such as erroneously rounding p-values towards significance, which occurred for at least 13.81\% of all $p$-values reported as "$p =.05$" in articles from eight major psychology journals in the period 1985-2013 \cite{Hartgerink2016-mm}.
+This overemphasis is substantiated by the finding that >90\% of results in the psychology literature are statistically significant \cite{Open_Science_Collaboration2015-zs,Sterling1995-fe,Sterling1959-pf} despite low statistical power due to small sample sizes \cite{Cohen1962-jc,Sedlmeier1989-yc,Marszalek2011-rf,Bakker2012-tf}.
+Consequently, publications have become biased by overrepresenting statistically significant results \cite{Greenwald1975-ck}, which generally results in effect size overestimation in individual studies \cite{Nuijten2015-od} and in meta-analyses \cite{Van_Assen2015-gg,Lane_1978,Rothstein2005-zg,Borenstein2009-vs}.
+The overemphasis on statistically significant effects has been accompanied by questionable research practices (QRPs, \cite{John2012-uj}) such as erroneously rounding p-values towards significance, which for example occurred for 13.8\% of all $p$-values reported as "$p =.05$" in articles from eight major psychology journals in the period 1985-2013 \cite{Hartgerink2016-mm}.
 
@@
 This has not changed throughout the subsequent fifty years \cite{Bakker2012-tf,Fraley2014-xs}.
-In other words, the problem of false negatives has no empirical evidence of being resolved in psychology.
-Fiedler, Kutzner, and Krueger \cite{Fiedler2012-gx} worry that an increased focus on false positives is too shortsighted, arguing that false negatives are more difficult to detect than false positives.
+In other words, no evidence exists that the problem of false negatives has been resolved in psychology.
+Moreover, Fiedler, Kutzner, and Krueger \cite{Fiedler2012-gx} worry that an increased focus on false positives is too shortsighted, arguing that false negatives are more difficult to detect than false positives.
 They also argue that, because of the focus on statistically significant results, negative results are less likely to be the subject of replications than positive results, decreasing the probability of detecting a false negative.
@@
 To this end, we inspected a large number of nonsignificant results from eight flagship psychology journals.
-First, we compared the observed effect distributions for eight journals (combined and separately) to the expected null distribution based on simulations, where a discrepancy between observed and expected distribution was anticipated (i.e., presence of false negatives).
-Second, we propose to use the Fisher test to test the hypothesis that $H_0$ is true for all nonsignificant results in a paper, which we show to have high power to detect false negatives in a simulation study.
+First, we compared the observed effect distributions of nonsignificant results for eight journals (combined and separately) to the expected null distribution based on simulations, where a discrepancy between observed and expected distribution was anticipated (i.e., presence of false negatives).
+Second, we propose to use the Fisher test to test the hypothesis that $H_0$ is true for all nonsignificant results reported in a paper, which we show to have high power to detect false negatives in a simulation study.
 Third, we applied the Fisher test to the nonsignificant results in 14,765 psychology papers from these eight flagship psychology journals to inspect how many papers show evidence of at least one false negative result.
@@
 
-We begin by reviewing how individual- and sets of nonsignificant $p$-values are distributed.
-Subsequently, we propose a way to test whether a collection of nonsignificant results across papers deviates from what would be expected under $H_0$.
-We also propose a way to test whether nonsignificant results deviate from $H_0$ within a paper.
-These methods will be used to test whether and to what extent there is evidence for false negatives in the psychology literature.
+We begin by reviewing the probability density function of both an individual $p$-value and a set of independent $p$-values as a function of population effect size.
+Subsequently, we propose  a method to test whether a collection of nonsignificant results across papers deviates from what would be expected under the $H_0$.
+We also propose a method to test whether nonsignificant results deviate from $H_0$ within a paper.
+These methods will be used to test whether there is evidence for false negatives in the psychology literature.
 
@@
 When the population effect is zero, the probability distribution of one $p$-value is uniform.
-When there is an effect, the probability distribution is right-skewed.
-More specifically, as sample size or true effect size increases, the probability distribution of one $p$-value becomes increasingly right skewed.
-These regularities also generalize to a set of $p$-values, which are uniformly distributed when there is no population effect and right skew distributed when there is a population effect, with more right skew as the population effect and/or precision increases.
+When there is a non-zero effect, the probability distribution is right-skewed.
+More specifically, as sample size or true effect size increases, the probability distribution of one $p$-value becomes increasingly right-skewed.
+These regularities also generalize to a set of independent $p$-values, which are uniformly distributed when there is no population effect and right-skew distributed when there is a population effect, with more right-skew as the population effect and/or precision increases.
 
@@
 \end{equation}
-where $p_i$ an untransformed nonsignificant $p$-value and $\alpha$ is the selected significance cutoff (i.e., $\alpha=.05$).
-This transformation retains the distributional properties of the original $p$-values for the selected nonsignificant results.
+where $p_i$ is the  reported nonsignificant $p$-value and $\alpha$ is the selected significance cutoff (i.e., $\alpha=.05$).
+Note this transformation retains the distributional properties of the original $p$-values for the selected nonsignificant results.
 
@@
 
-We applied the Fisher test to inspect whether observed nonsignificant results deviate from those expected under $H_0$.
-The Fisher test was initially introduced as a meta-analytic technique to synthesize results across studies \cite{Fisher1925-jl,Hedges1985-dy}, but when applied to transformed nonsignificant $p$-values (see Equation \ref{pistar}) the Fisher test tests for evidence against $H_0$ in a set of nonsignificant results.
+We applied the Fisher test to inspect whether the distribution of observed nonsignificant $p$-values deviates from those expected under $H_0$.
+The Fisher test was initially introduced as a meta-analytic technique to synthesize results across studies \cite{Fisher1925-jl,Hedges1985-dy}.
+When applied to transformed nonsignificant $p$-values (see Equation \ref{pistar}) the Fisher test tests for evidence against $H_0$ in a set of nonsignificant $p$-values.
 In other words, the null we test with the Fisher test is that all included nonsignificant results are true negatives.
@@
 \label{fishertest}
-\chi^2_{2k}=-2\sum\limits^k_{i=1}ln(p_i)
+\chi^2_{2k}=-2\sum\limits^k_{i=1}ln(p^*_i)
 \end{equation}
@@
 
-We estimated the power of detecting false negatives with the Fisher test as a function of sample size $N$, correlation effect size $\eta$, and $k$ nonsignificant test results (procedure described in Appendix A).
-The 25th, 50th (median) and 75th percentiles of the degrees of freedom in eight flagship psychology journals (see Application 1 below) were taken to represent sample size, given their direct relation to sample size (e.g., for a two-group comparison including 100 people, df = 98).
-Table \ref{tab:tab2} summarizes results for the simulations of the Fisher test when the nonsignificant $p$-values are generated by either small- or medium population effect sizes.
+We estimated the power of detecting false negatives with the Fisher test as a function of sample size $N$, true correlation effect size $\eta$, and $k$ nonsignificant test results (procedure described in Appendix A).
+The three levels of sample size (33, 62, 119) correspond to the  25th, 50th (median) and 75th percentiles of the degrees of freedom of reported $t$, $F$, and $r$ statistics in eight flagship psychology journals (see Application 1 below).
+Degrees of freedom of these statistics are directly related to sample size, for instance, for a two-group comparison including 100 people, df = 98.
+
+Table \ref{tab:tab2} summarizes the results for the simulations of the Fisher test when the nonsignificant $p$-values are generated by either small- or medium population effect sizes.
 Results for all 5,400 conditions can be found on the OSF (\url{osf.io/qpfnw}).
 The results indicate that the Fisher test is a powerful method to test for a false negative among nonsignificant results when there are not only small effects investigated in small samples.
-For example, for small effect sizes ($\eta=.1$), 50, 25, 7 nonsignificant results are required to obtain a power of 69\%, 85\%, 83\% for sample sizes 33, 62, and 119, respectively.
-For medium effects ($\eta=.25$), small samples ($N=33$) and three nonsignificant results already provide 89\% power for detecting a false negative with the Fisher test.
-For large effects ($\eta=.4$), small samples and 2 nonsignificant results already detects all false negatives (based on the simulations).
+For example, for small true effect sizes ($\eta=.1$), 50, 25, 7 nonsignificant results are required to obtain a power of 69\%, 85\%, 83\% for sample sizes of 33, 62, and 119, respectively.
+For medium true effects ($\eta=.25$), small samples ($N=33$) and three nonsignificant results already provide 89\% power for detecting a false negative with the Fisher test.
+For large effects ($\eta=.4$), small samples and 2 nonsignificant results already almost always detects all false negatives.
 
@@
 \begin{table}[htbp]
+\caption{Power of Fisher test to detect false negatives for small- and medium effect sizes (i.e., $\eta=.1$ and $\eta=.25$), for different sample sizes (i.e., $N$) and number of test results (i.e., $k$).
+Results of each condition are based on 10,000 iterations.
+Power was rounded to 1 whenever it was larger than .9995.}
 \rowcolors{2}{gray!25}{white}
@@
 \begin{tabular}{llllllll}
-&        & $\eta=.1$ (small) &         &  &        & $\eta=.25$ (medium) &         \\
-& $N=33$ & $N=62$         & $N=119$ &  & $N=33$ & $N=62$           & $N=119$ \\
+&        & $\eta=.1$ &         &        & $\eta=.25$ &         \\
+& $N=33$ & $N=62$ & $N=119$ & $N=33$ & $N=62$ & $N=119$ \\
 \hline
-$k=1$  & 0.1512 & 0.211          & 0.341   &  & 0.5752 & 0.8516           & 0.9833  \\
-$k=2$  & 0.1746 & 0.2667         & 0.4591  &  & 0.7793 & 0.9778           & 1       \\
-$k=3$  & 0.2008 & 0.3167         & 0.5717  &  & 0.8935 & 1                & 1       \\
-$k=4$  & 0.2077 & 0.352          & 0.6587  &  & 0.9482 & 1                & 1       \\
-$k=5$  & 0.2287 & 0.3897         & 0.7194  &  & 0.9748 & 1                & 1       \\
-$k=6$  & 0.251  & 0.4336         & 0.7842  &  & 0.9899 & 1                & 1       \\
-$k=7$  & 0.2585 & 0.471          & 0.8336  &  & 0.9953 & 1                & 1       \\
-$k=8$  & 0.2801 & 0.5136         & 0.8709  &  & 0.9979 & 1                & 1       \\
-$k=9$  & 0.2984 & 0.5298         & 0.8945  &  & 1      & 1                & 1       \\
-$k=10$ & 0.3035 & 0.5702         & 0.9178  &  & 1      & 1                & 1       \\
-$k=15$ & 0.3624 & 0.6912         & 0.9798  &  & 1      & 1                & 1       \\
-$k=20$ & 0.4291 & 0.7804         & 0.9958  &  & 1      & 1                & 1       \\
-$k=25$ & 0.4898 & 0.852          & 0.9995  &  & 1      & 1                & 1       \\
-$k=30$ & 0.5308 & 0.8936         & 1       &  & 1      & 1                & 1       \\
-$k=35$ & 0.578  & 0.9303         & 1       &  & 1      & 1                & 1       \\
-$k=40$ & 0.6214 & 0.953          & 1       &  & 1      & 1                & 1       \\
-$k=45$ & 0.6538 & 0.9661         & 1       &  & 1      & 1                & 1       \\
-$k=50$ & 0.6855 & 0.9762         & 1       &  & 1      & 1                & 1   \\
+$k=1$ & 0.151 & 0.211 & 0.341 & 0.575 & 0.852 & 0.983 \\
+$k=2$ & 0.175 & 0.267 & 0.459 & 0.779 & 0.978 & 1 \\
+$k=3$ & 0.201 & 0.317 & 0.572 & 0.894 & 1 & 1 \\
+$k=4$ & 0.208 & 0.352 & 0.659 & 0.948 & 1 & 1 \\
+$k=5$ & 0.229 & 0.390 & 0.719 & 0.975 & 1 & 1 \\
+$k=6$ & 0.251 & 0.434 & 0.784 & 0.990 & 1 & 1 \\
+$k=7$ & 0.259 & 0.471 & 0.834 & 0.995 & 1 & 1 \\
+$k=8$ & 0.280 & 0.514 & 0.871 & 0.998 & 1 & 1 \\
+$k=9$ & 0.298 & 0.530 & 0.895 & 1 & 1 & 1 \\
+$k=10$ & 0.304 & 0.570 & 0.918 & 1 & 1 & 1 \\
+$k=15$ & 0.362 & 0.691 & 0.980 & 1 & 1 & 1 \\
+$k=20$ & 0.429 & 0.780 & 0.996 & 1 & 1 & 1 \\
+$k=25$ & 0.490 & 0.852 & 1 & 1 & 1 & 1 \\
+$k=30$ & 0.531 & 0.894 & 1 & 1 & 1 & 1 \\
+$k=35$ & 0.578 & 0.930 & 1 & 1 & 1 & 1 \\
+$k=40$ & 0.621 & 0.953 & 1 & 1 & 1 & 1 \\
+$k=45$ & 0.654 & 0.966 & 1 & 1 & 1 & 1 \\
+$k=50$ & 0.686 & 0.976 & 1 & 1 & 1 & 1 \\
+
 \hline
@@
 \end{adjustbox}
-\caption{Power of Fisher test to detect false negatives for small- and medium effect sizes (i.e., $\eta=.1$ and $\eta=.25$), for different sample sizes (i.e., $N$) and number of test results (i.e., $k$).
-Results of each condition are based on 10,000 iterations.
-Power was rounded to 1 whenever it was larger than .995.}
 \label{tab:tab2}
@@
 To show that statistically nonsignificant results do not warrant the interpretation that there is truly no effect, we analyzed statistically nonsignificant results from eight major psychology journals.
-First, we investigate to what degree nonsignificant effect sizes reported in articles deviate from what is expected if there is truly no effect (i.e., $H_0$).
+First, we investigate if and how much the distribution of reported nonsignificant effect sizes deviates from what the expected effect size distribution is if there is truly no effect (i.e., $H_0$).
 Second, we investigate how many research articles report nonsignificant results and how many of those show evidence for at least one false negative using the Fisher test \cite{Fisher1925-jl}.
@@
 The database also includes $\chi^2$ results, which we did not use in our analyses because effect sizes based on these results are not readily mapped on the correlation scale.
+Two erroneously reported test statistics were eliminated, such that these did not confound results.
+
+The analyses reported in this paper use the recalculated $p$-values to eliminate potential errors in the reported $p$-values.
+However, our recalculated $p$-values assumed that all other test statistics (degrees of freedom, test values of $t$, $F$, or $r$) are correctly reported.
+These errors,  may have affected the results of our analyses.
+Since most $p$-values and corresponding test statistics were consistent in our dataset (\Sexpr{round((dim(dat)[1] - sum(dat$Error[!is.na(dat$Error)])) / dim(dat)[1] * 100,1)}\%), we do not believe these typing errors substantially affected our results and conclusions based on them.
 
@@
 \begin{table}[htbp]
+\caption{Summary table of articles downloaded per journal, their mean number of results, and proportion of (non)significant results.
+Statistical significance was determined using $\alpha=.05$, two-tailed}
 \rowcolors{2}{gray!25}{white}
@@
 \begin{tabular}{lrrrrr}
-Journal (Acronym)                                    & Time frame         & Results         & Mean results per article & Significant (\%)          & Nonsignificant (\%)      \\
+\pbox{3cm}{Journal (Acronym)}                                    & Time frame         & Results         & \pbox{1.5cm}{Mean results per article} & \pbox{1.5cm}{Significant (\%)}          & \pbox{2cm}{Nonsignificant (\%)}      \\
 \hline
-Developmental Psychology (DP)                        & 1985-2013          & 30920           & 13.5                    & 24,584 (79.5\%)           & 6,336 (20.5\%)           \\
-Frontiers in Psychology (FP)                         & 2010-2013          & 9172            & 14.9                    & 6,595 (71.9\%)            & 2,577 (28.1\%)           \\
-Journal of Applied Psychology (JAP)                  & 1985-2013          & 11240           & 9.1                     & 8,455 (75.2\%)            & 2,785 (24.8\%)           \\
-Journal of Consulting and Clinical Psychology (JCCP) & 1985-2013          & 20083           & 9.8                     & 15,672 (78.0\%)           & 4,411 (22.0\%)           \\
-Journal of Experimental Psychology: General (JEPG)   & 1985-2013          & 17283           & 22.4                    & 12,706 (73.5\%)           & 4,577 (26.5\%)           \\
-Journal of Personality and Social Psychology (JPSP)  & 1985-2013          & 91791           & 22.5                    & 69,836 (76.1\%)           & 21,955 (23.9\%)          \\
-Public Library of Science (PLOS)                     & 2003-2013          & 28561           & 13.2                    & 19,696 (69.0\%)           & 8,865 (31.0\%)           \\
-Psychological Science (PS)                           & 2003-2013          & 14032           & 9                       & 10,943 (78.0\%)           & 3,089 (22.0\%)           \\
+\pbox{3cm}{Developmental Psychology (DP)}                        & 1985-2013          & 30,920           & 13.5                    & \pbox{1.5cm}{24,584 (79.5\%)}           & \pbox{2cm}{6,336 (20.5\%)}           \\
+\pbox{3cm}{Frontiers in Psychology (FP)}                         & 2010-2013          & 9,172            & 14.9                    & \pbox{1.5cm}{6,595 (71.9\%)}            & \pbox{2cm}{2,577 (28.1\%)}           \\
+\pbox{3cm}{Journal of Applied Psychology (JAP)}                  & 1985-2013          & 11,240           & 9.1                     & \pbox{1.5cm}{8,455 (75.2\%)}            & \pbox{2cm}{2,785 (24.8\%)}           \\
+\pbox{3cm}{Journal of Consulting and Clinical Psychology (JCCP)} & 1985-2013          & 20,083           & 9.8                     & \pbox{1.5cm}{15,672 (78.0\%)}           & \pbox{2cm}{4,411 (22.0\%)}           \\
+\pbox{3cm}{Journal of Experimental Psychology: General (JEPG)}   & 1985-2013          & 17,283           & 22.4                    & \pbox{1.5cm}{12,706 (73.5\%)}           & \pbox{2cm}{4,577 (26.5\%)}           \\
+\pbox{3cm}{Journal of Personality and Social Psychology (JPSP)}  & 1985-2013          & 91,791           & 22.5                    & \pbox{1.5cm}{69,836 (76.1\%)}           & \pbox{2cm}{21,955 (23.9\%)}          \\
+\pbox{3cm}{Public Library of Science (PLOS)}                     & 2003-2013          & 28,561           & 13.2                    & \pbox{1.5cm}{19,696 (69.0\%)}           & \pbox{2cm}{8,865 (31.0\%)}           \\
+\pbox{3cm}{Psychological Science (PS)}                           & 2003-2013          & 14,032           & 9                       & \pbox{1.5cm}{10,943 (78.0\%)}           & \pbox{2cm}{3,089 (22.0\%)}           \\
 \hline
-\textit{Totals}                                      & \textit{1985-2013} & \textit{223082} & \textit{14.3}           & \textit{168,487 (75.5\%)} & \textit{54,595 (24.5\%)}\\
+\textit{Totals}                                      & \textit{1985-2013} & \textit{223,082} & \textit{14.3}           & \pbox{1.5cm}{\textit{168,487 (75.5\%)}} & \pbox{2cm}{\textit{54,595 (24.5\%)}}\\
 \hline
@@
 \end{adjustbox}
-\caption{Summary table of articles downloaded per journal, their mean number of results, and proportion of (non)significant results.
-Statistical significance was determined using $\alpha=.05$, two-tailed}
 \label{tab:tab3}
@@
 The expected effect size distribution under $H_0$ was approximated using simulation.
-We first randomly drew an observed test result (with replacement) and subsequently drew a random nonsignificant $p$-value between 0.05 and 1.
-Based on the drawn $p$-value and the degrees of freedom of the test result, we computed the accompanying test statistic and the corresponding effect size (for details on effect size computation see Appendix B).
+We first randomly drew an observed test result (with replacement) and subsequently drew a random nonsignificant $p$-value between 0.05 and 1 (i.e., under the distribution of the $H_0$).
+Based on the drawn $p$-value and the degrees of freedom of the drawn test result, we computed the accompanying test statistic and the corresponding effect size (for details on effect size computation see Appendix B).
 This procedure was repeated 163,785 times, which is three times the number of observed nonsignificant test results (54,595).
 The collection of simulated results approximates the expected effect size distribution under $H_0$, assuming independence of test results.
-This expected effect size distribution is compared to the observed effect size distribution (i) across all journals and (ii) per journal.
+This expected effect size distribution was compared to the observed effect size distribution (i) across all journals and (ii) per journal.
 To test for differences between the expected and observed nonsignificant effect size distributions we applied the Kolmogorov-Smirnov test.
-This is a non-parametric goodness-of-fit test for equality of distributions, which is based on the maximum absolute deviation between the independent distributions being compared (denoted D; \cite{Massey1951-gj}).
+This is a non-parametric goodness-of-fit test for equality of distributions, which is based on the maximum absolute deviation between the independent distributions being compared (denoted $D$; \cite{Massey1951-gj}).
 
@@
 <<percentages, echo = FALSE, results = hide>>=
-small <- sum(dat$esComp[!is.na(dat$esComp)] < .1) / length(dat$esComp[!is.na(dat$esComp)]) * 100
-medium <- sum(dat$esComp[!is.na(dat$esComp)] >= .1 & dat$esComp[!is.na(dat$esComp)] < .25) / length(dat$esComp[!is.na(dat$esComp)]) * 100
-large <- sum(dat$esComp[!is.na(dat$esComp)] >= .25 & dat$esComp[!is.na(dat$esComp)] < .4) / length(dat$esComp[!is.na(dat$esComp)]) * 100
-larger <- sum(dat$esComp[!is.na(dat$esComp)] >= .4) / length(dat$esComp[!is.na(dat$esComp)]) * 100
-@
+small <- sum(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] < .1) / length(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))]) * 100
+medium <- sum(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] >= .1 & sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] < .25) / length(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))]) * 100
+large <- sum(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] >= .25 & sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] < .4) / length(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))]) * 100
+larger <- sum(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] >= .4) / length(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))]) * 100
 
-Figure \ref{fig:fig1} shows the distribution of observed effect sizes (in $|\eta|$) across all articles and indicates that, of the 223,082 observed effects, \Sexpr{round(small, 0)}\% were zero to small (i.e., $0\leq|\eta|<.1$), \Sexpr{round(medium, 0)}\% were small to medium (i.e., $.1\leq|\eta|<.25$), \Sexpr{round(large, 0)}\% medium to large (i.e., $.25\leq|\eta|<.4$), and \Sexpr{round(larger, 0)}\% large or larger (i.e., $|\eta|\geq.4$; \cite{Cohen1988-wg}).
-This suggests that the majority of effects reported in psychology is medium or smaller (i.e., \Sexpr{round(medium+small,0)}\%).
-Of the full set of 223,082 test results, 54,595 (24.5\%) were nonsiginificant, which is the dataset for our main analyses.
+if(!file.exists(sprintf('%sfigures/Fig1.pdf', run)))
+{
+  pdf(sprintf('%sfigures/Fig1.pdf', run), width=11, height=7)
 
-\begin{figure}
-\begin{center}
-<<label=fig1,fig=TRUE,echo=FALSE>>=
-# par(mai = c(1, 1, .2, .2))
-
-plot(density(dat$esComp[!is.na(dat$esComp)]),
+  par(mai = c(1, 1, .2, .2))
+  plot(density(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))]),
        lty = 1,
@@
        ylab = "Density",
-     cex.axis = .8,
-     cex.lab = 1,
+       cex.axis = 1.5,
+       cex.lab = 1.5,
        col = "black", las = 1, bty = 'n')
   abline(v = c(.1, .25, .4), lty = 2, col = "grey")
-t1 <- sum(dat$esComp[!is.na(dat$esComp)] < .1) / length(dat$esComp[!is.na(dat$esComp)])
-t2 <- sum(dat$esComp[!is.na(dat$esComp)] >= .1 & dat$esComp[!is.na(dat$esComp)] < .25) / length(dat$esComp[!is.na(dat$esComp)])
-t3 <- sum(dat$esComp[!is.na(dat$esComp)] >= .25 & dat$esComp[!is.na(dat$esComp)] < .4) / length(dat$esComp[!is.na(dat$esComp)])
-t4 <- sum(dat$esComp[!is.na(dat$esComp)] >= .4) / length(dat$esComp[!is.na(dat$esComp)])
+  t1 <- sum(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] < .1) / length(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))])
+  t2 <- sum(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] >= .1 & sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] < .25) / length(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))])
+  t3 <- sum(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] >= .25 & sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] < .4) / length(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))])
+  t4 <- sum(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] >= .4) / length(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))])
   text(x = .1 / 2, y = .15, labels = round(t1, 2), cex = 1)
@@
   text(x = ((1 - .4) / 2) + .4, y = .15, labels = round(t4, 2), cex = 1)
-@
-\end{center}
-\caption{Density of observed effect sizes of results reported in eight psychology journals, with \Sexpr{round(small, 0)}\% of effects in the category none-small, \Sexpr{round(medium, 0)}\% small-medium, \Sexpr{round(large, 0)}\% medium-large, and \Sexpr{round(larger, 0)}\% beyond large.}
-\label{fig:fig1}
-\end{figure}
+  dev.off()
+}
 
-Our dataset indicated that more nonsignificant results are reported throughout the years, strengthening the case for inspecting potential false negatives.
-The proportion of nonsignificant results showed an upward trend, as depicted in Figure 4, from approximately 20\% to approximately 30\% of all reported APA results.
-
-\begin{figure}
-\begin{center}
-<<label=fig2,fig=TRUE,echo=FALSE>>=
-# par(mai = c(1, 1, .2, .2))
+if(!file.exists(sprintf('%sfigures/Fig2.pdf', run)))
+{
+  pdf(sprintf('%sfigures/Fig2.pdf', run), width=11, height=7)
+  par(mai = c(1, 1, .2, .2))
   # nonsignificant proportion p/year
@@
        nsigtemp,
-     ylim = c(0, .4),
+       ylim = c(0, .4), xlim = c(1985, 2014),
        type = 'o',
        xlab = "Year", ylab = 'Proportion nonsignificant',
-     yaxs = 'i',
-     cex.axis = 1, las = 1, bty = 'n')
-# abline(lm(nsigtemp ~ c(1985:2013)), lty = 2)
+       yaxs = 'i', xaxt = 'n',
+       cex.axis = 1.5, cex.lab = 1.5, las = 1, bty = 'n')
+  axis(1, at=c(seq(1985, 2010, 5), 2013), labels = c(seq(1985, 2010, 5), 2013), col.axis="black",
+       cex.axis = 1.5)
+  dev.off()
+}
+@
 
-@
+Figure \ref{fig:fig1} shows the distribution of observed effect sizes (in $|\eta|$) across all articles and indicates that, of the 223,082 observed effects, \Sexpr{round(small, 0)}\% were zero to small (i.e., $0\leq|\eta|<.1$), \Sexpr{round(medium, 0)}\% were small to medium (i.e., $.1\leq|\eta|<.25$), \Sexpr{round(large, 0)}\% medium to large (i.e., $.25\leq|\eta|<.4$), and \Sexpr{round(larger, 0)}\% large or larger (i.e., $|\eta|\geq.4$; \cite{Cohen1988-wg}).
+This suggests that the majority of effects reported in psychology is medium or smaller (i.e., \Sexpr{round(medium+small,0)}\%), which is somewhat in line with a previous study on effect distributions \cite{Gignac2016-je}.
+Of the full set of 223,082 test results, 54,595 (24.5\%) were nonsiginificant, which is the dataset for our main analyses.
+
+\begin{figure}
+\begin{center}
+\includegraphics{../figures/Fig1.pdf}
+\end{center}
+\caption{Density of observed effect sizes of results reported in eight psychology journals, with \Sexpr{round(small, 0)}\% of effects in the category none-small, \Sexpr{round(medium, 0)}\% small-medium, \Sexpr{round(large, 0)}\% medium-large, and \Sexpr{round(larger, 0)}\% beyond large.}
+\label{fig:fig1}
+\end{figure}
+
+Our dataset indicated that more nonsignificant results are reported throughout the years, strengthening the case for inspecting potential false negatives.
+The proportion of reported nonsignificant results showed an upward trend, as depicted in Figure \ref{fig:fig2}, from approximately 20\% in the eighties to approximately 30\% of all reported APA results in 2015.
+
+\begin{figure}
+\begin{center}
+\includegraphics{../figures/Fig2.pdf}
 \end{center}
@@
 
-<<Simulating null distribution>>=
+<<Simulating null distribution, echo = FALSE, results = hide>>=
+if(file.exists(sprintf('%sdata/simNullEs', run)))
+{
+  load(sprintf('%sdata/simNullEs', run))
+} else
+{
   # takes some time to run these, have to simulate many values
@@
 
+  save(simNullEs, file = sprintf('%sdata/simNullEs', run))
+}
+
 temp <- ks.test(simNullEs$esComp,
@@
                 alternative="greater")
+
+if(!file.exists(sprintf('%sfigures/Fig3.pdf', run)))
+{
+  pdf(sprintf('%sfigures/Fig3.pdf', run), width=11, height=7)
+  par(mfrow = c(1,2), mai = c(1.2,1.2,.8,.5))
+  # Overall
+  plot(ecdf(na.omit(sqrt(simNullEs$esComp))),
+       lty = 1,
+       frame.plot = T, 
+       main = TeX(
+         sprintf(
+           "Unadjusted, $D=%s,p<2.2\\times 10^{-16}$", round(temp$statistic,2))),
+       xlim = c(0, 1),
+       xaxs = "i",
+       yaxs = "i",
+       xlab = TeX("Correlation (|$\\eta$|)"),
+       ylab = "Cumulative density",
+       cex.axis=.8,
+       cex.lab=1,
+       cex.main=1.5,
+       col = "grey", las=1)
+  lines(ecdf(na.omit(sqrt(dat$esComp[nsig]))))
+  legend(x = .6, y = .2, legend = c(TeX("$H_0$"), 'Observed'),
+         cex = 1, lty = c(1, 1),
+         col = c("grey", "black", 2),
+         box.lwd = 0, lwd = 2, bty = 'n')
+  for(es in esR){
+    h0horiz <- sum(sqrt(simNullEs$esComp[!is.na(simNullEs$esComp)]) < es) / length(simNullEs$esComp[!is.na(simNullEs$esComp)])
+    clip(es, 1, 0, h0horiz)
+    abline(h = h0horiz, v = es, lty = 2, col = "grey")
+    clip(0, 1, 0, 1)
+    text(x = .9, y = h0horiz - .02, labels = round(h0horiz, 2), cex = 1, col = 'darkgrey')
+    x <- sqrt(dat$esComp[nsig]) <= es
+    horiz <- sum(x[!is.na(x)]) / length(x[!is.na(x)])
+    text(x = .05, y = horiz + .02, labels = round(horiz, 2), cex = 1)
+    clip(0, es, 0, horiz)
+    abline(h = horiz, v = es, lty = 2, col = "black")
+    clip(0, 1, 0, 1)
+  }
+}
+
+temp <- ks.test(simNullEs$adjESComp,
+                dat$adjESComp[nsig],
+                alternative="greater")
+# Overall[adj]
+plot(ecdf(na.omit(sqrt(simNullEs$adjESComp))),
+     lty = 1,
+     frame.plot = T, 
+     main = TeX(
+       sprintf(
+         "Adjusted, $D=%s,p<2.2\\times 10^{-16}$", round(temp$statistic,2))),
+     xlim = c(0, 1),
+     xaxs = "i",
+     yaxs = "i",
+     xlab = TeX("Correlation (|$\\eta$|)"),
+     ylab = "Cumulative density",
+     cex.axis = .8,
+     cex.lab = 1,
+     cex.main = 1.5,
+     col = "grey", las = 1)
+lines(ecdf(na.omit(sqrt(dat$adjESComp[nsig]))))
+legend(x = .6,y = .2,legend = c(TeX("$H_0$"), 'Observed'),
+       cex = 1,lty = c(1, 1),
+       col = c("grey", "black", 2), box.lwd = 0, lwd = 2, bty = 'n')
+for(es in esR){
+  h0horiz <- sum(sqrt(simNullEs$adjESComp[!is.na(simNullEs$adjESComp)]) < es) / length(simNullEs$adjESComp[!is.na(simNullEs$adjESComp)])
+  clip(es, 1, 0, h0horiz)
+  abline(h = h0horiz, v = es, lty = 2, col = "grey")
+  clip(0, 1, 0, 1)
+  text(x = .9, y = h0horiz - .02, labels = round(h0horiz, 2), cex = 1, col = 'darkgrey')
+  x <- sqrt(dat$adjESComp[nsig]) <= es
+  horiz <- sum(x[!is.na(x)]) / length(x[!is.na(x)])
+  text(x = .05, y = horiz + .02, labels = round(horiz, 2), cex = 1)
+  clip(0, es, 0, horiz)
+  abline(h = horiz, v = es, col = "black", lty = 2)
+  clip(0, 1, 0, 1)
+}
+dev.off()
+
+if(!file.exists(sprintf('%sfigures/S1Fig.pdf', run)))
+{
+  pdf(sprintf('%sfigures/S1Fig.pdf', run), onefile = TRUE, width = 11, height = 11)
+  par(mfrow = c(2, 2), mai = c(1.2, 1.2, .8, .5))
+
+  for(i in 1:4){
+    sel <- dat$journals.jour. == sort(unique(dat$journals.jour.))[i] & nsig
+    set.seed(i)
+    simNullEs <- simNullDist(dat, n.iter=length(dat$esComp[sel])*3, alpha = .05)
+    temp <- ks.test(simNullEs$esComp,
+                    dat$esComp[dat$journals.jour. == sort(unique(dat$journals.jour.))[i] & nsig],
+                    alternative = "greater")
+    print((temp))
+    if(i == 3){
+      plot(ecdf(na.omit(sqrt(simNullEs$esComp))),
+           lty = 1,
+           frame.plot = T, 
+           main = TeX(
+             sprintf("%s, D=%s, $p=7.934\\times 10^{-6}$",
+                     sort(unique(dat$journals.jour.))[i],
+                     round(temp$statistic,3))),
+           xlim = c(0,1),
+           xaxs = "i",
+           yaxs = "i",
+           xlab = TeX("Correlation (|$\\eta$|)"),
+           ylab = "Cumulative density",
+           cex.axis = .8,
+           cex.lab = 1,
+           cex.main = 1.5,
+           col = "grey", las = 1)
+    }
+    else{plot(ecdf(na.omit(sqrt(simNullEs$esComp))),
+              lty = 1,
+              frame.plot = T, 
+              main = TeX(
+                sprintf("%s, D=%s, $p=2.2\\times 10^{-16}$",
+                        sort(unique(dat$journals.jour.))[i],
+                        round(temp$statistic,3))),
+              xlim = c(0,1),
+              xaxs = "i",
+              yaxs = "i",
+              xlab = TeX("Correlation (|$\\eta$|)"),
+              ylab = "Cumulative density",
+              cex.axis = .8,
+              cex.lab = 1,
+              cex.main = 1.5,
+              col = "grey", las = 1)}
+    lines(ecdf(sqrt(dat$esComp[sel])),
+          lwd = .5)
+    legend(x = .6, y = .2, legend = c(TeX("$H_0$"), 'Observed'),
+           cex = 1.2, lty = c(1, 1),
+           col = c("grey", "black", 2), box.lwd = 0, lwd = 2, bty = 'n')
+    for(es in esR){
+      h0horiz <- sum(sqrt(simNullEs$esComp[!is.na(simNullEs$esComp)]) < es) / length(simNullEs$esComp[!is.na(simNullEs$esComp)])
+      clip(es, 1, 0, h0horiz)
+      abline(h = h0horiz, v = es, lty = 2, col = "grey")
+      clip(0, 1, 0, 1)
+      x <- sqrt(dat$esComp[sel]) <= es
+      horiz <- sum(x[!is.na(x)]) / length(x[!is.na(x)])
+      text(x = .05, y = horiz + .02, labels = round(horiz, 2), cex = 1.2)
+      text(x = .9, y = h0horiz - .02, labels = round(h0horiz, 2), cex = 1.2, col = 'darkgrey')
+      clip(0, es, 0, horiz)
+      abline(h = horiz, v = es, col = "black", lty = 2)
+      clip(0, 1, 0, 1)
+    }
+  }
+
+  for(i in 5:8){
+    sel <- dat$journals.jour. == sort(unique(dat$journals.jour.))[i] & nsig
+    set.seed(i)
+    simNullEs <- simNullDist(dat, n.iter=length(dat$esComp[sel])*3, alpha=.05)
+    temp <- ks.test(simNullEs$esComp,
+                    dat$esComp[dat$journals.jour. == sort(unique(dat$journals.jour.))[i] & nsig],
+                    alternative="greater")
+    print((temp))
+    plot(ecdf(na.omit(sqrt(simNullEs$esComp))),
+         lty = 1,
+         frame.plot = T, 
+         main = TeX(
+           sprintf("%s, D=%s, $p=2.2\\times 10^{-16}$",
+                   sort(unique(dat$journals.jour.))[i],
+                   round(temp$statistic,3))),
+         xlim = c(0, 1),
+         xaxs = "i",
+         yaxs = "i",
+         xlab = TeX("Correlation (|$\\eta$|)"),
+         ylab = "Cumulative density",
+         cex.axis = .8,
+         cex.lab = 1,
+         cex.main = 1.5,
+         col = "grey", las = 1)
+    lines(ecdf(sqrt(dat$esComp[sel])),
+          lwd = .5)
+    legend(x = .6,y = .2,legend = c(TeX("$H_0$"), 'Observed'),
+           cex = 1.2,lty = c(1, 1),
+           col = c("grey", "black", 2), box.lwd = 0 , lwd = 2, bty = 'n')
+    for(es in esR){
+      h0horiz <- sum(sqrt(simNullEs$esComp[!is.na(simNullEs$esComp)]) < es) / length(simNullEs$esComp[!is.na(simNullEs$esComp)])
+      clip(es, 1, 0, h0horiz)
+      abline(h = h0horiz, v = es, lty = 2, col = "grey")
+      clip(0, 1, 0, 1)
+      x <- sqrt(dat$esComp[sel]) <= es
+      horiz <- sum(x[!is.na(x)]) / length(x[!is.na(x)])
+      text(x = .05, y = horiz + .02, labels = round(horiz, 2), cex = 1.2)
+      text(x = .9, y = h0horiz - .02, labels = round(h0horiz, 2), cex = 1.2, col = 'darkgrey')
+      clip(0, es, 0, horiz)
+      abline(h = horiz, v = es, col = "black", lty = 2)
+      clip(0, 1, 0, 1)
+    }
+  }
+  dev.off()
+}
+
 @
 
-For the entire set of nonsignificant results across journals, Figure 5 indicates that there is substantial evidence of false negatives.
-Under $H_0$, 46\% of all observed effects is expected to be within the range $0\geq|\eta|<.1$, as can be seen in the left panel of Figure 5 highlighted by the lowest grey line.
+For the entire set of nonsignificant results across journals, Figure \ref{fig:fig3} indicates that there is substantial evidence of false negatives.
+Under $H_0$, 46\% of all observed effects is expected to be within the range $0\leq|\eta|<.1$, as can be seen in the left panel of Figure \ref{fig:fig3} highlighted by the lowest grey line.
 However, of the observed effects, only 26\% fall within this range, as highlighted by the lowest black line.
-Similarly, we would expect 85\% of all effect sizes to be within the range $0\geq|\eta|<.25$ (middle grey line), but we observed 14 percentage points less in this range (i.e., 71\%; middle black line); 96\% is expected for the range $0\geq|\eta|<.4$ (top grey line), but we observed 4 percentage points less (i.e., 92\%; top black line).
-These differences indicate that larger effects are observed in the nonsignificant results than expected under a null effect.
-This indicates the presence of false negatives, which is confirmed by the Kolmogorov-Smirnov test, $D=.23$, $p<.000000000000001$.
-Results were similar when the nonsignificant effects were considered separately for the eight journals, although deviations were smaller for the Journal of Applied Psychology (see Figure S1 for results per journal).
+Similarly, we would expect 85\% of all effect sizes to be within the range $0\leq|\eta|<.25$ (middle grey line), but we observed 14 percentage points less in this range (i.e., 71\%; middle black line); 96\% is expected for the range $0\leq|\eta|<.4$ (top grey line), but we observed 4 percentage points less (i.e., 92\%; top black line).
+These differences indicate that larger nonsignificant effects are reported in papers than expected under a null effect.
+This indicates the presence of false negatives, which is confirmed by the Kolmogorov-Smirnov test, $D=\Sexpr{round(temp$statistic, 2)}$, $p<.000000000000001$.
+Results were similar when the nonsignificant effects were considered separately for the eight journals, although deviations were smaller for the Journal of Applied Psychology (see \href{../figures/S1Fig}{Figure S1} for results per journal).
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{../figures/Fig3.pdf}
+\end{center}
+\caption{Observed and expected (adjusted and unadjusted) effect size distribution for statistically nonsignificant APA results reported in eight psychology journals.
+The three vertical dotted lines correspond to a small, medium, large effect, respectively.
+Legenda includes Kolmogorov-Smirnov test results.}
+\label{fig:fig3}
+\end{figure}
+
+Because effect sizes and their distribution overestimate population effect size, particularly when sample size is small \cite{Voelkle2007-at,Hedges1981-og}, we also compared the observed and expected adjusted nonsignificant effect sizes (right panel of Figure \ref{fig:fig3}).
+Unsurprisingly, the distribution of adjusted effect sizes of nonsignificant results tells the same story; observed effect sizes are larger than expected effect sizes.
+For instance, the distribution of adjusted reported effect size suggests 49\% of effect sizes are at least small, whereas under the $H_0$ only 22\% is expected.
+
+\subsubsection*{Evidence of false negatives in articles.}
+
+<<Paper level application, echo = FALSE, results = hide>>=
+# Computing the Fisher Tests
+if(!file.exists(sprintf('%sdata/fishRes', run)))
+{
+  fishRes <- FisherMethod(dat$Computed, as.character(dat$Source))
+  save(fishRes, file = sprintf('%sdata/fishRes', run))
+} else
+{
+  load(sprintf('%sdata/fishRes', run))
+}
+
+if(!file.exists(sprintf('%sdata/fishDF', run)))
+{
+  # Get vector to identify which papers are from which journal
+  sourcejour <- NULL
+  for(i in 1:length(unique(dat$Source))){
+    sourcejour[i] <- unique(dat$journals.jour.[dat$Source==unique(dat$Source)[i]])
+  }
+
+  years <- NULL
+  for(i in 1:length(sort(unique(dat$Source)))){
+    sel <- dat$Source == sort(unique(dat$Source))[i]
+    years[i] <- unique(dat$years.y.[sel])
+    print(i)
+  }
+
+  # Make vector of sig/nsig/na 
+  fishDF <- data.frame(FisherP=fishRes$PFish, journal=sourcejour, kRes=fishRes$CountNSig, year=years)
+
+  save(fishDF, file = sprintf('%sdata/fishDF', run))
+} else
+{
+  load(sprintf('%sdata/fishDF', run))
+}
+
+alphaF <- 0.10
+# Compute amount of papers and proportion of sig/nsig/NA Fisher Method tests
+final <- NULL
+kLen <- c(1, 2, 3, 4, 5, 10, 20)
+
+for(journals in sort(unique(dat$journals.jour.))){
+  sel <- fishDF$journal == journals
+
+  # Amount of papers in a journal
+  amount <- length(fishDF$FisherP[sel])
+  # Proportion of significant fisher results
+  amountSig <- sum(fishDF$FisherP[sel & !is.na(fishDF$FisherP)] < alphaF)
+
+  # Amount of papers in a journal without significant results
+  countNA <- sum(is.na(fishDF$FisherP[sel]))
+  journalSet <- NULL  
+  # Writing out the results
+  for(k in 1:length(kLen)){
+    if(k == 7){
+      x <- sum(fishDF$FisherP[sel & !is.na(fishDF$FisherP) & fishDF$kRes >= kLen[k]] < alphaF) / length(fishDF$FisherP[sel  & fishDF$kRes >= kLen[k]])
+      journalSet <- cbind(journalSet, x)
+    }
+    else if(k == 5 | k ==6){
+      x <- sum(fishDF$FisherP[sel & !is.na(fishDF$FisherP) & fishDF$kRes >= kLen[k]& fishDF$kRes < kLen[k+1]] < alphaF) / length(fishDF$FisherP[sel & fishDF$kRes >= kLen[k]& fishDF$kRes < kLen[k+1]])
+      journalSet <- cbind(journalSet, x)
+    } else{
+      x <- sum(fishDF$FisherP[sel & !is.na(fishDF$FisherP) & fishDF$kRes == kLen[k]] < alphaF) / length(fishDF$FisherP[sel & fishDF$kRes == kLen[k]])
+      journalSet <- cbind(journalSet, x)}
+  }
+  temp <- cbind(journals,
+                journalSet,
+                amountSig / amount,
+                countNA,
+                amountSig,
+                amount)
+  # This is the result that goes into the table
+  final <- rbind(final, temp)
+}
+temp <- "Overall"
+for(i in 1:length(kLen)){
+  if(i == 7){
+    temp[i+1] <- sum(fishDF$FisherP[fishDF$kRes >= kLen[i] & !is.na(fishDF$FisherP)] < alphaF )/ length(fishDF$FisherP[fishDF$kRes >= kLen[i]])
+  }
+  else if(i == 5|i == 6){
+    temp[i+1] <- sum(fishDF$FisherP[fishDF$kRes >= kLen[i] &fishDF$kRes < kLen[i+1] & !is.na(fishDF$FisherP)] < alphaF )/ length(fishDF$FisherP[fishDF$kRes >= kLen[i] & fishDF$kRes < kLen[i+1]])
+  }
+  else{
+    temp[i+1] <- sum(fishDF$FisherP[fishDF$kRes == kLen[i] & !is.na(fishDF$FisherP)] < alphaF )/ length(fishDF$FisherP[fishDF$kRes == kLen[i]])  
+  }
+
+}
+temp <- c(temp,
+          sum(as.numeric(as.character(final[,dim(final)[2]-1])))/sum(as.numeric(as.character(final[,dim(final)[2]]))),
+          sum(as.numeric(as.character(final[,dim(final)[2]-2]))),
+          sum(as.numeric(as.character(final[,dim(final)[2]-1]))),
+          sum(as.numeric(as.character(final[,dim(final)[2]]))))
+final <- rbind(as.character(temp), final)
+final <- as.data.frame(final)
+
+names(final) <- c('journals', paste0('k', kLen), 'overall', 'countNA', 'amountSig', 'nrpapers')
+# write.csv(final, 'table4.csv', row.names=F)
+
+# Overall
+table(fishDF$kRes)
+# Per journal
+table(fishDF$kRes[fishDF$journal=="DP"])
+table(fishDF$kRes[fishDF$journal=="FP"])
+table(fishDF$kRes[fishDF$journal=="JAP"])
+table(fishDF$kRes[fishDF$journal=="JCCP"])
+table(fishDF$kRes[fishDF$journal=="JEPG"])
+table(fishDF$kRes[fishDF$journal=="JPSP"])
+table(fishDF$kRes[fishDF$journal=="PLOS"])
+table(fishDF$kRes[fishDF$journal=="PS"])
+
+# Median per journal
+x = as.numeric(as.character(final$amountSig)) / (as.numeric(as.character(final$nrpapers)) - as.numeric(as.character(final$countNA)))
+y = c(median(fishDF$kRes[fishDF$journal=="DP"]),
+      median(fishDF$kRes[fishDF$journal=="FP"]),
+      median(fishDF$kRes[fishDF$journal=="JAP"]),
+      median(fishDF$kRes[fishDF$journal=="JCCP"]),
+      median(fishDF$kRes[fishDF$journal=="JEPG"]),
+      median(fishDF$kRes[fishDF$journal=="JPSP"]),
+      median(fishDF$kRes[fishDF$journal=="PLOS"]),
+      median(fishDF$kRes[fishDF$journal=="PS"]))
+cor(x[-1], y)
+
+# Computing the number of significant Fisher results per year
+# As proportion of all papers reporting nonsignificant results
+fishDF$logicalP <- ifelse(fishDF$FisherP < .1, 1, 0)
+fisherYear <- ddply(fishDF, .(year), summarise, propYear=mean(logicalP, na.rm=TRUE))
+
+knsYear <- ddply(fishDF, .(year), summarise, kYear=mean(kRes, na.rm=TRUE))
+pmeanYear <- ddply(dat[dat$Reported.Comparison == '=' & dat$Reported.P.Value > .05, ],
+                   .(years.y.), summarise, pYear=mean(Reported.P.Value, na.rm=TRUE))
+
+esYear <- ddply(dat[dat$Reported.Comparison == '=' & dat$Reported.P.Value > .05, ],
+                .(years.y.), summarise, esYear=mean(esComp, na.rm=TRUE))
+
+mydf <- data.frame(x = fisherYear$year,
+                   y = fisherYear$propYear,
+                   count = knsYear$kYear)
+
+mydf
+
+if(!file.exists(sprintf('%sfigures/Fig4.pdf', run)))
+{
+  ggplot(mydf, aes(x = x, y = y)) + geom_point(aes(size = count)) + ylim(0, 1) + geom_smooth(method="lm") +
+    xlab("Year") + ylab("Proportion significant Fisher results")
+
+  ggsave(filename = sprintf('%sfigures/Fig4.pdf', run), plot = last_plot(), width = 7, height = 5)
+}
+
+# sample size development over time
+medianN <- NULL
+p25 <- NULL
+p75 <- NULL
+i <- 1
+for(y in 1985:2013){
+  temp <- summary(dat$df2[dat$years.y. == y])
+
+  medianN[i] <- temp[3]
+  p25[i] <- temp[2]
+  p75[i] <- temp[5]
+
+  i <- i + 1
+}
+
+if(!file.exists(sprintf('%sfigures/Fig5.pdf', run)))
+{
+  pdf(sprintf('%sfigures/Fig5.pdf', run), width=7, height=6)
+  par(mar = c(4, 4, .2, 2))
+  plot(x=1985:2013, y=medianN, type='o', col="black",
+       ylab="Degrees of freedom", xlab="Year",
+       xlim = c(1985, 2015), 
+       ylim=c(0,150), cex.lab=1.2, las=1, lwd=1, cex.axis=1.2, xaxs='i',
+       yaxs='i',
+       bty = 'n')
+  lines(x=1985:2013, y=p25, type='o', col='grey')
+  lines(x=1985:2013, y=p75, type='o', col='grey')
+  text(y = 100, x = 2010, "P75", col = "grey")
+  text(y = 50, x = 2010, "P50", col = "black")
+  text(y = 22, x = 2010, "P25", col = "grey")
+  dev.off()
+}
+@
+
+The Fisher test was applied to the nonsignificant test results of each of the 14,765 papers separately, to inspect whether $p$-values within a paper deviate from what can be expected under the $H_0$.
+Table \ref{tab:tab4} shows the number of papers with evidence for false negatives, specified per journal and per $k$ number of nonsignificant test results.
+The first row indicates the number of papers that report no nonsignificant results.
+Overall results (last row) indicate that 47.1\% of all articles show evidence of false negatives (i.e.
+6,951 articles), and 66.7\% of articles reporting at least one result.
+
+%Sorry, this table was manually done prior to Sweave. Manually check with code in above chunk
+\begin{table}[htbp]
+\caption{Summary table of Fisher test results applied to the nonsignificant results ($k$) of each article separately, overall and specified per journal.
+A significant Fisher test result is indicative of a false negative (FN).
+DP = Developmental Psychology; FP = Frontiers in Psychology; JAP = Journal of Applied Psychology; JCCP = Journal of Consulting and Clinical Psychology; JEPG = Journal of Experimental Psychology: General; JPSP = Journal of Personality and Social Psychology; PLOS = Public Library of Science; PS = Psychological Science.}
+\rowcolors{2}{gray!25}{white}
+\begin{adjustbox}{width=\textwidth,totalheight=\textheight,keepaspectratio,angle=0}
+\centering
+\begin{tabular}{lllllllllll}
+ &  & Overall             & DP                & FP     & JAP    & JCCP   & JEPG   & JPSP   & PLOS   & PS \\
+\hline
+& Nr. of papers     & 14,765  & 2,283   & 614    & 1,239   & 2,039   & 772    & 4,087   & 2,166   & 1,565   \\
+$k=0$               & Count             & 4,340   & 758    & 133    & 488    & 907    & 122    & 840    & 565    & 527    \\
+& \%                & 29.4\% & 33.2\% & 21.7\% & 39.4\% & 44.5\% & 15.8\% & 20.6\% & 26.1\% & 33.7\% \\
+\hline
+$k=1$               & Evidence FN       & 57.7\% & 66.1\% & 41.2\% & 48.7\% & 58.7\% & 51.4\% & 66.0\% & 47.2\% & 56.4\% \\
+& Count             & 2,510   & 433    & 102    & 238    & 380    & 109    & 556    & 339    & 353    \\
+$k=2$               & Evidence FN       & 60.6\% & 66.9\% & 50.0\% & 36.3\% & 57.7\% & 66.7\% & 75.2\% & 51.6\% & 57.1\% \\
+& Count             & 1,768   & 293    & 64     & 157    & 227    & 81     & 424    & 289    & 233    \\
+$k=3$               & Evidence FN       & 65.3\% & 69.8\% & 57.6\% & 53.1\% & 54.4\% & 77.1\% & 80.6\% & 47.8\% & 60.2\% \\
+& Count             & 1,257   & 199    & 66     & 98     & 125    & 83     & 341    & 184    & 161    \\
+$k=4$               & Evidence FN       & 68.7\% & 75.0\% & 63.8\% & 53.1\% & 69.7\% & 67.9\% & 81.4\% & 52.7\% & 62.5\% \\
+& Count             & 892    & 128    & 47     & 64     & 89     & 56     & 264    & 148    & 96     \\
+$5\leq k<10$  & Evidence FN       & 72.3\% & 71.2\% & 67.7\% & 56.7\% & 66.3\% & 71.2\% & 87.1\% & 52.4\% & 63.0\% \\
+& Count             & 2,394   & 326    & 124    & 134    & 208    & 163    & 898    & 368    & 173    \\
+$10\leq k<20$ & Evidence FN       & 77.7\% & 76.9\% & 67.7\% & 60.0\% & 72.4\% & 81.2\% & 88.1\% & 57.3\% & 81.0\% \\
+& Count             & 1,280   & 121    & 65     & 55     & 87     & 117    & 596    & 218    & 21     \\
+$k\geq20$              & Evidence FN       & 84.0\% & 76.0\% & 53.8\% & 60.0\% & 87.5\% & 80.5\% & 94.0\% & 69.1\% & 0.0\%  \\
+& Count             & 324    & 25     & 13     & 5      & 16     & 41     & 168    & 55     & 1      \\
+\hline
+All                 & Evidence FN       & 47.1\% & 46.5\% & 45.1\% & 29.9\% & 34.3\% & 59.1\% & 64.6\% & 38.4\% & 39.3\% \\
+& Evidence FN $k\geq1$ & 66.7\% & 69.6\% & 57.6\% & 49.4\% & 61.7\% & 70.2\% & 81.3\% & 51.9\% & 59.2\% \\
+& Count             & 6,951   & 1,061   & 277    & 371    & 699    & 456    & 2,641   & 831    & 615   \\
+\hline
+\end{tabular}
+\end{adjustbox}
+\label{tab:tab4}
+\end{table}
+
+Table \ref{tab:tab4} also shows evidence of false negatives for each of the eight journals.
+The lowest proportion of articles with evidence of at least one false negative was for the Journal of Applied Psychology (49.4\%; penultimate row).
+The remaining journals show higher proportions, with a maximum of 81.3\% (Journal of Personality and Social Psychology).
+Researchers should thus be wary to interpret negative results in journal articles as a sign that there is no effect; at least half of the papers provide evidence for at least one false negative finding.
+
+As would be expected, we found a higher proportion of articles with evidence of at least one false negative for higher numbers of statistically nonsignificant results ($k$; see Table \ref{tab:tab4}).
+For instance, 84\% of all papers that report more than 20 nonsignificant results show evidence for false negatives, whereas 57.7\% of all papers with only 1 nonsignificant result show evidence for false negatives.
+Consequently, we observe that journals with articles containing a higher number of nonsignificant results, such as JPSP, have a higher proportion of articles with evidence of false negatives.
+
+We also checked whether evidence of at least one false negative at the article level changed over time.
+Figure \ref{fig:fig4} depicts evidence across all articles per year, as a function of time (1985-2013); point size in the figure corresponds to the mean number of nonsignificant results per article (mean $k$) in that year.
+Interestingly, the proportion of articles with evidence for false negatives decreased from \Sexpr{round(mydf$y[1]*100, 0)}\% in 1985 to \Sexpr{round(mydf$y[29]*100, 0)}\% in 2013, despite the increase in mean $k$ (from \Sexpr{round(mydf$count[1], 2)} in 1985 to \Sexpr{round(mydf$y[29], 2)} in 2013).
+This decreasing evidence over time cannot be explained by a decrease in sample size over time, as sample size in psychology articles has stayed stable across time (see Figure \ref{fig:fig5}).
+One (partial) explanation of this surprising result is that in the early days researchers primarily used to report more APA results with 'marginally significant' $p$-values (i.e., $p$-values slightly larger than .05), compared to nowadays.
+This explanation is supported by both a smaller number of reported APA results in the past and the smaller mean reported nonsignificant $p$-value (\Sexpr{round(mean(dat$Reported.P.Value[dat$Reported.Comparison == '=' & dat$years.y.
+== 1985 & dat$Reported.P.Value > .05]), 3)} in 1985, \Sexpr{round(mean(dat$Reported.P.Value[dat$Reported.Comparison == '=' & dat$years.y.
+== 2013 & dat$Reported.P.Value > .05]), 3)} in 2013).
+We do not know whether these marginally significant $p$-values were interpreted as evidence in favor of a finding (or not) and how these interpretations changed over time.
+Another potential explanation is that the effect sizes being studied have become smaller over time (mean effect $r$ \Sexpr{round(mean(sqrt(dat$esComp[dat$Reported.Comparison == '=' & dat$years.y.
+== 1985 & dat$Reported.P.Value > .05])), 3)} in 1985, \Sexpr{round(mean(sqrt(dat$esComp[dat$Reported.Comparison == '=' & dat$years.y.
+== 2013 & dat$Reported.P.Value > .05])), 3)} in 2013), which results in both higher $p$-values over time and lower power of the Fisher test.
+Using the data at hand, we cannot distinguish between the two explanations.
+
+\begin{figure}
+\begin{center}
+\includegraphics{../figures/Fig4.pdf}
+\end{center}
+\caption{Proportion of papers reporting nonsignificant results in a given year, showing evidence for false negative results.
+Larger point size indicates a higher mean number of nonsignificant results reported in that year.}
+\label{fig:fig4}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics{../figures/Fig5.pdf}
+\end{center}
+\caption{Sample size development in psychology throughout 1985-2013, based on degrees of freedom across 258,050 test results.
+P25 = 25th percentile.
+P50 = 50th percentile (i.e., median).
+P75 = 75th percentile.}
+\label{fig:fig5}
+\end{figure}
+
+\subsection*{Discussion}
+
+The result that 2 out of 3 papers containing nonsignificant results show evidence of at least one false negative empirically verifies previously voiced concerns about insufficient attention for false negatives \cite{Fiedler2012-gx}.
+The Fisher test proved a powerful test to inspect for false negatives in our simulation study, where three nonsignificant results already results in high power to detect evidence of a false negative if sample size is at least 33 per result and the population effect is medium.
+Journals differed in the proportion of papers that showed evidence of false negatives, but this was largely due to differences in the amount of nonsignificant results reported.
+More generally, we observed that more nonsignificant results were reported in 2013 than in 1985.
+
+The repeated concern about power and false negatives throughout the last decades seems not to have trickled down into substantial change in psychology research practice.
+Cohen \cite{Cohen1962-jc} and Sedlmeier and Gigerenzer \cite{Sedlmeier1989-yc} already voiced concern decades ago and showed that power in psychology was low.
+Fiedler et al.
+\cite{Fiedler2012-gx} contended that false negatives are harder to detect in the current scientific system and therefore warrant more concern.
+Despite recommendations of increasing power by increasing sample size, we found no evidence for increased sample size (see Figure \ref{fig:fig5}).
+To the contrary, the data indicate that sample sizes have been remarkably stable since 1985, despite the improved ease of collecting participants with data collection tools such as online services.
+
+However, what has changed is the amount of nonsignificant results reported in the literature.
+Our data show that more nonsignificant results are reported throughout the years (see Figure \ref{fig:fig2}), which seems contrary to findings that indicate that relatively more significant results are being reported \cite{Fanelli2011-xa, Sterling1995-fe, Sterling1959-pf,De_Winter2015-ru}.
+It would seem the field is not shying away from publishing negative results per se, as proposed before \cite{Fanelli2011-xa,Greenwald1975-ck,Nosek2012-aw,Rosenthal1979-lx,Schimmack2012-du}, but whether this is also the case for results relating to hypotheses of explicit interest in a study and not all results reported in a paper, requires further research.
+Other research strongly suggests that most reported results relating to hypotheses of explicit interest are statistically significant \cite{Open_Science_Collaboration2015-zs}.
 
@@
 
+In order to illustrate the practical value of the Fisher test to test for evidential value of (non)significant $p$-values, we investigated gender related effects in a random subsample of our database.
+Gender effects are particularly interesting because gender is typically a control variable and not the primary focus of studies.
+Hence, we expect little $p$-hacking and substantial evidence of false negatives in reported gender effects in psychology.
+We apply the Fisher test to significant and nonsignificant gender results to test for evidential value \cite{Van_Assen2015-gg,Simonsohn2014-dm}.
+More precisely, we investigate whether evidential value depends on whether the result is statistically significant or not, and whether the results were in line with expectations expressed in the paper, or not.
+
+\subsection*{Method}
+
+We planned to test for evidential value in six categories (expectation [3 levels] $\times$ significance [2 levels]).
+Expectations were specified as '$H_1$ expected', '$H_0$ expected', or 'no expectation'.
+Prior to data collection, we assessed the required sample size for the Fisher test based on research on the gender similarities hypothesis \cite{Hyde2005-gj}.
+We calculated that the required number of statistical results for the Fisher test, given $r=.11$ \cite{Hyde2005-gj} and 80\% power, is 15 $p$-values per condition, requiring 90 results in total.
+.
+However, the six categories are unlikely to occur equally throughout the literature, hence we sampled 90 significant and 90 nonsignificant results pertaining to gender, with an expected cell size of 30 if results are equally distributed across the six cells of our design.
+Significance was coded based on the reported $p$-value, where $\leq.05$ was used as the decision criterion to determine significance \cite{Nuijten2015-od}.
+
+We sampled the 180 gender results from our database of over 250,000 test results in four steps.
+First, we automatically searched for "gender", "sex", "female" AND "male", " man" AND " woman" [sic], or " men" AND " women" [sic] in the $100$ characters before the statistical result and $100$ after the statistical result (i.e., range of $200$ characters surrounding the result), which yielded 27,523 results.
+Second, the first author inspected $500$ characters before and after the first result of a randomly ordered list of all 27,523 results and coded whether it indeed pertained to gender.
+This was done until 180 results pertaining to gender were retrieved from 180 different articles.
+Third, these results were independently coded by all authors with respect to the expectations of the original researcher(s) (coding scheme available at \url{osf.io/9ev63}).
+The coding included checks for qualifiers pertaining to the expectation of the statistical result (confirmed/theorized/hypothesized/expected/etc.).
+If researchers reported such a qualifier, we assumed they correctly represented these expectations with respect to the statistical significance of the result.
+For example, if the text stated "as expected no evidence for an effect was found, $t(12)=1, p=.337$" we assumed the authors expected a nonsignificant result.
+Fourth, discrepant codings were resolved by discussion (25 cases [13.9\%]; two cases remained unresolved and were dropped).
+178 valid results remained for analysis.
+
+Prior to analyzing these 178 $p$-values for evidential value with the Fisher test, we transformed them to variables ranging from 0 to 1.
+Statistically nonsignificant results were transformed with Equation \ref{pistar}; statistically significant $p$-values were divided by alpha (.05; \cite{Van_Assen2015-gg,Simonsohn2014-dm}).
+
+\subsection*{Results}
+
+<<gender, echo = FALSE, results = hide>>=
+# 27,523 gender results
+# manually extracted from datafilegender500_post.csv
+# number of rows (take into account header row)
+
+# gender effect evaluated -------------------------------------------------
+
+gend <- read.csv2(sprintf('%sdata/gendercoded cleaned and discussed.csv', run), sep = ";", dec = ".", header = TRUE)
+
+# 1 = null expected
+# 2 = effect expected
+# 3 = no expectation
+table(gend$significance, gend$final_code)
+
+options(scipen = 5, digits = 8)
+# sel <- gend$significance == "significant" & gend$final_code == "no expectation"
+for(sig in unique(gend$significance)){
+  for(code in unique(gend$final_code[!is.na(gend$final_code)])){
+    sel <- gend$significance == sig & gend$final_code == code
+
+    if(sig == "significant"){
+      temp <- gend$Computed[sel] / .05
+      pstar <- temp[!is.na(temp)]
+      x$CountNSig <- length(pstar)
+      x$Fish <- -2*sum(log(pstar))
+      x$PFish <- pchisq(x$Fish, df = 2 * length(pstar), lower.tail = FALSE)
+    }
+    if(sig == "nonsignificant"){
+      x <- (FisherMethod(x = gend$Computed[sel], id = 1, alpha = 0.05))
+    }
+
+    cat(sprintf("For %s %s, k = %s, chi2 = %s, p = %s\n", sig, code, x$CountNSig, x$Fish, x$PFish))
+  }
+}
+
+if(!file.exists(sprintf('%sfigures/Fig6.pdf', run)))
+{
+
+    ggplot(gend, aes(x = Computed, fill = significance)) + 
+    geom_density(alpha = .3) + 
+    xlab(TeX("$P$-value")) + 
+    ylab("Density")
+  ggsave(filename = sprintf('%sfigures/Fig6.pdf', run), plot = last_plot(), width = 7, height = 5)
+  }
+@
+
+The coding of the 178 results indicated that results rarely specify whether these are in line with the hypothesized effect (see Table \ref{tab:tab5}).
+For the 178 results, only 15 clearly stated whether their results were as expected, whereas the remaining 163 did not.
+Illustrative of the lack of clarity in expectations is the following quote: "\textit{As predicted, there was little gender difference [...] p < .06.}" As a result, the conditions significant-$H_0$ expected, nonsignificant-$H_0$ expected, and nonsignificant-$H_1$ expected contained too few results for meaningful investigation of evidential value (i.e., with sufficient statistical power).
+
+\begin{table}[htbp]
+\caption{Number of gender results coded per condition in a 2 (significance: significant or nonsignificant) by 3 (expectation: $H_0$ expected, $H_1$ expected, or no expectation) design.
+Cells printed in bold had sufficient results to inspect for evidential value.}
+\rowcolors{2}{gray!25}{white}
+% \begin{adjustbox}{width=\textwidth,totalheight=\textheight,keepaspectratio,angle=0}
+\centering
+\begin{tabular}{lrrr}
+& $H_0$ expected & $H_1$ expected & No expectation \\
+\hline
+Significant    & 0           & \textbf{12}          & \textbf{76}             \\
+Nonsignificant & 2           & 1           & \textbf{87}     \\
+\hline
+\end{tabular}
+% \end{adjustbox}
+\label{tab:tab5}
+\end{table}
+
+\begin{figure}
+\begin{center}
+\includegraphics{../figures/Fig6.pdf}
+\end{center}
+\caption{Probability density distributions of the $p$-values for gender effects, split for nonsignificant and significant results.
+A uniform density distribution indicates the absence of a true effect.}
+\label{fig:fig6}
+\end{figure}
+
+% these results are available in the code chunk above
+Figure \ref{fig:fig6} presents the distributions of both transformed significant and non-significant $p$-values.
+For significant results, applying the Fisher test to the $p$-values showed evidential value for a gender effect both when an effect was expected ($\chi^2(24)=358.725$, $p<.001$) and when no expectation was presented at all ($\chi^2(152)=1093.884$, $p<.001$).
+Similarly, applying the Fisher test to nonsignificant gender results without stated expectation yielded evidence of at least one false negative ($\chi^2(174)=324.374$, $p<.001$).
+Unfortunately we could not examine whether evidential value of gender effects is dependent on the hypothesis/expectation of the researcher, because these effects are most frequently reported without stated expectations.
+
+\subsection*{Discussion}
+
+We observed evidential value of gender effects both in the statistically significant (no expectation or $H_1$ expected) and nonsignificant results (no expectation).
+The data from the 178 results we investigated indicated that in only 15 cases the expectation of the test result was clearly explicated.
+This indicates that based on test results alone, it is very difficult to differentiate between results that relate to a priori hypotheses and results that are of an exploratory nature.
+The importance of being able to differentiate between confirmatory and exploratory results has been previously demonstrated \cite{Wagenmakers2012-jq} and has been incorporated into the Transparency and Openness Promotion guidelines (TOP; \cite{Nosek2015-nr}) with explicit attention paid to pre-registration.
+
 \section*{Application 3: Reproducibility Project Psychology}
+
+Out of the 100 replicated studies in the RPP, 64 did not yield a statistically significant effect sizee, despite the fact that high replication power was one of the aims of the project \cite{Open_Science_Collaboration2015-zs}.
+Regardless, the authors suggest "\textit{… that at least one replication could be a false negative}" (p.
+aac4716-4).
+Here we estimate how many of these nonsignificant replications might be false negative, by applying the Fisher test to these nonsignificant effects.
+
+\subsection*{Method}
+
+Of the 64 nonsignificant studies in the RPP data (\url{osf.io/fgjvw}), we selected the 63 nonsignificant studies with a test statistic.
+We first applied the Fisher test to the nonsignificant results, after transforming them to variables ranging from 0 to 1 using equations \ref{pistar} and \ref{fishertest}.
+Denote the value of this Fisher test by $Y$; note that under the $H_0$ of no evidential value $Y$ is $\chi^2$-distributed with 126 degrees of freedom.
+
+Subsequently, we hypothesized that $X$ out of these 63 nonsignificant results had a weak, medium, or strong population effect size (i.e., $\rho=.1$, $.3$, $.5$, respectively; \cite{Cohen1988-wg}) and the remaining $63-X$ had a zero population effect size.
+For each of these hypotheses, we generated 10,000 data sets (see next paragraph for details) and used them to approximate the distribution of the Fisher test statistic (i.e., $Y$).
+Using this distribution, we computed the probability that a $\chi^2$-value exceeds $Y$, further denoted by $p_Y$.
+We then used the inversion method \cite{Casella2002-cy} to compute confidence intervals of $X$, the number of nonzero effects.
+Specifically, the confidence interval for $X$ is ($X_{LB};X_{UB}$), where $X_{LB}$ is the value of $X$ for which $p_Y$ is closest to $.025$ and $X_{UB}$ is the value of $X$ for which $p_Y$ is closest to $.975$.
+We computed three confidence intervals of $X$: one for the number of weak, medium, and large effects.
+
+We computed $p_Y$ for a combination of a value of $X$ and a true effect size using 10,000 randomly generated datasets, in three steps. For each dataset we: 
+\begin{enumerate}
+\item Randomly selected $X$ out of 63 effects which are supposed to be generated by true nonzero effects, with the remaining $63-X$ supposed to be generated by true zero effects;
+\item Given the degrees of freedom of the effects, we randomly generated $p$-values under the $H_0$ using the central distributions and non-central distributions (for the $63-X$ and $X$ effects selected in step 1, respectively);
+\item The Fisher statistic $Y$ was computed by applying Equation \ref{fishertest} to the transformed $p$-values (see Equation \ref{pistar}) of step 2. 
+\end{enumerate}
+Probability $p_Y$ equals the proportion of 10,000 datasets with $Y$ exceeding the value of the Fisher statistic applied to the RPP data.
+See \url{osf.io/egnh9} for the analysis script to compute the confidence intervals of $X$.
+
+\subsection*{Results}
+
+<<rpp reanalysis, echo = FALSE, results = hide>>=
+# Read in Tilburg data
+if(!file.exists(sprintf('%sdata/rpp_data.csv', run)))
+{
+  info <- GET('https://osf.io/fgjvw/?action=download', write_disk(sprintf('%sdata/rpp_data.csv', run), overwrite = TRUE)) #downloads data file from the OSF
+}
+MASTER <- read.csv(sprintf("%sdata/rpp_data.csv", run))[1:167, ]
+colnames(MASTER)[1] <- "ID" # Change first column name to ID to be able to load .csv file
+
+# number of iterations per condition
+# if true probability is .025 or .975, then the SE = .00494 for n.iter = 1,000
+n.iter <- 10000
+# select only the available and nonsignificant replications
+# call this M
+M <- MASTER[MASTER$T_sign_R == 0 
+            & !is.na(MASTER$T_sign_R) 
+            & (MASTER$T_Test.Statistic..R. == 't'
+               | MASTER$T_Test.Statistic..R. == 'F'
+               | MASTER$T_Test.Statistic..R. == 'r'
+               | MASTER$T_Test.Statistic..R. == 'z'
+               | MASTER$T_Test.Statistic..R. == 'Chi2'), ]
+
+Fish_M <- FisherMethod(x = M$T_pval_USE..R.,
+                       id = 1,
+                       alpha = .05)
+
+if(!file.exists(sprintf('%sdata/res_application_3', run)))
+{
+
+  # alpha of the individual test
+  alpha <- .05
+  # vector of ES
+  es <- c(.1, .3, .5)
+
+  # set seed
+  set.seed(alpha * n.iter * sum(es))
+
+  # selectors for easy selection later on  
+  selr <- M$T_Test.Statistic..R. == 'r'
+  selz <- M$T_Test.Statistic..R. == 'z'
+  selChi2 <- M$T_Test.Statistic..R. == 'Chi2'
+
+  # ensure that we can easily compute the effect size r
+  M$T_df1..R.[selr] <- 1
+  M$T_df2..R.[selr] <- M$T_N..R.[selr] - 2  
+  # ensure z is tranformed to fisher z
+  M$sigma[selz] <- sqrt(1 / (M$T_N..R.[selz] - 3))
+
+  # object to write count to
+  res <- list(NULL)
+  res[[1]] <- rep(0, dim(M)[1] + 1)
+  res[[2]] <- rep(0, dim(M)[1] + 1)
+  res[[3]] <- rep(0, dim(M)[1] + 1)
+
+  # compute critical value for F and t values
+  # we assume two-tailed tests everywhere
+  fCV <- qf(p = alpha, df1 = M$T_df1..R., df2 = M$T_df2..R., lower.tail = FALSE)
+  # compute critical value for z values
+  zCV <- qnorm(p = .025, mean = 0, sd = M$sigma[selz], lower.tail = FALSE)  
+  # compute critical value for chi2 values
+  Chi2CV <- qchisq(p = .05, df = M$T_df1..R.[selChi2], lower.tail = FALSE)
+
+  for(es_loop in 1:length(es)){
+
+    # L will be the number of nonsignificant studies sampled from studies from M, 
+    # which have true effect es > 0
+    for (L in 0:dim(M)[1]){
+
+      # randomly generate a p-value given the effect sizes
+      # the null effects will yield uniform p-values      
+      for (i in 1:n.iter){
+
+        ran_L <- sample(dim(M)[1], size = L, replace = FALSE)
+
+        # set population effect for the randomly sampled to es.
+        pop_effect <- rep(0, dim(M)[1])
+        if (!L == 0) pop_effect[ran_L] <- es[es_loop]
+
+        # compute the noncentrality parameter
+        # for the null effects this will be 0
+        f2 <- pop_effect^2 / (1 - pop_effect^2)
+        ncp <- f2 * ifelse(M$T_Test.Statistic..R. == "F",
+                           M$T_df1..R. + M$T_df2..R. + 1,
+                           ifelse(selr,
+                                  M$T_df1..R. + M$T_df2..R. + 1,
+                                  ifelse(selChi2,
+                                         M$T_N..R.,
+                                         M$T_df1..R. + M$T_df2..R.)))
+
+        # determine area under H1 that corresponds to nonsignificant findings (= beta = Type II error)      
+        beta <- pf(q = fCV, df1 = M$T_df1..R., df2 = M$T_df2..R., ncp = ncp, lower.tail = TRUE)
+        beta[selz] <- pnorm(zCV, atanh(pop_effect[selz]), M$sigma[selz], lower.tail = TRUE) - pnorm(-zCV, atanh(pop_effect[selz]), M$sigma[selz], lower.tail = TRUE) 
+        beta[selChi2] <- pchisq(Chi2CV, df = M$T_df1..R.[selChi2], ncp = ncp[selChi2], lower.tail = TRUE)
+
+        # compute p-value alternative dist; sample from beta
+        pA <- runif(length(beta), min = 0, max = beta)
+
+        # test statistics simulated under alternative, based on beta
+        fA <- qf(p = pA, df1 = M$T_df1..R., df2 = M$T_df2..R., ncp = ncp, lower.tail = TRUE)
+        fA[selz] <- qnorm(pA[selz] + pnorm(-zCV, atanh(pop_effect[selz]), M$sigma[selz], lower.tail = TRUE),
+                          atanh(pop_effect[selz]), M$sigma[selz], lower.tail = TRUE)
+        fA[selChi2] <- qchisq(pA[selChi2], df = M$T_df1..R.[selChi2], ncp = ncp[selChi2], lower.tail = TRUE)
+
+        # pValues under null
+        # convert test statistics under alternative to p-values under h0
+        p0 <- pf(q = fA, df1 = M$T_df1..R., df2 = M$T_df2..R., lower.tail = FALSE)
+        p0[selz] <- 1 - 2 * abs(pnorm(fA[selz], 0, M$sigma[selz], lower.tail = FALSE) - .5)
+        p0[selChi2] <- pchisq(fA[selChi2], M$T_df1..R.[selChi2], lower.tail = FALSE)
+
+        # Result of Fisher test for this run with L true effects > 0
+        simulated <- FisherMethod(p0, 1, .05)
+
+        res[[es_loop]][L + 1] <- res[[es_loop]][L + 1] + ifelse(simulated$Fish > Fish_M$Fish, 1, 0)
+      }
+    }
+  }
+  save(res, file = sprintf('%sdata/res_application_3', run))
+}
+
+load(sprintf('%sdata/res_application_3', run))
+res[[1]] / n.iter
+res[[2]] / n.iter
+res[[3]] / n.iter
+
+# pop_effect = .1
+# sampled from L = 0:63
+# 10000 iterations
+# > res[[1]] / n.iter
+# [1] 0.0386 0.0428 0.0519 0.0551 0.0576 0.0638 0.0752 0.0818 0.0902 0.0921 0.1018 0.1142
+# [13] 0.1287 0.1312 0.1468 0.1595 0.1669 0.1812 0.1828 0.2010 0.2186 0.2352 0.2470 0.2629
+# [25] 0.2733 0.2935 0.3037 0.3222 0.3439 0.3596 0.3723 0.3950 0.4047 0.4197 0.4432 0.4584
+# [37] 0.4826 0.5048 0.5080 0.5365 0.5536 0.5576 0.5955 0.6062 0.6181 0.6363 0.6505 0.6713
+# [49] 0.6738 0.6996 0.7166 0.7239 0.7394 0.7540 0.7760 0.7736 0.7920 0.8046 0.8165 0.8329
+# [61] 0.8328 0.8523 0.8621 0.8719
+
+# pop_effect = .3
+# sampled from L = 0:63
+# 10000 iterations
+# > res[[2]] / n.iter
+# [1] 0.0397 0.0590 0.0901 0.1294 0.1726 0.2231 0.2856 0.3542 0.4347 0.4947 0.5769 0.6511
+# [13] 0.7153 0.7817 0.8280 0.8777 0.9038 0.9339 0.9532 0.9678 0.9790 0.9851 0.9903 0.9955
+# [25] 0.9975 0.9982 0.9989 0.9995 0.9995 0.9996 0.9998 0.9999 1.0000 1.0000 1.0000 1.0000
+# [37] 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000
+# [49] 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000
+# [61] 1.0000 1.0000 1.0000 1.0000
+
+# pop_effect = .5
+# sampled from L = 0:63
+# 10000 iterations
+# > res[[3]] / n.iter
+# [1] 0.0386 0.0777 0.1265 0.2085 0.3026 0.4241 0.5481 0.6754 0.7932 0.8589 0.9169 0.9558
+# [13] 0.9776 0.9888 0.9958 0.9985 0.9991 0.9995 0.9999 0.9999 1.0000 1.0000 1.0000 1.0000
+# [25] 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000
+# [37] 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000
+# [49] 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000
+# [61] 1.0000 1.0000 1.0000 1.0000
+
+@
+
+Upon reanalysis of the 63 statistically nonsignificant replications within RPP we determined that many of these "failed" replications say hardly anything about whether there are truly no effects.
+The Fisher test of these 63 nonsignificant results indicated some evidence for the presence of at least one false negative finding ($\chi^2(126)=155.2382$, $p=0.039$).
+Assuming $X$ small nonzero true effects among the nonsignificant results yields a confidence interval of 0-63 (0-100\%).
+More specifically, if all results are in fact true negatives then $p_Y=.039$, whereas if all true effects are $\rho=.1$ then $p_Y=.872$.
+Hence, the 63 statistically nonsignificant results of the RPP are in line with any number of true small effects --- from none to all.
+Consequently, we cannot draw firm conclusions about the state of the field psychology concerning the frequency of false negatives using the RPP results and the Fisher test, when all true effects are small.
+Assuming $X$ medium or strong true effects underlying the nonsignificant results from RPP yields confidence intervals 0-21 (0-33.3\%) and 0-13 (0-20.6\%), respectively.
+In other words, the 63 statistically nonsignificant RPP results are also in line with some true effects actually being medium or even large.
+
+\subsection*{Discussion}
+
+The reanalysis of the nonsignificant RPP results using the Fisher method demonstrates that any conclusions on the validity of individual effects based on "failed" replications, as determined by statistical significance, is unwarranted and irresponsible.
+This was also noted by both the original RPP team \cite{Open_Science_Collaboration2015-zs,Anderson2016-bv} and in a critique of the RPP \cite{Gilbert2016-mi}.
+Replication efforts such as the RPP or the Many Labs project remove publication bias and result in a less biased assessment of the true effect size.
+Nonetheless, single replications should not be seen as the definitive result, considering that these results indicate there remains much uncertainty about whether a nonsignificant result is a true negative or a false negative.
+The explanation of this finding is that most of the RPP replications, although often statistically more powerful than the original studies, still did not have enough statistical power to distinguish a true small effect from a true zero effect \cite{Maxwell2015-yb}.
+Interpreting results of replications should therefore also take the precision of the estimate of both the original and replication into account \cite{Cumming2014-fi}.
 
@@
 
+Much attention has been paid to false positive results in recent years.
+Our study demonstrates the importance of focusing on false negatives as well.
+We examined evidence for false negatives in nonsignificant results in three different ways.
+To this end, we adapted the Fisher method to detect the presence of at least one false negative in a set of statistically nonsignificant results; simulations indicated it to be a powerful method for that purpose.
+The three applications indicated that (i) approximately two out of three psychology articles reporting nonsignificant results contain evidence for at least one false negative, (ii) nonsignificant results on gender effects contain evidence of true nonzero effects, and (iii) the statistically nonsignificant replications from the Reproducibility Project Psychology (RPP) do not warrant conclusions about the absence or presence of true zero effects underlying these nonsignificant results.
+
+The methods used in the three different applications provide crucial context to interpret the results.
+In applications 1 and 2, we did not differentiate between main and peripheral results.
+Hence, the interpretation of a significant Fisher test result pertains to the evidence of at least one false negative in all reported results, not the evidence for at least one false negative in the main results.
+Nonetheless, even when we focused only on the main results in application 3, the Fisher test does not indicate specifically which result is false negative, only whether there is evidence for a false negative in a set of results.
+As such, the Fisher test is primarily useful to test a set of potentially underpowered results in a more powerful manner, albeit that the result then applies to the complete set.
+Additionally, in applications 1 and 2 we focused on results reported in eight psychology journals; extrapolating the results to other journals might not be warranted given that there might be substantial differences in the type of results reported in other journals or fields.
+
+More generally, our results in these three applications confirm that the problem of false negatives in psychology remains pervasive.
+Previous concern about power \cite{Cohen1962-jc,Sedlmeier1989-yc,Bakker2012-tf,Marszalek2011-rf}, which was even addressed by an APA Statistical Task Force in 1999 that recommended increased statistical power \cite{Wilkinson_APA_Task_Force_on_Statistical_Inference1999-ht}, seems not to have resulted in actual change \cite{Marszalek2011-rf}.
+A potential explanation for this lack of change is that researchers overestimate statistical power when designing a study for small effects \cite{Bakker2016-nj}.
+
+Reducing the emphasis on binary decisions in individual studies and increasing the emphasis on the precision of a study might help reduce the problem of decision errors.
+For example, a large but statistically nonsignificant study might yield a confidence interval (CI) of the effect size of [-0.01; 0.05], whereas a small but significant study might yield a CI of [0.01; 1.30].
+In a purely binary decision mode, the small but significant study would result in the conclusion that there is an effect because it provided a statistically significant result, despite it containing much more uncertainty than the larger study about the underlying true effect size.
+In a precision mode, the large study provides a more certain estimate and therefore is deemed more informative and provides the best estimate.
+Using meta-analyses to combine estimates obtained in studies on the same effect may further increase the overall estimate’s precision.
+Although the emphasis on precision and the meta-analytic approach is fruitful in theory, we should realize that publication bias will result in precise but biased (overestimated) effect size estimates of meta-analyses \cite{Nuijten2015-kh}.
+
+\subsection*{Limitations and further research}
+
+One assumption of the Fisher test is independence of $p$-values.
+In Application 1, we analyzed all statistically nonsignificant results reported in the papers for false negatives, which may result in dependent $p$-values within a paper.
+We inspected this possible dependency with the intra-class correlation ($ICC$), where $ICC=1$ indicates full dependency and $ICC=0$ indicates full independence.
+For the set of observed results, the ICC for p-values was .001, indicating independence of $p$-values within a paper.
+We therefore believe that our conclusions are not affected by this possible dependence.
+
+For all three applications, the Fisher tests' conclusions are limited to detecting at least one false negative in a \textit{set of results}.
+The method cannot be used to draw inferences on individuals results in the set.
+To draw inferences on the true effect size underlying one specific observed effect size, generally more information (i.e., studies) is needed to increase the precision of the effect size estimate.
+
+Another potential caveat relates to the data collected with the \texttt{R} package \texttt{statcheck} and used in applications 1 and 2.
+\texttt{statcheck} extracts inline, APA style reported test statistics, but does not include results included from tables or results that are not reported as the APA prescribes.
+Consequently, our results and conclusions may not be generalizable to \textit{all} results reported in articles.
+
+Given that the results indicate that false negatives are still a problem in psychology, albeit slowly on the decline in published research, further research is warranted.
+Further research could focus on comparing evidence for false negatives in main and peripheral results.
+Our results in combination with results of previous studies suggest that publication bias mainly operates on results of tests of main hypotheses, and less so on peripheral results.
+Another venue for future research is using the Fisher test to re-examine evidence in the literature on certain other effects or often-used covariates, such as age and race.
+Finally, the Fisher test may and is also used to meta-analyze effect sizes of different studies.
+Whereas Fisher used his method to test the null-hypothesis of an underlying true zero effect using several studies’ $p$-values, the method has recently been extended to test the same hypothesis using only statistically significant $p$-values.
+The principle of uniformly distributed $p$-values given the true effect size on which the Fisher method is based, also underlies newly developed methods of meta-analysis that adjust for publication bias, such as $p$-uniform \cite{Van_Assen2015-gg} and $p$-curve \cite{Simonsohn2014-dm}.
+Extensions of these methods to include nonsignificant as well as significant $p$-values and to estimate heterogeneity are still under construction.
+
+To conclude, the three applications that were presented indicate that false negatives remain a problem in the psychology literature, despite the decreased attention and that we should be wary to interpret statistically nonsignificant results as there being no effect in reality.
+One way to combat this interpretation of statistically nonsignificant results is to incorporate testing for potential false negatives, which the Fisher method facilitates in a highly approachable manner  (a spreadsheet for carrying out such a test is available at \url{https://osf.io/tk57v/}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Appendix A}
@@
 \bibliography{../bibliography/library}
+
+\section*{Author note}
+All research files, data, and analyses scripts are available for download at \url{https://github.com/chartgerink/2014tgtbf/archive/master.zip}. 
 \end{document}

### 2016-09-20 submission/manuscript.tex
Clean repo, make sure dling files and generating ms works: YES

--- 2016-09-20 submission/manuscript.Rnw
@@
 
+\usepackage{Sweave}
 \begin{document}
-\SweaveOpts{concordance=TRUE}
+\input{manuscript-concordance}
 \maketitle
@@
 \newpage
-
-<<Dependencies, echo=FALSE, print=FALSE>>=
-# Running in Sweave or running the code in Rstudio project
-# If you want to run in sweave, comment out the line with run <- ''
-run <- '../'
-# run <- ''
-
-# Set the cran mirror
-r <- getOption("repos")
-r["CRAN"] <- "http://cran.cnr.berkeley.edu/"
-options(repos = r)
-# Download and load dependencies
-if(!require(httr)){install.packages('httr')}
-library(httr)
-if(!require(latex2exp)){install.packages('latex2exp')}
-library(latex2exp)
-if(!require(plyr)){install.packages('plyr')}
-library(plyr)
-if(!require(ggplot2)){install.packages('ggplot2')}
-library(ggplot2)
-if(!require(stringr)){install.packages('stringr')}
-library(stringr)
-if(!require(car)){install.packages('car')}
-library(car)
-if(!require(xtable)){install.packages('xtable')}
-library(xtable)
-
-# custom functions
-source(sprintf("%sfunctions/functions.R", run))
-@
 
@@
 
-<<Download, echo=FALSE, results=hide>>=
-# Downloads the data if not available locally
-
-# The data from the Nuijten et al paper
-if(!file.exists(sprintf('%sdata/statcheck_full_anonymized.csv', run)))
-{
-  GET('https://osf.io/gdr4q/?action=download',
-      write_disk(sprintf('%sdata/statcheck_full_anonymized.csv', run), overwrite = TRUE))
-}
-
-if(!file.exists(sprintf('%sdata/datafilegender500_post.csv', run)))
-{
-  # the gender related results (ALL)
-  GET('https://raw.githubusercontent.com/chartgerink/2014tgtbf/master/data/datafilegender500_post.csv',
-      write_disk(sprintf('%sdata/datafilegender500_post.csv', run), overwrite = TRUE))
-}
-
-if(!file.exists(sprintf('%sdata/gendercoded cleaned and discussed.csv', run)))
-{
-  # the coded gender results
-  GET('https://raw.githubusercontent.com/chartgerink/2014tgtbf/master/data/gendercoded%20cleaned%20and%20discussed.csv',
-      write_disk(sprintf('%sdata/gendercoded cleaned and discussed.csv', run), overwrite = TRUE))
-}
-@
-
-<<Read in data clean data, echo=FALSE, results=hide>>=
-dat <- read.csv2(sprintf("%sdata/statcheck_full_anonymized.csv", run),
-                 stringsAsFactors = F,
-                 dec = ",",
-                 sep = ";")[-1]
-
-# There are two test statistic indicators that are NA
-# Manually correct these
-dat$Statistic[is.na(dat$Statistic)] <- "F"
-
-# Computing unadjusted and adjusted effect sizes (OBSERVED)
-dat <- cbind(dat, esComp.statcheck(dat))
-dat$adjESComp[dat$adjESComp < 0] <- 0
-
-# Turning df1 for t and r into 1.
-dat$df1[dat$Statistic == "t" | dat$Statistic == "r"] <- 1
-
-# Select out incorrectly exttracted r values
-dat <- dat[!(dat$Statistic=="r" & dat$Value > 1),]
-
-# Select out irrefutably wrong df reporting
-dat <- dat[!dat$df1 == 0,]
-
-# select out NA computed p-values
-dat <- dat[!is.na(dat$Computed),]
-
-# Selecting only the t, r and F values
-dat <- dat[dat$Statistic == 't' | dat$Statistic == 'r' | dat$Statistic == 'F',]
-nsig <- dat$Computed >= .05
-esR <- c(.1, .25, .4)
-alpha = .05
-alphaF = .1
-@
-
-<<Simulations, echo=FALSE, results=hide, eval = FALSE>>=
-# Statistical properties of the Fisher method -----------------------------
-
-# condition setting
-N <- c(as.numeric(summary(dat$df2)[2]), # 25th percentile
-       as.numeric(summary(dat$df2)[3]), # 50th percentile
-       as.numeric(summary(dat$df2)[5]) # 75th percentile
-)
-
-ES <- c(.00,
-        seq(.01, .99, .01))
-
-P <- c(seq(1, 10, 1), seq(15, 50, 5))
-
-alpha <- .05
-alphaF <- 0.10
-n.iter <- 10000
-
-# NOTE: runs if the results file (N_33.csv, N_62.csv, N_119.csv) are absent
-
-if(!file.exists(sprintf('%sdata/N_33.csv', run)) &
-   !file.exists(sprintf('%sdata/N_62.csv', run)) &
-   !file.exists(sprintf('%sdata/N_119.csv', run)))
-{
-  set.seed(35438759)
-  source(sprintf('%sfunctions/simCode.R', run))
-}
-
-# Load all results back in
-files <- list.files()[grepl("N_", list.files())]
-
-names <- str_sub(files,start=1L, end=-5L)
-for(i in 1:length(files)){
-  assign(x = names[i], read.csv(files[i]))
-  assign(x = names[i], t(get(x = names[i])[ ,-1]))
-}
-
-# Data for table
-# rows are k
-# columns are effect size
-# N = 33
-t(get(x = names[2]))
-# N = 62
-t(get(x = names[3]))
-# N = 119
-t(get(x = names[1]))
-
-# Table 3 power computations
-ser <- 1/sqrt(c(33, 62, 119)-3)
-rho <- .1
-zcv <- 1.282
-rcv <- (exp(2*(zcv*ser))-1)/(exp(2*(zcv*ser))+1)
-zrcv <- .5*log((1+rcv)/(1-rcv))
-zrho <- .5*log((1+rho)/(1-rho))
-round(1-pnorm(zrcv, mean=zrho, sd=ser),4)
-
-rho <- .25
-rcv <- (exp(2*(zcv*ser))-1)/(exp(2*(zcv*ser))+1)
-zrcv <- .5*log((1+rcv)/(1-rcv))
-zrho <- .5*log((1+rho)/(1-rho))
-round(1-pnorm(zrcv, mean=zrho, sd=ser),4)
-
-# Agresti-Coull CI
-.1 - qnorm(.95, 0, 1) * (sqrt((1/10000) * .1 * .9))
-.1 + qnorm(.95, 0, 1) * (sqrt((1/10000) * .1 * .9))
-
-@
-
 APA style $t$, $r$, and $F$ test statistics were extracted from eight psychology journals with the \texttt{R} package \texttt{statcheck} \cite{Nuijten2015-od,Epskamp2015-ps}.
@@
 These errors,  may have affected the results of our analyses.
-Since most $p$-values and corresponding test statistics were consistent in our dataset (\Sexpr{round((dim(dat)[1] - sum(dat$Error[!is.na(dat$Error)])) / dim(dat)[1] * 100,1)}\%), we do not believe these typing errors substantially affected our results and conclusions based on them.
+Since most $p$-values and corresponding test statistics were consistent in our dataset (90.7\%), we do not believe these typing errors substantially affected our results and conclusions based on them.
 
 % Sorry, inserted table manually long time ago, need to check manually
-<<prep table 3, echo = FALSE, results = hide>>=
-# Descriptives dataset
-journals <- sort(unique(dat$journals.jour.))
-for(j in 1:length(journals)){
-  selJournal <- dat$journals.jour. == journals[j]
-  meanK <- mean(table(dat$Source[selJournal]))
-  len <- length(dat$Computed[selJournal & !is.na(dat$Computed)])
-  sigRes <- sum(dat$Computed[selJournal & !is.na(dat$Computed)] < .05)
-  print(
-    paste0(
-      journals[j], "\t", len, "\t", round(meanK, 1), "\t", sigRes, "\t", len-sigRes
-    )
-  )
-}
-@
 
@@
 
-<<percentages, echo = FALSE, results = hide>>=
-small <- sum(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] < .1) / length(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))]) * 100
-medium <- sum(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] >= .1 & sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] < .25) / length(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))]) * 100
-large <- sum(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] >= .25 & sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] < .4) / length(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))]) * 100
-larger <- sum(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] >= .4) / length(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))]) * 100
-
-if(!file.exists(sprintf('%sfigures/Fig1.pdf', run)))
-{
-  pdf(sprintf('%sfigures/Fig1.pdf', run), width=11, height=7)
-
-  par(mai = c(1, 1, .2, .2))
-  plot(density(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))]),
-       lty = 1,
-       frame.plot = T, 
-       main = "",
-       xlim = c(0, 1), ylim = c(0, 2),
-       xaxs = "i",
-       yaxs = 'i',
-       xlab = TeX("Correlation (|$\\eta$|)"),
-       ylab = "Density",
-       cex.axis = 1.5,
-       cex.lab = 1.5,
-       col = "black", las = 1, bty = 'n')
-  abline(v = c(.1, .25, .4), lty = 2, col = "grey")
-  t1 <- sum(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] < .1) / length(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))])
-  t2 <- sum(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] >= .1 & sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] < .25) / length(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))])
-  t3 <- sum(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] >= .25 & sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] < .4) / length(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))])
-  t4 <- sum(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))] >= .4) / length(sqrt(dat$esComp)[!is.na(sqrt(dat$esComp))])
-  text(x = .1 / 2, y = .15, labels = round(t1, 2), cex = 1)
-  text(x = ((.25 - .1) / 2) + .1, y = .15, labels = round(t2, 2), cex = 1)
-  text(x = ((.4 - .25) / 2) + .25, y = .15, labels = round(t3, 2), cex = 1)
-  text(x = ((1 - .4) / 2) + .4, y = .15, labels = round(t4, 2), cex = 1)
-  dev.off()
-}
-
-if(!file.exists(sprintf('%sfigures/Fig2.pdf', run)))
-{
-  pdf(sprintf('%sfigures/Fig2.pdf', run), width=11, height=7)
-  par(mai = c(1, 1, .2, .2))
-  # nonsignificant proportion p/year
-  i <- 1
-  sig <- NULL
-  nsigtemp <- NULL
-  kval <- NULL
-
-  for(y in 1985:2013){
-    sel <- dat$years.y. == y
-    sig[i] <- sum(dat$Computed[sel] < alpha) / length(dat$Computed[sel])
-    nsigtemp[i] <- sum(dat$Computed[sel] > alpha) / length(dat$Computed[sel])
-    kval[i] <- median(table(dat$Source[sel])) / sum(table(dat$Source[sel]))
-    i <- i + 1
-  }
-  par(mfrow = c(1, 1), mai = c(1, 1, .2, .2))
-  plot(x = 1985:2013,
-       nsigtemp,
-       ylim = c(0, .4), xlim = c(1985, 2014),
-       type = 'o',
-       xlab = "Year", ylab = 'Proportion nonsignificant',
-       yaxs = 'i', xaxt = 'n',
-       cex.axis = 1.5, cex.lab = 1.5, las = 1, bty = 'n')
-  axis(1, at=c(seq(1985, 2010, 5), 2013), labels = c(seq(1985, 2010, 5), 2013), col.axis="black",
-       cex.axis = 1.5)
-  dev.off()
-}
-@
-
-Figure \ref{fig:fig1} shows the distribution of observed effect sizes (in $|\eta|$) across all articles and indicates that, of the 223,082 observed effects, \Sexpr{round(small, 0)}\% were zero to small (i.e., $0\leq|\eta|<.1$), \Sexpr{round(medium, 0)}\% were small to medium (i.e., $.1\leq|\eta|<.25$), \Sexpr{round(large, 0)}\% medium to large (i.e., $.25\leq|\eta|<.4$), and \Sexpr{round(larger, 0)}\% large or larger (i.e., $|\eta|\geq.4$; \cite{Cohen1988-wg}).
-This suggests that the majority of effects reported in psychology is medium or smaller (i.e., \Sexpr{round(medium+small,0)}\%), which is somewhat in line with a previous study on effect distributions \cite{Gignac2016-je}.
+Figure \ref{fig:fig1} shows the distribution of observed effect sizes (in $|\eta|$) across all articles and indicates that, of the 223,082 observed effects, 7\% were zero to small (i.e., $0\leq|\eta|<.1$), 23\% were small to medium (i.e., $.1\leq|\eta|<.25$), 27\% medium to large (i.e., $.25\leq|\eta|<.4$), and 42\% large or larger (i.e., $|\eta|\geq.4$; \cite{Cohen1988-wg}).
+This suggests that the majority of effects reported in psychology is medium or smaller (i.e., 30\%), which is somewhat in line with a previous study on effect distributions \cite{Gignac2016-je}.
 Of the full set of 223,082 test results, 54,595 (24.5\%) were nonsiginificant, which is the dataset for our main analyses.
@@
 \end{center}
-\caption{Density of observed effect sizes of results reported in eight psychology journals, with \Sexpr{round(small, 0)}\% of effects in the category none-small, \Sexpr{round(medium, 0)}\% small-medium, \Sexpr{round(large, 0)}\% medium-large, and \Sexpr{round(larger, 0)}\% beyond large.}
+\caption{Density of observed effect sizes of results reported in eight psychology journals, with 7\% of effects in the category none-small, 23\% small-medium, 27\% medium-large, and 42\% beyond large.}
 \label{fig:fig1}
@@
 
-<<Simulating null distribution, echo = FALSE, results = hide>>=
-if(file.exists(sprintf('%sdata/simNullEs', run)))
-{
-  load(sprintf('%sdata/simNullEs', run))
-} else
-{
-  # takes some time to run these, have to simulate many values
-  # go get coffee
-  set.seed(1234)
-  simNullEs <- simNullDist(dat, n.iter = length(dat$esComp[nsig]) * 3, alpha = .05)
-  simNullEs$adjESComp[simNullEs$adjESComp < 0] <- 0
-
-  save(simNullEs, file = sprintf('%sdata/simNullEs', run))
-}
-
-temp <- ks.test(simNullEs$esComp,
-                dat$esComp[nsig],
-                alternative="greater")
-
-if(!file.exists(sprintf('%sfigures/Fig3.pdf', run)))
-{
-  pdf(sprintf('%sfigures/Fig3.pdf', run), width=11, height=7)
-  par(mfrow = c(1,2), mai = c(1.2,1.2,.8,.5))
-  # Overall
-  plot(ecdf(na.omit(sqrt(simNullEs$esComp))),
-       lty = 1,
-       frame.plot = T, 
-       main = TeX(
-         sprintf(
-           "Unadjusted, $D=%s,p<2.2\\times 10^{-16}$", round(temp$statistic,2))),
-       xlim = c(0, 1),
-       xaxs = "i",
-       yaxs = "i",
-       xlab = TeX("Correlation (|$\\eta$|)"),
-       ylab = "Cumulative density",
-       cex.axis=.8,
-       cex.lab=1,
-       cex.main=1.5,
-       col = "grey", las=1)
-  lines(ecdf(na.omit(sqrt(dat$esComp[nsig]))))
-  legend(x = .6, y = .2, legend = c(TeX("$H_0$"), 'Observed'),
-         cex = 1, lty = c(1, 1),
-         col = c("grey", "black", 2),
-         box.lwd = 0, lwd = 2, bty = 'n')
-  for(es in esR){
-    h0horiz <- sum(sqrt(simNullEs$esComp[!is.na(simNullEs$esComp)]) < es) / length(simNullEs$esComp[!is.na(simNullEs$esComp)])
-    clip(es, 1, 0, h0horiz)
-    abline(h = h0horiz, v = es, lty = 2, col = "grey")
-    clip(0, 1, 0, 1)
-    text(x = .9, y = h0horiz - .02, labels = round(h0horiz, 2), cex = 1, col = 'darkgrey')
-    x <- sqrt(dat$esComp[nsig]) <= es
-    horiz <- sum(x[!is.na(x)]) / length(x[!is.na(x)])
-    text(x = .05, y = horiz + .02, labels = round(horiz, 2), cex = 1)
-    clip(0, es, 0, horiz)
-    abline(h = horiz, v = es, lty = 2, col = "black")
-    clip(0, 1, 0, 1)
-  }
-}
-
-temp <- ks.test(simNullEs$adjESComp,
-                dat$adjESComp[nsig],
-                alternative="greater")
-# Overall[adj]
-plot(ecdf(na.omit(sqrt(simNullEs$adjESComp))),
-     lty = 1,
-     frame.plot = T, 
-     main = TeX(
-       sprintf(
-         "Adjusted, $D=%s,p<2.2\\times 10^{-16}$", round(temp$statistic,2))),
-     xlim = c(0, 1),
-     xaxs = "i",
-     yaxs = "i",
-     xlab = TeX("Correlation (|$\\eta$|)"),
-     ylab = "Cumulative density",
-     cex.axis = .8,
-     cex.lab = 1,
-     cex.main = 1.5,
-     col = "grey", las = 1)
-lines(ecdf(na.omit(sqrt(dat$adjESComp[nsig]))))
-legend(x = .6,y = .2,legend = c(TeX("$H_0$"), 'Observed'),
-       cex = 1,lty = c(1, 1),
-       col = c("grey", "black", 2), box.lwd = 0, lwd = 2, bty = 'n')
-for(es in esR){
-  h0horiz <- sum(sqrt(simNullEs$adjESComp[!is.na(simNullEs$adjESComp)]) < es) / length(simNullEs$adjESComp[!is.na(simNullEs$adjESComp)])
-  clip(es, 1, 0, h0horiz)
-  abline(h = h0horiz, v = es, lty = 2, col = "grey")
-  clip(0, 1, 0, 1)
-  text(x = .9, y = h0horiz - .02, labels = round(h0horiz, 2), cex = 1, col = 'darkgrey')
-  x <- sqrt(dat$adjESComp[nsig]) <= es
-  horiz <- sum(x[!is.na(x)]) / length(x[!is.na(x)])
-  text(x = .05, y = horiz + .02, labels = round(horiz, 2), cex = 1)
-  clip(0, es, 0, horiz)
-  abline(h = horiz, v = es, col = "black", lty = 2)
-  clip(0, 1, 0, 1)
-}
-dev.off()
-
-if(!file.exists(sprintf('%sfigures/S1Fig.pdf', run)))
-{
-  pdf(sprintf('%sfigures/S1Fig.pdf', run), onefile = TRUE, width = 11, height = 11)
-  par(mfrow = c(2, 2), mai = c(1.2, 1.2, .8, .5))
-
-  for(i in 1:4){
-    sel <- dat$journals.jour. == sort(unique(dat$journals.jour.))[i] & nsig
-    set.seed(i)
-    simNullEs <- simNullDist(dat, n.iter=length(dat$esComp[sel])*3, alpha = .05)
-    temp <- ks.test(simNullEs$esComp,
-                    dat$esComp[dat$journals.jour. == sort(unique(dat$journals.jour.))[i] & nsig],
-                    alternative = "greater")
-    print((temp))
-    if(i == 3){
-      plot(ecdf(na.omit(sqrt(simNullEs$esComp))),
-           lty = 1,
-           frame.plot = T, 
-           main = TeX(
-             sprintf("%s, D=%s, $p=7.934\\times 10^{-6}$",
-                     sort(unique(dat$journals.jour.))[i],
-                     round(temp$statistic,3))),
-           xlim = c(0,1),
-           xaxs = "i",
-           yaxs = "i",
-           xlab = TeX("Correlation (|$\\eta$|)"),
-           ylab = "Cumulative density",
-           cex.axis = .8,
-           cex.lab = 1,
-           cex.main = 1.5,
-           col = "grey", las = 1)
-    }
-    else{plot(ecdf(na.omit(sqrt(simNullEs$esComp))),
-              lty = 1,
-              frame.plot = T, 
-              main = TeX(
-                sprintf("%s, D=%s, $p=2.2\\times 10^{-16}$",
-                        sort(unique(dat$journals.jour.))[i],
-                        round(temp$statistic,3))),
-              xlim = c(0,1),
-              xaxs = "i",
-              yaxs = "i",
-              xlab = TeX("Correlation (|$\\eta$|)"),
-              ylab = "Cumulative density",
-              cex.axis = .8,
-              cex.lab = 1,
-              cex.main = 1.5,
-              col = "grey", las = 1)}
-    lines(ecdf(sqrt(dat$esComp[sel])),
-          lwd = .5)
-    legend(x = .6, y = .2, legend = c(TeX("$H_0$"), 'Observed'),
-           cex = 1.2, lty = c(1, 1),
-           col = c("grey", "black", 2), box.lwd = 0, lwd = 2, bty = 'n')
-    for(es in esR){
-      h0horiz <- sum(sqrt(simNullEs$esComp[!is.na(simNullEs$esComp)]) < es) / length(simNullEs$esComp[!is.na(simNullEs$esComp)])
-      clip(es, 1, 0, h0horiz)
-      abline(h = h0horiz, v = es, lty = 2, col = "grey")
-      clip(0, 1, 0, 1)
-      x <- sqrt(dat$esComp[sel]) <= es
-      horiz <- sum(x[!is.na(x)]) / length(x[!is.na(x)])
-      text(x = .05, y = horiz + .02, labels = round(horiz, 2), cex = 1.2)
-      text(x = .9, y = h0horiz - .02, labels = round(h0horiz, 2), cex = 1.2, col = 'darkgrey')
-      clip(0, es, 0, horiz)
-      abline(h = horiz, v = es, col = "black", lty = 2)
-      clip(0, 1, 0, 1)
-    }
-  }
-
-  for(i in 5:8){
-    sel <- dat$journals.jour. == sort(unique(dat$journals.jour.))[i] & nsig
-    set.seed(i)
-    simNullEs <- simNullDist(dat, n.iter=length(dat$esComp[sel])*3, alpha=.05)
-    temp <- ks.test(simNullEs$esComp,
-                    dat$esComp[dat$journals.jour. == sort(unique(dat$journals.jour.))[i] & nsig],
-                    alternative="greater")
-    print((temp))
-    plot(ecdf(na.omit(sqrt(simNullEs$esComp))),
-         lty = 1,
-         frame.plot = T, 
-         main = TeX(
-           sprintf("%s, D=%s, $p=2.2\\times 10^{-16}$",
-                   sort(unique(dat$journals.jour.))[i],
-                   round(temp$statistic,3))),
-         xlim = c(0, 1),
-         xaxs = "i",
-         yaxs = "i",
-         xlab = TeX("Correlation (|$\\eta$|)"),
-         ylab = "Cumulative density",
-         cex.axis = .8,
-         cex.lab = 1,
-         cex.main = 1.5,
-         col = "grey", las = 1)
-    lines(ecdf(sqrt(dat$esComp[sel])),
-          lwd = .5)
-    legend(x = .6,y = .2,legend = c(TeX("$H_0$"), 'Observed'),
-           cex = 1.2,lty = c(1, 1),
-           col = c("grey", "black", 2), box.lwd = 0 , lwd = 2, bty = 'n')
-    for(es in esR){
-      h0horiz <- sum(sqrt(simNullEs$esComp[!is.na(simNullEs$esComp)]) < es) / length(simNullEs$esComp[!is.na(simNullEs$esComp)])
-      clip(es, 1, 0, h0horiz)
-      abline(h = h0horiz, v = es, lty = 2, col = "grey")
-      clip(0, 1, 0, 1)
-      x <- sqrt(dat$esComp[sel]) <= es
-      horiz <- sum(x[!is.na(x)]) / length(x[!is.na(x)])
-      text(x = .05, y = horiz + .02, labels = round(horiz, 2), cex = 1.2)
-      text(x = .9, y = h0horiz - .02, labels = round(h0horiz, 2), cex = 1.2, col = 'darkgrey')
-      clip(0, es, 0, horiz)
-      abline(h = horiz, v = es, col = "black", lty = 2)
-      clip(0, 1, 0, 1)
-    }
-  }
-  dev.off()
-}
-
-@
-
 For the entire set of nonsignificant results across journals, Figure \ref{fig:fig3} indicates that there is substantial evidence of false negatives.
@@
 These differences indicate that larger nonsignificant effects are reported in papers than expected under a null effect.
-This indicates the presence of false negatives, which is confirmed by the Kolmogorov-Smirnov test, $D=\Sexpr{round(temp$statistic, 2)}$, $p<.000000000000001$.
+This indicates the presence of false negatives, which is confirmed by the Kolmogorov-Smirnov test, $D=0.25$, $p<.000000000000001$.
 Results were similar when the nonsignificant effects were considered separately for the eight journals, although deviations were smaller for the Journal of Applied Psychology (see \href{../figures/S1Fig}{Figure S1} for results per journal).
@@
 \subsubsection*{Evidence of false negatives in articles.}
-
-<<Paper level application, echo = FALSE, results = hide>>=
-# Computing the Fisher Tests
-if(!file.exists(sprintf('%sdata/fishRes', run)))
-{
-  fishRes <- FisherMethod(dat$Computed, as.character(dat$Source))
-  save(fishRes, file = sprintf('%sdata/fishRes', run))
-} else
-{
-  load(sprintf('%sdata/fishRes', run))
-}
-
-if(!file.exists(sprintf('%sdata/fishDF', run)))
-{
-  # Get vector to identify which papers are from which journal
-  sourcejour <- NULL
-  for(i in 1:length(unique(dat$Source))){
-    sourcejour[i] <- unique(dat$journals.jour.[dat$Source==unique(dat$Source)[i]])
-  }
-
-  years <- NULL
-  for(i in 1:length(sort(unique(dat$Source)))){
-    sel <- dat$Source == sort(unique(dat$Source))[i]
-    years[i] <- unique(dat$years.y.[sel])
-    print(i)
-  }
-
-  # Make vector of sig/nsig/na 
-  fishDF <- data.frame(FisherP=fishRes$PFish, journal=sourcejour, kRes=fishRes$CountNSig, year=years)
-
-  save(fishDF, file = sprintf('%sdata/fishDF', run))
-} else
-{
-  load(sprintf('%sdata/fishDF', run))
-}
-
-alphaF <- 0.10
-# Compute amount of papers and proportion of sig/nsig/NA Fisher Method tests
-final <- NULL
-kLen <- c(1, 2, 3, 4, 5, 10, 20)
-
-for(journals in sort(unique(dat$journals.jour.))){
-  sel <- fishDF$journal == journals
-
-  # Amount of papers in a journal
-  amount <- length(fishDF$FisherP[sel])
-  # Proportion of significant fisher results
-  amountSig <- sum(fishDF$FisherP[sel & !is.na(fishDF$FisherP)] < alphaF)
-
-  # Amount of papers in a journal without significant results
-  countNA <- sum(is.na(fishDF$FisherP[sel]))
-  journalSet <- NULL  
-  # Writing out the results
-  for(k in 1:length(kLen)){
-    if(k == 7){
-      x <- sum(fishDF$FisherP[sel & !is.na(fishDF$FisherP) & fishDF$kRes >= kLen[k]] < alphaF) / length(fishDF$FisherP[sel  & fishDF$kRes >= kLen[k]])
-      journalSet <- cbind(journalSet, x)
-    }
-    else if(k == 5 | k ==6){
-      x <- sum(fishDF$FisherP[sel & !is.na(fishDF$FisherP) & fishDF$kRes >= kLen[k]& fishDF$kRes < kLen[k+1]] < alphaF) / length(fishDF$FisherP[sel & fishDF$kRes >= kLen[k]& fishDF$kRes < kLen[k+1]])
-      journalSet <- cbind(journalSet, x)
-    } else{
-      x <- sum(fishDF$FisherP[sel & !is.na(fishDF$FisherP) & fishDF$kRes == kLen[k]] < alphaF) / length(fishDF$FisherP[sel & fishDF$kRes == kLen[k]])
-      journalSet <- cbind(journalSet, x)}
-  }
-  temp <- cbind(journals,
-                journalSet,
-                amountSig / amount,
-                countNA,
-                amountSig,
-                amount)
-  # This is the result that goes into the table
-  final <- rbind(final, temp)
-}
-temp <- "Overall"
-for(i in 1:length(kLen)){
-  if(i == 7){
-    temp[i+1] <- sum(fishDF$FisherP[fishDF$kRes >= kLen[i] & !is.na(fishDF$FisherP)] < alphaF )/ length(fishDF$FisherP[fishDF$kRes >= kLen[i]])
-  }
-  else if(i == 5|i == 6){
-    temp[i+1] <- sum(fishDF$FisherP[fishDF$kRes >= kLen[i] &fishDF$kRes < kLen[i+1] & !is.na(fishDF$FisherP)] < alphaF )/ length(fishDF$FisherP[fishDF$kRes >= kLen[i] & fishDF$kRes < kLen[i+1]])
-  }
-  else{
-    temp[i+1] <- sum(fishDF$FisherP[fishDF$kRes == kLen[i] & !is.na(fishDF$FisherP)] < alphaF )/ length(fishDF$FisherP[fishDF$kRes == kLen[i]])  
-  }
-
-}
-temp <- c(temp,
-          sum(as.numeric(as.character(final[,dim(final)[2]-1])))/sum(as.numeric(as.character(final[,dim(final)[2]]))),
-          sum(as.numeric(as.character(final[,dim(final)[2]-2]))),
-          sum(as.numeric(as.character(final[,dim(final)[2]-1]))),
-          sum(as.numeric(as.character(final[,dim(final)[2]]))))
-final <- rbind(as.character(temp), final)
-final <- as.data.frame(final)
-
-names(final) <- c('journals', paste0('k', kLen), 'overall', 'countNA', 'amountSig', 'nrpapers')
-# write.csv(final, 'table4.csv', row.names=F)
-
-# Overall
-table(fishDF$kRes)
-# Per journal
-table(fishDF$kRes[fishDF$journal=="DP"])
-table(fishDF$kRes[fishDF$journal=="FP"])
-table(fishDF$kRes[fishDF$journal=="JAP"])
-table(fishDF$kRes[fishDF$journal=="JCCP"])
-table(fishDF$kRes[fishDF$journal=="JEPG"])
-table(fishDF$kRes[fishDF$journal=="JPSP"])
-table(fishDF$kRes[fishDF$journal=="PLOS"])
-table(fishDF$kRes[fishDF$journal=="PS"])
-
-# Median per journal
-x = as.numeric(as.character(final$amountSig)) / (as.numeric(as.character(final$nrpapers)) - as.numeric(as.character(final$countNA)))
-y = c(median(fishDF$kRes[fishDF$journal=="DP"]),
-      median(fishDF$kRes[fishDF$journal=="FP"]),
-      median(fishDF$kRes[fishDF$journal=="JAP"]),
-      median(fishDF$kRes[fishDF$journal=="JCCP"]),
-      median(fishDF$kRes[fishDF$journal=="JEPG"]),
-      median(fishDF$kRes[fishDF$journal=="JPSP"]),
-      median(fishDF$kRes[fishDF$journal=="PLOS"]),
-      median(fishDF$kRes[fishDF$journal=="PS"]))
-cor(x[-1], y)
-
-# Computing the number of significant Fisher results per year
-# As proportion of all papers reporting nonsignificant results
-fishDF$logicalP <- ifelse(fishDF$FisherP < .1, 1, 0)
-fisherYear <- ddply(fishDF, .(year), summarise, propYear=mean(logicalP, na.rm=TRUE))
-
-knsYear <- ddply(fishDF, .(year), summarise, kYear=mean(kRes, na.rm=TRUE))
-pmeanYear <- ddply(dat[dat$Reported.Comparison == '=' & dat$Reported.P.Value > .05, ],
-                   .(years.y.), summarise, pYear=mean(Reported.P.Value, na.rm=TRUE))
-
-esYear <- ddply(dat[dat$Reported.Comparison == '=' & dat$Reported.P.Value > .05, ],
-                .(years.y.), summarise, esYear=mean(esComp, na.rm=TRUE))
-
-mydf <- data.frame(x = fisherYear$year,
-                   y = fisherYear$propYear,
-                   count = knsYear$kYear)
-
-mydf
-
-if(!file.exists(sprintf('%sfigures/Fig4.pdf', run)))
-{
-  ggplot(mydf, aes(x = x, y = y)) + geom_point(aes(size = count)) + ylim(0, 1) + geom_smooth(method="lm") +
-    xlab("Year") + ylab("Proportion significant Fisher results")
-
-  ggsave(filename = sprintf('%sfigures/Fig4.pdf', run), plot = last_plot(), width = 7, height = 5)
-}
-
-# sample size development over time
-medianN <- NULL
-p25 <- NULL
-p75 <- NULL
-i <- 1
-for(y in 1985:2013){
-  temp <- summary(dat$df2[dat$years.y. == y])
-
-  medianN[i] <- temp[3]
-  p25[i] <- temp[2]
-  p75[i] <- temp[5]
-
-  i <- i + 1
-}
-
-if(!file.exists(sprintf('%sfigures/Fig5.pdf', run)))
-{
-  pdf(sprintf('%sfigures/Fig5.pdf', run), width=7, height=6)
-  par(mar = c(4, 4, .2, 2))
-  plot(x=1985:2013, y=medianN, type='o', col="black",
-       ylab="Degrees of freedom", xlab="Year",
-       xlim = c(1985, 2015), 
-       ylim=c(0,150), cex.lab=1.2, las=1, lwd=1, cex.axis=1.2, xaxs='i',
-       yaxs='i',
-       bty = 'n')
-  lines(x=1985:2013, y=p25, type='o', col='grey')
-  lines(x=1985:2013, y=p75, type='o', col='grey')
-  text(y = 100, x = 2010, "P75", col = "grey")
-  text(y = 50, x = 2010, "P50", col = "black")
-  text(y = 22, x = 2010, "P25", col = "grey")
-  dev.off()
-}
-@
 
@@
 Figure \ref{fig:fig4} depicts evidence across all articles per year, as a function of time (1985-2013); point size in the figure corresponds to the mean number of nonsignificant results per article (mean $k$) in that year.
-Interestingly, the proportion of articles with evidence for false negatives decreased from \Sexpr{round(mydf$y[1]*100, 0)}\% in 1985 to \Sexpr{round(mydf$y[29]*100, 0)}\% in 2013, despite the increase in mean $k$ (from \Sexpr{round(mydf$count[1], 2)} in 1985 to \Sexpr{round(mydf$y[29], 2)} in 2013).
+Interestingly, the proportion of articles with evidence for false negatives decreased from 77\% in 1985 to 55\% in 2013, despite the increase in mean $k$ (from 2.11 in 1985 to 0.55 in 2013).
 This decreasing evidence over time cannot be explained by a decrease in sample size over time, as sample size in psychology articles has stayed stable across time (see Figure \ref{fig:fig5}).
 One (partial) explanation of this surprising result is that in the early days researchers primarily used to report more APA results with 'marginally significant' $p$-values (i.e., $p$-values slightly larger than .05), compared to nowadays.
-This explanation is supported by both a smaller number of reported APA results in the past and the smaller mean reported nonsignificant $p$-value (\Sexpr{round(mean(dat$Reported.P.Value[dat$Reported.Comparison == '=' & dat$years.y.
-== 1985 & dat$Reported.P.Value > .05]), 3)} in 1985, \Sexpr{round(mean(dat$Reported.P.Value[dat$Reported.Comparison == '=' & dat$years.y.
-== 2013 & dat$Reported.P.Value > .05]), 3)} in 2013).
+This explanation is supported by both a smaller number of reported APA results in the past and the smaller mean reported nonsignificant $p$-value (0.222 in 1985, 0.386 in 2013).
 We do not know whether these marginally significant $p$-values were interpreted as evidence in favor of a finding (or not) and how these interpretations changed over time.
-Another potential explanation is that the effect sizes being studied have become smaller over time (mean effect $r$ \Sexpr{round(mean(sqrt(dat$esComp[dat$Reported.Comparison == '=' & dat$years.y.
-== 1985 & dat$Reported.P.Value > .05])), 3)} in 1985, \Sexpr{round(mean(sqrt(dat$esComp[dat$Reported.Comparison == '=' & dat$years.y.
-== 2013 & dat$Reported.P.Value > .05])), 3)} in 2013), which results in both higher $p$-values over time and lower power of the Fisher test.
+Another potential explanation is that the effect sizes being studied have become smaller over time (mean effect $r$ 0.257 in 1985, 0.187 in 2013), which results in both higher $p$-values over time and lower power of the Fisher test.
 Using the data at hand, we cannot distinguish between the two explanations.
@@
 
-<<gender, echo = FALSE, results = hide>>=
-# 27,523 gender results
-# manually extracted from datafilegender500_post.csv
-# number of rows (take into account header row)
-
-# gender effect evaluated -------------------------------------------------
-
-gend <- read.csv2(sprintf('%sdata/gendercoded cleaned and discussed.csv', run), sep = ";", dec = ".", header = TRUE)
-
-# 1 = null expected
-# 2 = effect expected
-# 3 = no expectation
-table(gend$significance, gend$final_code)
-
-options(scipen = 5, digits = 8)
-# sel <- gend$significance == "significant" & gend$final_code == "no expectation"
-for(sig in unique(gend$significance)){
-  for(code in unique(gend$final_code[!is.na(gend$final_code)])){
-    sel <- gend$significance == sig & gend$final_code == code
-
-    if(sig == "significant"){
-      temp <- gend$Computed[sel] / .05
-      pstar <- temp[!is.na(temp)]
-      x$CountNSig <- length(pstar)
-      x$Fish <- -2*sum(log(pstar))
-      x$PFish <- pchisq(x$Fish, df = 2 * length(pstar), lower.tail = FALSE)
-    }
-    if(sig == "nonsignificant"){
-      x <- (FisherMethod(x = gend$Computed[sel], id = 1, alpha = 0.05))
-    }
-
-    cat(sprintf("For %s %s, k = %s, chi2 = %s, p = %s\n", sig, code, x$CountNSig, x$Fish, x$PFish))
-  }
-}
-
-if(!file.exists(sprintf('%sfigures/Fig6.pdf', run)))
-{
-
-    ggplot(gend, aes(x = Computed, fill = significance)) + 
-    geom_density(alpha = .3) + 
-    xlab(TeX("$P$-value")) + 
-    ylab("Density")
-  ggsave(filename = sprintf('%sfigures/Fig6.pdf', run), plot = last_plot(), width = 7, height = 5)
-  }
-@
-
 The coding of the 178 results indicated that results rarely specify whether these are in line with the hypothesized effect (see Table \ref{tab:tab5}).
@@
 \subsection*{Results}
-
-<<rpp reanalysis, echo = FALSE, results = hide>>=
-# Read in Tilburg data
-if(!file.exists(sprintf('%sdata/rpp_data.csv', run)))
-{
-  info <- GET('https://osf.io/fgjvw/?action=download', write_disk(sprintf('%sdata/rpp_data.csv', run), overwrite = TRUE)) #downloads data file from the OSF
-}
-MASTER <- read.csv(sprintf("%sdata/rpp_data.csv", run))[1:167, ]
-colnames(MASTER)[1] <- "ID" # Change first column name to ID to be able to load .csv file
-
-# number of iterations per condition
-# if true probability is .025 or .975, then the SE = .00494 for n.iter = 1,000
-n.iter <- 10000
-# select only the available and nonsignificant replications
-# call this M
-M <- MASTER[MASTER$T_sign_R == 0 
-            & !is.na(MASTER$T_sign_R) 
-            & (MASTER$T_Test.Statistic..R. == 't'
-               | MASTER$T_Test.Statistic..R. == 'F'
-               | MASTER$T_Test.Statistic..R. == 'r'
-               | MASTER$T_Test.Statistic..R. == 'z'
-               | MASTER$T_Test.Statistic..R. == 'Chi2'), ]
-
-Fish_M <- FisherMethod(x = M$T_pval_USE..R.,
-                       id = 1,
-                       alpha = .05)
-
-if(!file.exists(sprintf('%sdata/res_application_3', run)))
-{
-
-  # alpha of the individual test
-  alpha <- .05
-  # vector of ES
-  es <- c(.1, .3, .5)
-
-  # set seed
-  set.seed(alpha * n.iter * sum(es))
-
-  # selectors for easy selection later on  
-  selr <- M$T_Test.Statistic..R. == 'r'
-  selz <- M$T_Test.Statistic..R. == 'z'
-  selChi2 <- M$T_Test.Statistic..R. == 'Chi2'
-
-  # ensure that we can easily compute the effect size r
-  M$T_df1..R.[selr] <- 1
-  M$T_df2..R.[selr] <- M$T_N..R.[selr] - 2  
-  # ensure z is tranformed to fisher z
-  M$sigma[selz] <- sqrt(1 / (M$T_N..R.[selz] - 3))
-
-  # object to write count to
-  res <- list(NULL)
-  res[[1]] <- rep(0, dim(M)[1] + 1)
-  res[[2]] <- rep(0, dim(M)[1] + 1)
-  res[[3]] <- rep(0, dim(M)[1] + 1)
-
-  # compute critical value for F and t values
-  # we assume two-tailed tests everywhere
-  fCV <- qf(p = alpha, df1 = M$T_df1..R., df2 = M$T_df2..R., lower.tail = FALSE)
-  # compute critical value for z values
-  zCV <- qnorm(p = .025, mean = 0, sd = M$sigma[selz], lower.tail = FALSE)  
-  # compute critical value for chi2 values
-  Chi2CV <- qchisq(p = .05, df = M$T_df1..R.[selChi2], lower.tail = FALSE)
-
-  for(es_loop in 1:length(es)){
-
-    # L will be the number of nonsignificant studies sampled from studies from M, 
-    # which have true effect es > 0
-    for (L in 0:dim(M)[1]){
-
-      # randomly generate a p-value given the effect sizes
-      # the null effects will yield uniform p-values      
-      for (i in 1:n.iter){
-
-        ran_L <- sample(dim(M)[1], size = L, replace = FALSE)
-
-        # set population effect for the randomly sampled to es.
-        pop_effect <- rep(0, dim(M)[1])
-        if (!L == 0) pop_effect[ran_L] <- es[es_loop]
-
-        # compute the noncentrality parameter
-        # for the null effects this will be 0
-        f2 <- pop_effect^2 / (1 - pop_effect^2)
-        ncp <- f2 * ifelse(M$T_Test.Statistic..R. == "F",
-                           M$T_df1..R. + M$T_df2..R. + 1,
-                           ifelse(selr,
-                                  M$T_df1..R. + M$T_df2..R. + 1,
-                                  ifelse(selChi2,
-                                         M$T_N..R.,
-                                         M$T_df1..R. + M$T_df2..R.)))
-
-        # determine area under H1 that corresponds to nonsignificant findings (= beta = Type II error)      
-        beta <- pf(q = fCV, df1 = M$T_df1..R., df2 = M$T_df2..R., ncp = ncp, lower.tail = TRUE)
-        beta[selz] <- pnorm(zCV, atanh(pop_effect[selz]), M$sigma[selz], lower.tail = TRUE) - pnorm(-zCV, atanh(pop_effect[selz]), M$sigma[selz], lower.tail = TRUE) 
-        beta[selChi2] <- pchisq(Chi2CV, df = M$T_df1..R.[selChi2], ncp = ncp[selChi2], lower.tail = TRUE)
-
-        # compute p-value alternative dist; sample from beta
-        pA <- runif(length(beta), min = 0, max = beta)
-
-        # test statistics simulated under alternative, based on beta
-        fA <- qf(p = pA, df1 = M$T_df1..R., df2 = M$T_df2..R., ncp = ncp, lower.tail = TRUE)
-        fA[selz] <- qnorm(pA[selz] + pnorm(-zCV, atanh(pop_effect[selz]), M$sigma[selz], lower.tail = TRUE),
-                          atanh(pop_effect[selz]), M$sigma[selz], lower.tail = TRUE)
-        fA[selChi2] <- qchisq(pA[selChi2], df = M$T_df1..R.[selChi2], ncp = ncp[selChi2], lower.tail = TRUE)
-
-        # pValues under null
-        # convert test statistics under alternative to p-values under h0
-        p0 <- pf(q = fA, df1 = M$T_df1..R., df2 = M$T_df2..R., lower.tail = FALSE)
-        p0[selz] <- 1 - 2 * abs(pnorm(fA[selz], 0, M$sigma[selz], lower.tail = FALSE) - .5)
-        p0[selChi2] <- pchisq(fA[selChi2], M$T_df1..R.[selChi2], lower.tail = FALSE)
-
-        # Result of Fisher test for this run with L true effects > 0
-        simulated <- FisherMethod(p0, 1, .05)
-
-        res[[es_loop]][L + 1] <- res[[es_loop]][L + 1] + ifelse(simulated$Fish > Fish_M$Fish, 1, 0)
-      }
-    }
-  }
-  save(res, file = sprintf('%sdata/res_application_3', run))
-}
-
-load(sprintf('%sdata/res_application_3', run))
-res[[1]] / n.iter
-res[[2]] / n.iter
-res[[3]] / n.iter
-
-# pop_effect = .1
-# sampled from L = 0:63
-# 10000 iterations
-# > res[[1]] / n.iter
-# [1] 0.0386 0.0428 0.0519 0.0551 0.0576 0.0638 0.0752 0.0818 0.0902 0.0921 0.1018 0.1142
-# [13] 0.1287 0.1312 0.1468 0.1595 0.1669 0.1812 0.1828 0.2010 0.2186 0.2352 0.2470 0.2629
-# [25] 0.2733 0.2935 0.3037 0.3222 0.3439 0.3596 0.3723 0.3950 0.4047 0.4197 0.4432 0.4584
-# [37] 0.4826 0.5048 0.5080 0.5365 0.5536 0.5576 0.5955 0.6062 0.6181 0.6363 0.6505 0.6713
-# [49] 0.6738 0.6996 0.7166 0.7239 0.7394 0.7540 0.7760 0.7736 0.7920 0.8046 0.8165 0.8329
-# [61] 0.8328 0.8523 0.8621 0.8719
-
-# pop_effect = .3
-# sampled from L = 0:63
-# 10000 iterations
-# > res[[2]] / n.iter
-# [1] 0.0397 0.0590 0.0901 0.1294 0.1726 0.2231 0.2856 0.3542 0.4347 0.4947 0.5769 0.6511
-# [13] 0.7153 0.7817 0.8280 0.8777 0.9038 0.9339 0.9532 0.9678 0.9790 0.9851 0.9903 0.9955
-# [25] 0.9975 0.9982 0.9989 0.9995 0.9995 0.9996 0.9998 0.9999 1.0000 1.0000 1.0000 1.0000
-# [37] 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000
-# [49] 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000
-# [61] 1.0000 1.0000 1.0000 1.0000
-
-# pop_effect = .5
-# sampled from L = 0:63
-# 10000 iterations
-# > res[[3]] / n.iter
-# [1] 0.0386 0.0777 0.1265 0.2085 0.3026 0.4241 0.5481 0.6754 0.7932 0.8589 0.9169 0.9558
-# [13] 0.9776 0.9888 0.9958 0.9985 0.9991 0.9995 0.9999 0.9999 1.0000 1.0000 1.0000 1.0000
-# [25] 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000
-# [37] 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000
-# [49] 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000 1.0000
-# [61] 1.0000 1.0000 1.0000 1.0000
-
-@
 

### 2016-09-20 Analyzing/inversion_method.R

@@ -1,150 +1,0 @@
-# Written by CHJ Hartgerink van MALM van Assen
-if(!require(httr)){install.packages('httr')}
-library(httr)
-
-# Read in data
-info <- GET('https://osf.io/fgjvw/?action=download', write_disk('rpp_data.csv', overwrite = TRUE)) #downloads data file from the OSF
-MASTER <- read.csv("rpp_data.csv")[1:167, ]
-colnames(MASTER)[1] <- "ID" # Change first column name to ID to be able to load .csv file
-
-# source function needed
-info <- GET('https://osf.io/b2vn7/?action=download', write_disk('functions.r', overwrite = TRUE)) 
-source('functions.r')
-
-# number of iterations per condition
-# if true probability is .025 or .975, then the SE = .00494 for n.iter = 1,000
-n.iter <- 10000
-# alpha of the individual test
-alpha <- .05
-# vector of ES
-es <- c(.1, .3, .5)
-
-# set seed
-set.seed(alpha * n.iter * sum(es))
-
-# select only the available and nonsignificant replications
-# call this M
-M <- MASTER[MASTER$T_sign_R == 0 
-            & !is.na(MASTER$T_sign_R) 
-            & (MASTER$T_Test.Statistic..R. == 't'
-               | MASTER$T_Test.Statistic..R. == 'F'
-               | MASTER$T_Test.Statistic..R. == 'r'
-               | MASTER$T_Test.Statistic..R. == 'z'
-               | MASTER$T_Test.Statistic..R. == 'Chi2'), ]
-
-Fish_M <- FisherMethod(x = M$T_pval_USE..R.,
-                       id = 1,
-                       alpha = .05)
-
-# selectors for easy selection later on  
-selr <- M$T_Test.Statistic..R. == 'r'
-selz <- M$T_Test.Statistic..R. == 'z'
-selChi2 <- M$T_Test.Statistic..R. == 'Chi2'
-
-# ensure that we can easily compute the effect size r
-M$T_df1..R.[selr] <- 1
-M$T_df2..R.[selr] <- M$T_N..R.[selr] - 2  
-# ensure z is tranformed to fisher z
[…]

### 2016-09-20 Analyzing/mastercode.R

@@ -1,761 +1,0 @@
-# Code written by CHJ Hartgerink
-# Checked by: -
-
-# load packages -----------------------------------------------------------
-
-if(!require(httr)){install.packages('httr')}
-library(httr)
-if(!require(latex2exp)){install.packages('latex2exp')}
-library(latex2exp)
-if(!require(plyr)){install.packages('plyr')}
-library(plyr)
-if(!require(ggplot2)){install.packages('ggplot2')}
-library(ggplot2)
-if(!require(stringr)){install.packages('stringr')}
-library(stringr)
-if(!require(car)){install.packages('car')}
-library(car)
-
-# download and load dependent files ---------------------------------------
-
-# custom functions
-source("functions/functions.R")
-
-# data
-# literally gets the data from the Nuijten et al paper
-GET('https://osf.io/gdr4q/?action=download',
-    write_disk('data/statcheck_full_anonymized.csv', overwrite = TRUE))
-dat <- read.csv2("data/statcheck_full_anonymized.csv",
-                 stringsAsFactors = F,
-                 dec = ",",
-                 sep = ";")[-1]
-
-# the gender related results (ALL)
-GET('https://raw.githubusercontent.com/chartgerink/2014tgtbf/master/data/datafilegender500_post.csv',
-    write_disk('datafilegender500_post.csv', overwrite = TRUE))
-# the coded gender results
-GET('https://raw.githubusercontent.com/chartgerink/2014tgtbf/master/data/gendercoded%20cleaned%20and%20discussed.csv',
-    write_disk('gendercoded cleaned and discussed.csv', overwrite = TRUE))
-
-
-
-# data cleaning -----------------------------------------------------------
-
-# There are two test statistic indicators that are NA
-# Manually correct these
-dat$Statistic[is.na(dat$Statistic)] <- "F"
-
-# Computing unadjusted and adjusted effect sizes (OBSERVED)
-dat <- cbind(dat, esComp.statcheck(dat))
-dat$adjESComp[dat$adjESComp < 0] <- 0
-
[…]

### 2016-09-20 Analyzing/simCode.R

@@ -1,76 +1,0 @@
-#################
-# Do not adjust #
-#################
-powe <- NULL
-power <- NULL
-chiP <- NULL
-# Per N
-for(n in 1:length(N)){
-  power <- NULL
-  for(k in 1:length(P)){
-    pow <- 0
-    powe <- NULL
-    for(es in 1:length(ES)){
-      if(pow < .995){
-        for(i in 1:n.iter){
-          # Step 1 - Critical value
-          tCV <- qt(p=alpha, df=N[n]-1,lower.tail=F)
-          
-          # Step 2 - non-centrality parameter
-          f2 <- ES[es]^2/(1-ES[es]^2)
-          ncp <- f2*N[n]
-          
-          # Step 3 - beta
-          beta <- pt(q=tCV,df=N[n]-1,ncp=ncp, lower.tail=T)
-          
-          # Step 4 - pValues under alternative distribution
-          pA <- runif(n=P[k],min=0,max=beta)
-          
-          # Step 5 - tValues simulated under alternative
-          tA <- qt(p=pA, df=N[n]-1, ncp=ncp, lower.tail=T)
-          
-          # Step 6 - pValues under null
-          p0 <- pt(q=tA, df=N[n]-1,lower.tail=F)
-          
-          # Step 7 - transform p-values back into state space [0;1]
-          p0 <- (p0-alpha)/(1-alpha)
-          
-          # Step 8 - computing fisher statistic
-          chiF <- -2*sum(log(p0))
-          chiP[i] <- pchisq(q=chiF, df=2*length(p0), lower.tail=F)
-        }
-        # Step 9 - computing the proportion significant
-        pow <- sum(chiP < alphaF)/n.iter
-        print(paste(N[n], P[k], ES[es], pow,sep=" "))
-      } else{
-        # For computing efficiency all subsequent effect sizes
-        # are rounded to one if previous was .995 or higher
-        pow <- 1
-      }
-      if(pow == 0){pow <- 1}
-      powe <- cbind(powe,
-                    pow)
-    }
-    power <- rbind(power, powe)
-  }
-  filepath <- sprintf('%sdata/N_%s.csv', 
-                      run,
-                      N[n])
-  power <- as.data.frame(power)
-  names(power) <- ES
-  write.csv(cbind(P, power),
-            file=filepath)
-  ### General comments
-  ### Comment 1
-  ### Noncentral distribution estimation yields the possibility
-  ### of null beta values, which yields a power of null as all
-  ### p0 values are 1. This is a limit due to the precision of
[…]

### 2016-09-20 figures/Fig1.R

@@ -1,62 +1,0 @@
-# Set to project folder
-# NOT figures folder
-setwd(choose.dir())
-
-# Figure 1
-N <- 10000
-i <- seq(1, N, 1)
-fcv <- qf(p=1-.05 ,df1=1,df2=97)
-
-# Null
-beta <- pf(q=fcv, df1=1, df2=97)
-quadpoints <- (i/(N+1))*beta
-fquad <- qf(quadpoints, df1=1, df2=97)
-temp <- 1-pf(fquad, df1=1, df2=97)
-pquad0 <- (temp-.05)/(1-.05)
-
-# Small
-beta <- pf(q=fcv, df1=1, df2=97, ncp=(.01/(1-.01))*(100+1+1))
-N <- 10000
-i <- seq(1, N, 1)
-quadpoints <- (i/(N+1))*beta
-fquad <- qf(quadpoints, df1=1, df2=97, ncp=(.01/(1-.01))*(100+1+1))
-temp <- 1-pf(fquad, df1=1, df2=97)
-pquadS <- (temp-.05)/(1-.05)
-
-# Medium
-beta <- pf(q=fcv, df1=1, df2=97, ncp=(.0625/(1-.0625))*(100+1+1))
-quadpoints <- (i/(N+1))*beta
-fquad <- qf(quadpoints, df1=1, df2=97, ncp=(.0625/(1-.0625))*(100+1+1))
-temp <- 1-pf(fquad, df1=1, df2=97)
-pquadM <- (temp-.05)/(1-.05)
-
-# Large
-beta <- pf(q=fcv, df1=1, df2=97, ncp=(.14/(1-.14))*(100+1+1))
-quadpoints <- (i/(N+1))*beta
-fquad <- qf(quadpoints, df1=1, df2=97, ncp=(.14/(1-.14))*(100+1+1))
-temp <- 1-pf(fquad, df1=1, df2=97)
-pquadL <- (temp-.05)/(1-.05)
-
-pdf('figures/Fig1.pdf', width=7, height=8)
-par(mai=c(1,1,.2,.2))
-plot(density(pquadL, kernel="gaussian", bw="SJ", adjust=1), xlim=c(0.01,1), xaxs='i', lwd=4,
-     frame.plot=T, 
-     main="",
-     #      ylim=c(0,4.5),
-     xaxs="i",
-     yaxs="i",
-     xlab="P-value",
-     ylab = "Density",
-     cex.axis=.8,
-     cex.lab=1,
-     col = "black", las=1, bty = 'L')
[…]

### 2016-09-20 figures/Fig2.R

@@ -1,11 +1,0 @@
-# Set to project folder
-# NOT figures folder
-setwd(choose.dir())
-
-pdf('figures/Fig2.pdf', width = 7, height = 5)
-par(mar = c(1, 2, 3, 4))
-plot(dnorm(seq(-3, 3, .001), 0, 1), type = 'l',
-     bty = 'n', xaxt = 'n', yaxt = 'n')
-# lines(dnorm(seq(-2, 4, .001), 1, .5))
-dev.off()
-

### 2016-09-20 figures/Fig3.R

@@ -1,31 +1,0 @@
-# Choose the directory all files are cloned in
-# NOT the figures folder.
-setwd(choose.dir())
-
-load('figures/Fig3')
-
-# Effect PDF
-pdf('figures/Fig3.pdf',width=7, height=8)
-par(mai = c(1, 1, 0, .2))
-
-plot(density(dat$esComp[!is.na(dat$esComp)]),
-     lty = 1,
-     frame.plot = T, 
-     main = "",
-     xlim = c(0, 1),
-     xaxs = "i",
-     xlab = latex2exp("Correlation ($\\eta$)"),
-     ylab = "Density",
-     cex.axis = .8,
-     cex.lab = 1,
-     col = "black", las = 1, bty = 'n')
-abline(v = c(.1, .25, .4), lty = 2, col = "grey")
-t1 <- sum(dat$esComp[!is.na(dat$esComp)] < .1) / length(dat$esComp[!is.na(dat$esComp)])
-t2 <- sum(dat$esComp[!is.na(dat$esComp)] >= .1 & dat$esComp[!is.na(dat$esComp)] < .25) / length(dat$esComp[!is.na(dat$esComp)])
-t3 <- sum(dat$esComp[!is.na(dat$esComp)] >= .25 & dat$esComp[!is.na(dat$esComp)] < .4) / length(dat$esComp[!is.na(dat$esComp)])
-t4 <- sum(dat$esComp[!is.na(dat$esComp)] >= .4) / length(dat$esComp[!is.na(dat$esComp)])
-text(x = .1 / 2, y = .15, labels = round(t1, 2), cex = 1)
-text(x = ((.25 - .1) / 2) + .1, y = .15, labels = round(t2, 2), cex = 1)
-text(x = ((.4 - .25) / 2) + .25, y = .15, labels = round(t3, 2), cex = 1)
-text(x = ((1 - .4) / 2) + .4, y = .15, labels = round(t4, 2), cex = 1)
-dev.off()

### 2016-09-20 figures/Fig4.R

@@ -1,16 +1,0 @@
-# Set to main folder of project
-# NOT figures folder
-setwd(choose.dir())
-load('figures/Fig4')
-
-pdf(file = 'figures/Fig4.pdf', width = 7, height = 5)
-par(mfrow = c(1, 1), mai = c(1, 1, .2, .2))
-plot(x=1985:2013,
-     nsigtemp,
-     ylim = c(0, .4),
-     type = 'o',
-     xlab = "Year", ylab = 'Proportion nonsignificant',
-     yaxs = 'i',
-     cex.axis = 1, las = 1, bty = 'n')
-abline(lm(nsigtemp ~ c(1985:2013)), lty = 2)
-dev.off()

### 2016-09-20 figures/Fig5.R

@@ -1,84 +1,0 @@
-# Set to main folder of project
-# NOT figures folder
-setwd(choose.dir())
-
-simNullEs <- read.table('archive/simNullEs.csv', sep = ";", dec = ".")
-
-temp <- ks.test(simNullEs$esComp,
-                dat$esComp[nsig],
-                alternative="greater")
-
-pdf('figures/Fig5.pdf', width=11, height=7)
-par(mfrow = c(1,2), mai = c(1.2,1.2,.8,.5))
-# Overall
-plot(ecdf(na.omit(sqrt(simNullEs$esComp))),
-     lty = 1,
-     frame.plot = T, 
-     main = latex2exp(
-       sprintf(
-         "Unadjusted, $D=%s,p<2.2\\times 10^{-16}$", round(temp$statistic,2))),
-     xlim = c(0, 1),
-     xaxs = "i",
-     yaxs = "i",
-     xlab = latex2exp("Correlation ($|\\eta|$)"),
-     ylab = "Cumulative density",
-     cex.axis=.8,
-     cex.lab=1,
-     cex.main=1.5,
-     col = "grey", las=1)
-lines(ecdf(na.omit(sqrt(dat$esComp[nsig]))))
-legend(x = .6, y = .2, legend = c(latex2exp("$H_0$"), 'Observed'),
-       cex = 1, lty = c(1, 1),
-       col = c("grey", "black", 2),
-       box.lwd = 0, lwd = 2, bty = 'n')
-for(es in esR){
-  h0horiz <- sum(sqrt(simNullEs$esComp[!is.na(simNullEs$esComp)]) < es) / length(simNullEs$esComp[!is.na(simNullEs$esComp)])
-  clip(es, 1, 0, h0horiz)
-  abline(h = h0horiz, v = es, lty = 2, col = "grey")
-  clip(0, 1, 0, 1)
-  text(x = .9, y = h0horiz - .02, labels = round(h0horiz, 2), cex = 1, col = 'darkgrey')
-  x <- sqrt(dat$esComp[nsig]) <= es
-  horiz <- sum(x[!is.na(x)]) / length(x[!is.na(x)])
-  text(x = .05, y = horiz + .02, labels = round(horiz, 2), cex = 1)
-  clip(0, es, 0, horiz)
-  abline(h = horiz, v = es, lty = 2, col = "black")
-  clip(0, 1, 0, 1)
-}
-
[…]

### 2016-09-20 figures/Fig6.R

@@ -1,25 +1,0 @@
-# Set to project folder
-# NOT figures folder
-setwd(choose.dir())
-if(!require(ggplot2)){install.packages('ggplot2')}
-if(!require(plyr)){install.packages('plyr')}
-library(ggplot2)
-library(plyr)
-
-load('figures/Fig6')
-
-# Computing the number of significant Fisher results per year
-# As proportion of all papers reporting nonsignificant results
-fishDF$logicalP <- ifelse(fishDF$FisherP<.1, 1, 0)
-fisherYear <- ddply(fishDF, .(year), summarise, propYear=mean(logicalP, na.rm=TRUE))
-
-knsYear <- ddply(fishDF, .(year), summarise, kYear=mean(kRes, na.rm=TRUE))
-
-mydf <- data.frame(x = fisherYear$year,
-                   y = fisherYear$propYear,
-                   count = knsYear$kYear)
-
-ggplot(mydf, aes(x = x, y = y)) + geom_point(aes(size = count)) + ylim(0, 1) + geom_smooth(method="lm") +
-  xlab("Year") + ylab("Proportion significant Fisher results")
-
-ggsave(filename = 'figures/Fig6.png', plot = last_plot(), width = 7, height = 5)

### 2016-09-20 figures/Fig7.r

@@ -1,62 +1,0 @@
-# Set to project folder
-# NOT figures folder
-setwd(choose.dir())
-
-# Load custom functions all at once
-customFunct <- list.files('functions/')
-for(i in 1:length(customFunct)){
-  source(
-    paste0('functions/', customFunct[i])
-  )
-}
-
-# Read- and prepare data
-dat <- read.csv2("data/statcheck_full_anonymized.csv", stringsAsFactors=F, dec = ",", sep = ";")[-1]
-
-# There are two test statistic indicators that are NA
-# Manually correct these
-dat$Statistic[is.na(dat$Statistic)] <- "F"
-
-# Computing unadjusted and adjusted effect sizes (OBSERVED)
-dat <- cbind(dat, esComp.statcheck(dat))
-dat$adjESComp[dat$adjESComp < 0] <- 0
-
-# Turning df1 for t and r into 1.
-dat$df1[dat$Statistic == "t" | dat$Statistic == "r"] <- 1
-
-# Select out incorrectly exttracted r values
-dat <- dat[!(dat$Statistic=="r" & dat$Value > 1),]
-
-# Select out irrefutably wrong df reporting
-dat <- dat[!dat$df1 == 0,]
-
-# select out NA computed p-values
-dat <- dat[!is.na(dat$Computed),]
-
-# Selecting only the t, r and F values
-dat <- dat[dat$Statistic == 't' | dat$Statistic == 'r' | dat$Statistic == 'F',]
-
-medianN <- NULL
-p25 <- NULL
-p75 <- NULL
-i <- 1
-for(y in 1985:2013){
-  temp <- summary(dat$df2[dat$years.y. == y])
-  
-  medianN[i] <- temp[3]
-  p25[i] <- temp[2]
-  p75[i] <- temp[5]
-  
-  i <- i + 1
-}
-
-pdf('figures/Fig7.pdf', width=7, height=6)
-par(mar = c(4, 4, .2, 2))
-plot(x=1985:2013, y=medianN, type='o', col="black",
-     ylab="N", xlab="Year", ylim=c(0,150), cex.lab=1.2, las=1, lwd=1, cex.axis=1.2, xaxs='i', bty = 'n')
-lines(x=1985:2013, y=p25, type='o', col='grey')
-lines(x=1985:2013, y=p75, type='o', col='grey')
-text(y = 100, x = 2010, "P75", col = "grey")
[…]

### 2016-09-20 figures/Fig8.r

@@ -1,44 +1,0 @@
-# Choose the directory all files are cloned in
-# NOT the figures folder.
-setwd(choose.dir())
-
-load('figures/Fig3')
-
-# Effect PDF
-pdf('figures/Fig8.pdf',width=7, height=8)
-par(mai = c(1, 1, 0, .2))
-
-plot(density(dat$esComp[!is.na(dat$esComp) & dat$years.y. == 1985]),
-     lty = 1,
-     frame.plot = T, 
-     main = "",
-     xlim = c(0, 1),
-     xaxs = "i",
-     xlab = latex2exp("Correlation ($\\eta$)"),
-     ylab = "Density",
-     cex.axis = .8,
-     cex.lab = 1,
-     col = "black", las = 1, bty = 'n')
-lines(density(dat$esComp[!is.na(dat$esComp) & dat$years.y. == 2013]), col = "darkgrey")
-abline(v = c(.1, .25, .4), lty = 2, col = "grey")
-t11 <- sum(dat$esComp[!is.na(dat$esComp) & dat$years.y == 1985] < .1) / length(dat$esComp[!is.na(dat$esComp) & dat$years.y == 1985])
-t21 <- sum(dat$esComp[!is.na(dat$esComp) & dat$years.y == 1985] >= .1 & dat$esComp[!is.na(dat$esComp) & dat$years.y == 1985] < .25) / length(dat$esComp[!is.na(dat$esComp) & dat$years.y == 1985])
-t31 <- sum(dat$esComp[!is.na(dat$esComp) & dat$years.y == 1985] >= .25 & dat$esComp[!is.na(dat$esComp) & dat$years.y == 1985] < .4) / length(dat$esComp[!is.na(dat$esComp) & dat$years.y == 1985])
-t41 <- sum(dat$esComp[!is.na(dat$esComp) & dat$years.y == 1985] >= .4) / length(dat$esComp[!is.na(dat$esComp) & dat$years.y == 1985])
-t12 <- sum(dat$esComp[!is.na(dat$esComp) & dat$years.y == 2013] < .1) / length(dat$esComp[!is.na(dat$esComp) & dat$years.y == 2013])
-t22 <- sum(dat$esComp[!is.na(dat$esComp) & dat$years.y == 2013] >= .1 & dat$esComp[!is.na(dat$esComp) & dat$years.y == 2013] < .25) / length(dat$esComp[!is.na(dat$esComp) & dat$years.y == 2013])
[…]

### 2016-09-20 figures/S1Fig.r

@@ -1,152 +1,0 @@
-# Set to main folder of project
-# NOT figures folder
-setwd(choose.dir())
-if(!require(latex2exp)){install.packages('latex2exp')}
-library(latex2exp)
-
-# Load custom functions all at once
-customFunct <- list.files('functions/')
-for(i in 1:length(customFunct)){
-  source(
-    paste0('functions/', customFunct[i])
-  )
-}
-
-# Load data
-# Read- and prepare data
-dat <- read.csv2("data/statcheck_full_anonymized.csv", stringsAsFactors=F, dec = ",", sep = ";")[-1]
-
-# There are two test statistic indicators that are NA
-# Manually correct these
-dat$Statistic[is.na(dat$Statistic)] <- "F"
-
-# Computing unadjusted and adjusted effect sizes (OBSERVED)
-dat <- cbind(dat, esComp.statcheck(dat))
-dat$adjESComp[dat$adjESComp < 0] <- 0
-
-# Turning df1 for t and r into 1.
-dat$df1[dat$Statistic == "t" | dat$Statistic == "r"] <- 1
-
-# Select out incorrectly exttracted r values
-dat <- dat[!(dat$Statistic=="r" & dat$Value > 1),]
-
-# Select out irrefutably wrong df reporting
-dat <- dat[!dat$df1 == 0,]
-
-# select out NA computed p-values
-dat <- dat[!is.na(dat$Computed),]
-
-# Selecting only the t, r and F values
-dat <- dat[dat$Statistic == 't' | dat$Statistic == 'r' | dat$Statistic == 'F',]
-nsig <- dat$Computed >= .05
-esR <- c(.1, .25, .4)
-
-pdf('figures/S1Fig.pdf', onefile = TRUE, width = 11, height = 11)
-par(mfrow = c(2, 2), mai = c(1.2, 1.2, .8, .5))
-
-for(i in 1:4){
-  sel <- dat$journals.jour. == sort(unique(dat$journals.jour.))[i] & nsig
-  set.seed(i)
-  simNullEs <- simNullDist(dat, n.iter=length(dat$esComp[sel])*3, alpha = .05)
-  temp <- ks.test(simNullEs$esComp,
-                  dat$esComp[dat$journals.jour. == sort(unique(dat$journals.jour.))[i] & nsig],
-                  alternative = "greater")
-  print((temp))
-  if(i == 3){
[…]

### 2016-10-05 submission/manuscript.Rnw
Revisions after reading club

@@
 \begin{abstract}
-Statistically significant research results in psychology have sometimes been considered "too good to be true", reflecting false positive findings.
-In this paper, we examine nonsignificant research results and whether they are "too good to be false", i.e., false negatives, which are also a threat to scientific progress.
-We inspected three applications of detecting false negatives.
-In Application 1, eight flagship psychological journals during 1985-2013 (30,710 papers) are investigated for false negatives.
-Across 54,595 nonsignificant statistical test results extracted with statcheck, evidence for false negatives was abound.
-We applied the Fisher test, which has high power to detect false negatives when there are at least three nonsignificant results and the population effect size is medium.
-All eight journals and 66.7\% of papers reporting nonsignificant results show evidence of at least one false negative.
-In Application 2, we manually investigated whether evidential value of (non)significant gender results depended on explicit expectations, but found that expectations are hardly clear in research results.
-Moreover, in Application 3, we reanalysed the nonsignificant replications from the Reproducibility Project Psychology and conclude that these nonsignificant results do not warrant conclusions about the validity of individual effects.
-We conclude from our findings that concern for statistical power and false negatives in psychological science is still warranted.
+Due to its probabilistic nature, Null Hypothesis Significance Testing (NHST) is subject to decision errors.
+The concern for false positives has overshadowed the concern for false negatives in the recent debates in psychology, which seems unwarranted.
+Our study demonstrates the importance of paying attention to false negatives alongside those significant results that may be 'too good to be true'; nonsignificant results may be 'too good to be false'.
+We examined evidence for false negatives in nonsignificant results in three different ways.
+To this end, we adapted the Fisher method to detect the presence of at least one false negative in a set of statistically nonsignificant results; simulations indicated it to be a powerful method for that purpose.
+The three applications indicated that (i) approximately two out of three (66.7\%) psychology articles reporting nonsignificant results contain evidence for at least one false negative, (ii) nonsignificant results on gender effects contain evidence of true nonzero effects, and (iii) the statistically nonsignificant replications from the Reproducibility Project Psychology (RPP) do not warrant conclusions about the absence or presence of true zero effects underlying these nonsignificant results.
+False negatives deserve more attention in the debate among psychologists, because there is sufficient evidence in these three applications to indicate that false negatives are a threat to the scientific discovery process; it can be considered a waste of resources if effects are studied but results are neglected due to the lack of statistical power.
 \end{abstract}
@@
 \keywords{nonsignificant, underpowered, effect size, Fisher test}
+
+\section*{Author note}
+All research files, data, and analyses scripts are preserved and made available for download at \url{http://doi.org/10.5281/zenodo.154514}.
 \newpage
@@
 Within the theoretical framework of scientific hypothesis testing, accepting or rejecting a hypothesis is unequivocal, because the hypothesis is either true or false.
-Statistical hypothesis testing, on the other hand, is a probabilistic operationalization of scientific hypothesis testing and, in lieu of its probabilistic nature, is subject to decision errors.
+Statistical hypothesis testing, on the other hand, is a probabilistic operationalization of scientific hypothesis testing \cite{meehl1978theoretical} and, in lieu of its probabilistic nature, is subject to decision errors.
 Such decision errors are the topic of this paper.
@@
 Conversely, when the alternative hypothesis is true in the population and $H_1$ is accepted ('$H_1$'), this is a true positive (lower right cell).
-The probability of finding a positive if $H_1$ is true is the power ($1-\beta$), which is also called the sensitivity of the test.
+The probability of finding a statistically significant result if $H_1$ is true is the power ($1-\beta$), which is also called the sensitivity of the test.
 Power is a positive function of the (true) population effect size, the sample size, and the alpha of the study, such that higher power can always be achieved by altering either the sample size or the alpha level \cite{Aberson2010-xa}.
@@
 
-Recent debate about false positives has overtaken science and psychological science in particular.
+Recent debate about false positives has received much attention in science and psychological science in particular.
 The Reproducibility Project Psychology (RPP), which replicated 100 effects reported in prominent psychology journals in 2008, found that only 36\% of these effects were statistically significant in the replication \cite{Open_Science_Collaboration2015-zs}.
@@
 The concern for false positives has overshadowed the concern for false negatives in the recent debate, which seems unwarranted.
-Cohen \cite{Cohen1962-jc} was the first to indicate that psychological science was (severely) underpowered, which is defined as the chance of finding an effect in the sample is lower than 50\% when there is truly an effect in the population.
+Cohen \cite{Cohen1962-jc} was the first to indicate that psychological science was (severely) underpowered, which is defined as the chance of finding a statistically significant effect in the sample lower than 50\% when there is truly an effect in the population.
 This has not changed throughout the subsequent fifty years \cite{Bakker2012-tf,Fraley2014-xs}.
-In other words, no evidence exists that the problem of false negatives has been resolved in psychology.
+Given that the complement of true positives (i.e., power) are false negatives, no evidence either exists that the problem of false negatives has been resolved in psychology.
 Moreover, Fiedler, Kutzner, and Krueger \cite{Fiedler2012-gx} worry that an increased focus on false positives is too shortsighted, arguing that false negatives are more difficult to detect than false positives.
 They also argue that, because of the focus on statistically significant results, negative results are less likely to be the subject of replications than positive results, decreasing the probability of detecting a false negative.
+Additionally, the Positive Predictive Value (PPV; the number of statistically significant effects that are true \cite{Ioannidis2005-am}) has been a major point of discussion in recent years, whereas the Negative Predictive Value (NPV) is rarely mentioned.
 
@@
 Hence we expect little $p$-hacking and substantial evidence of false negatives in reported gender effects in psychology.
-Finally, as another application, we applied the Fisher test to the 64 nonsignificant results of the RPP \cite{Open_Science_Collaboration2015-zs} to examine whether at least one of these nonsignificant results may actually be a false negative.
+Finally, as another application, we applied the Fisher test to the 64 nonsignificant replication results of the RPP \cite{Open_Science_Collaboration2015-zs} to examine whether at least one of these nonsignificant results may actually be a false negative.
 
@@
 More specifically, as sample size or true effect size increases, the probability distribution of one $p$-value becomes increasingly right-skewed.
-These regularities also generalize to a set of independent $p$-values, which are uniformly distributed when there is no population effect and right-skew distributed when there is a population effect, with more right-skew as the population effect and/or precision increases.
+These regularities also generalize to a set of independent $p$-values, which are uniformly distributed when there is no population effect and right-skew distributed when there is a population effect, with more right-skew as the population effect and/or precision increases \cite{Fisher1925-jl}.
 
 Considering that the present paper focuses on false negatives, we primarily examine nonsignificant $p$-values and their distribution.
-Since the test we apply requires random variables distributed between 0 and 1, we apply the following transformation to each  nonsignificant $p$-value
+Since the test we apply is based on nonselected $p$-values, it requires random variables distributed between 0 and 1.
+We apply the following transformation to each nonsignificant $p$-value that is selected
 \begin{equation}
@@
 Note this transformation retains the distributional properties of the original $p$-values for the selected nonsignificant results.
+Both one-tailed and two-tailed tests can be included in this way.
 
@@
 When applied to transformed nonsignificant $p$-values (see Equation \ref{pistar}) the Fisher test tests for evidence against $H_0$ in a set of nonsignificant $p$-values.
-In other words, the null we test with the Fisher test is that all included nonsignificant results are true negatives.
+In other words, the null hypothesis we test with the Fisher test is that all included nonsignificant results are true negatives.
 The Fisher test statistic is calculated as
@@
 We estimated the power of detecting false negatives with the Fisher test as a function of sample size $N$, true correlation effect size $\eta$, and $k$ nonsignificant test results (procedure described in Appendix A).
-The three levels of sample size (33, 62, 119) correspond to the  25th, 50th (median) and 75th percentiles of the degrees of freedom of reported $t$, $F$, and $r$ statistics in eight flagship psychology journals (see Application 1 below).
+The three levels of sample size used in our simulation study (33, 62, 119) correspond to the  25th, 50th (median) and 75th percentiles of the degrees of freedom of reported $t$, $F$, and $r$ statistics in eight flagship psychology journals (see Application 1 below).
 Degrees of freedom of these statistics are directly related to sample size, for instance, for a two-group comparison including 100 people, df = 98.
@@
 Results for all 5,400 conditions can be found on the OSF (\url{osf.io/qpfnw}).
-The results indicate that the Fisher test is a powerful method to test for a false negative among nonsignificant results when there are not only small effects investigated in small samples.
-For example, for small true effect sizes ($\eta=.1$), 50, 25, 7 nonsignificant results are required to obtain a power of 69\%, 85\%, 83\% for sample sizes of 33, 62, and 119, respectively.
-For medium true effects ($\eta=.25$), small samples ($N=33$) and three nonsignificant results already provide 89\% power for detecting a false negative with the Fisher test.
-For large effects ($\eta=.4$), small samples and 2 nonsignificant results already almost always detects all false negatives.
+The results indicate that the Fisher test is a powerful method to test for a false negative among nonsignificant results.
+For example, for small true effect sizes ($\eta=.1$), 25 nonsignificant results from medium samples result in 85\% power (7 nonsignificant results from large samples yield 83\% power).
+For medium true effects ($\eta=.25$), three nonsignificant results from small samples ($N=33$) already provide 89\% power for detecting a false negative with the Fisher test.
+For large effects ($\eta=.4$), 2 nonsignificant results from small samples already almost always detects all false negatives.
 
@@
 APA style is defined as the format where the type of test statistic is reported, followed by the degrees of freedom (if applicable), the observed test value, and the $p$-value (e.g., $t(85)=2.86, p=.005$; \cite{American_Psychological_Association2010-qe}).
-The \texttt{statcheck} package also recalculates $p$-values; we used only these recalculated $p$-values to eliminate rounding errors \cite{Bakker2011-hg,Nuijten2015-od}.
-Table \ref{tab:tab3} depicts the journals, the timeframe and summaries of the results extracted.
+The \texttt{statcheck} package also recalculates $p$-values.
 We reuse the data from Nuijten et al.
 (\url{osf.io/gdr4q};\cite{Nuijten2015-od}).
+Table \ref{tab:tab3} depicts the journals, the timeframe, and summaries of the results extracted.
 The database also includes $\chi^2$ results, which we did not use in our analyses because effect sizes based on these results are not readily mapped on the correlation scale.
@@
 
-The analyses reported in this paper use the recalculated $p$-values to eliminate potential errors in the reported $p$-values.
+The analyses reported in this paper use the recalculated $p$-values to eliminate potential errors in the reported $p$-values \cite{Bakker2011-hg,Nuijten2015-od}.
 However, our recalculated $p$-values assumed that all other test statistics (degrees of freedom, test values of $t$, $F$, or $r$) are correctly reported.
-These errors,  may have affected the results of our analyses.
+These errors may have affected the results of our analyses.
 Since most $p$-values and corresponding test statistics were consistent in our dataset (\Sexpr{round((dim(dat)[1] - sum(dat$Error[!is.na(dat$Error)])) / dim(dat)[1] * 100,1)}\%), we do not believe these typing errors substantially affected our results and conclusions based on them.
@@
 \caption{Summary table of articles downloaded per journal, their mean number of results, and proportion of (non)significant results.
-Statistical significance was determined using $\alpha=.05$, two-tailed}
+Statistical significance was determined using $\alpha=.05$, two-tailed test}
 \rowcolors{2}{gray!25}{white}
@@
 
-First, we compared the observed nonsignificant effect size distribution to the expected nonsignificant effect size distribution under $H_0$.
+First, we compared the observed nonsignificant effect size distribution (computed with observed test results) to the expected nonsignificant effect size distribution under $H_0$.
 The expected effect size distribution under $H_0$ was approximated using simulation.
@@
 The collection of simulated results approximates the expected effect size distribution under $H_0$, assuming independence of test results.
-This expected effect size distribution was compared to the observed effect size distribution (i) across all journals and (ii) per journal.
+We inspected this possible dependency with the intra-class correlation ($ICC$), where $ICC=1$ indicates full dependency and $ICC=0$ indicates full independence.
+For the set of observed results, the ICC for $p$-values was .001, indicating independence of $p$-values within a paper.
+The resulting, expected effect size distribution was compared to the observed effect size distribution (i) across all journals and (ii) per journal.
 To test for differences between the expected and observed nonsignificant effect size distributions we applied the Kolmogorov-Smirnov test.
@@
 For the entire set of nonsignificant results across journals, Figure \ref{fig:fig3} indicates that there is substantial evidence of false negatives.
-Under $H_0$, 46\% of all observed effects is expected to be within the range $0\leq|\eta|<.1$, as can be seen in the left panel of Figure \ref{fig:fig3} highlighted by the lowest grey line.
+Under $H_0$, 46\% of all observed effects is expected to be within the range $0\leq|\eta|<.1$, as can be seen in the left panel of Figure \ref{fig:fig3} highlighted by the lowest grey line (dashed).
 However, of the observed effects, only 26\% fall within this range, as highlighted by the lowest black line.
@@
 \caption{Observed and expected (adjusted and unadjusted) effect size distribution for statistically nonsignificant APA results reported in eight psychology journals.
+Grey lines depict expected values; black lines depict observed values.
 The three vertical dotted lines correspond to a small, medium, large effect, respectively.
-Legenda includes Kolmogorov-Smirnov test results.}
+Header includes Kolmogorov-Smirnov test results.}
 \label{fig:fig3}
@@
 
-Because effect sizes and their distribution overestimate population effect size, particularly when sample size is small \cite{Voelkle2007-at,Hedges1981-og}, we also compared the observed and expected adjusted nonsignificant effect sizes (right panel of Figure \ref{fig:fig3}).
-Unsurprisingly, the distribution of adjusted effect sizes of nonsignificant results tells the same story; observed effect sizes are larger than expected effect sizes.
+Because effect sizes and their distribution overestimate population effect size, particularly when sample size is small \cite{Voelkle2007-at,Hedges1981-og}, we also compared the observed and expected adjusted nonsignificant effect sizes that correct for such overestimation of effect sizes (right panel of Figure \ref{fig:fig3}; see Appendix B).
+The distribution of adjusted effect sizes of nonsignificant results tells the same story; observed effect sizes are larger than expected effect sizes.
 For instance, the distribution of adjusted reported effect size suggests 49\% of effect sizes are at least small, whereas under the $H_0$ only 22\% is expected.
@@
 
-The Fisher test was applied to the nonsignificant test results of each of the 14,765 papers separately, to inspect whether $p$-values within a paper deviate from what can be expected under the $H_0$.
+The Fisher test was applied to the nonsignificant test results of each of the 14,765 papers separately, to inspect for evidence of false negatives.
+More technically, we inspected whether $p$-values within a paper deviate from what can be expected under the $H_0$ (i.e., uniformity).
+If $H_0$ is in fact true, our results would be that there is evidence for false negatives in 10\% of the papers (a meta-false positive).
 Table \ref{tab:tab4} shows the number of papers with evidence for false negatives, specified per journal and per $k$ number of nonsignificant test results.
@@
 Consequently, we observe that journals with articles containing a higher number of nonsignificant results, such as JPSP, have a higher proportion of articles with evidence of false negatives.
+This is the result of higher power of the Fisher method when there are more nonsignificant results.
 
@@
 This decreasing evidence over time cannot be explained by a decrease in sample size over time, as sample size in psychology articles has stayed stable across time (see Figure \ref{fig:fig5}).
-One (partial) explanation of this surprising result is that in the early days researchers primarily used to report more APA results with 'marginally significant' $p$-values (i.e., $p$-values slightly larger than .05), compared to nowadays.
+One (partial) explanation of this surprising result is that in the early days researchers primarily reported fewer APA results and used to report relatively more APA results with 'marginally significant' $p$-values (i.e., $p$-values slightly larger than .05), compared to nowadays.
 This explanation is supported by both a smaller number of reported APA results in the past and the smaller mean reported nonsignificant $p$-value (\Sexpr{round(mean(dat$Reported.P.Value[dat$Reported.Comparison == '=' & dat$years.y.
@@
 We calculated that the required number of statistical results for the Fisher test, given $r=.11$ \cite{Hyde2005-gj} and 80\% power, is 15 $p$-values per condition, requiring 90 results in total.
-.
 However, the six categories are unlikely to occur equally throughout the literature, hence we sampled 90 significant and 90 nonsignificant results pertaining to gender, with an expected cell size of 30 if results are equally distributed across the six cells of our design.
@@
 Similarly, applying the Fisher test to nonsignificant gender results without stated expectation yielded evidence of at least one false negative ($\chi^2(174)=324.374$, $p<.001$).
-Unfortunately we could not examine whether evidential value of gender effects is dependent on the hypothesis/expectation of the researcher, because these effects are most frequently reported without stated expectations.
+Unfortunately, we could not examine whether evidential value of gender effects is dependent on the hypothesis/expectation of the researcher, because these effects are most frequently reported without stated expectations.
 
@@
 
-Out of the 100 replicated studies in the RPP, 64 did not yield a statistically significant effect sizee, despite the fact that high replication power was one of the aims of the project \cite{Open_Science_Collaboration2015-zs}.
+Out of the 100 replicated studies in the RPP, 64 did not yield a statistically significant effect size, despite the fact that high replication power was one of the aims of the project \cite{Open_Science_Collaboration2015-zs}.
 Regardless, the authors suggest "\textit{… that at least one replication could be a false negative}" (p.
@@
 Of the 64 nonsignificant studies in the RPP data (\url{osf.io/fgjvw}), we selected the 63 nonsignificant studies with a test statistic.
+We eliminated one result because it was a regression coefficient that could not be used in the following procedure.
 We first applied the Fisher test to the nonsignificant results, after transforming them to variables ranging from 0 to 1 using equations \ref{pistar} and \ref{fishertest}.
@@
 To this end, we adapted the Fisher method to detect the presence of at least one false negative in a set of statistically nonsignificant results; simulations indicated it to be a powerful method for that purpose.
-The three applications indicated that (i) approximately two out of three psychology articles reporting nonsignificant results contain evidence for at least one false negative, (ii) nonsignificant results on gender effects contain evidence of true nonzero effects, and (iii) the statistically nonsignificant replications from the Reproducibility Project Psychology (RPP) do not warrant conclusions about the absence or presence of true zero effects underlying these nonsignificant results.
+The three applications indicated that (i) approximately two out of three psychology articles reporting nonsignificant results contain evidence for at least one false negative, (ii) nonsignificant results on gender effects contain evidence of true nonzero effects, and (iii) the statistically nonsignificant replications from the Reproducibility Project Psychology (RPP) do not warrant conclusions about the absence or presence of true zero effects underlying these nonsignificant results (RPP does yield less biased estimates of the effect; the original studies severely overestimated the effects of interest).
 
@@
 
-One assumption of the Fisher test is independence of $p$-values.
-In Application 1, we analyzed all statistically nonsignificant results reported in the papers for false negatives, which may result in dependent $p$-values within a paper.
-We inspected this possible dependency with the intra-class correlation ($ICC$), where $ICC=1$ indicates full dependency and $ICC=0$ indicates full independence.
-For the set of observed results, the ICC for p-values was .001, indicating independence of $p$-values within a paper.
-We therefore believe that our conclusions are not affected by this possible dependence.
-
 For all three applications, the Fisher tests' conclusions are limited to detecting at least one false negative in a \textit{set of results}.
@@
 Our results in combination with results of previous studies suggest that publication bias mainly operates on results of tests of main hypotheses, and less so on peripheral results.
-Another venue for future research is using the Fisher test to re-examine evidence in the literature on certain other effects or often-used covariates, such as age and race.
+Another venue for future research is using the Fisher test to re-examine evidence in the literature on certain other effects or often-used covariates, such as age and race, or to see if it helps researchers prevent dichotomous thinking with individual $p$-values \cite{Hoekstra2006}.
 Finally, the Fisher test may and is also used to meta-analyze effect sizes of different studies.
-Whereas Fisher used his method to test the null-hypothesis of an underlying true zero effect using several studies’ $p$-values, the method has recently been extended to test the same hypothesis using only statistically significant $p$-values.
+Whereas Fisher used his method to test the null-hypothesis of an underlying true zero effect using several studies’ $p$-values, the method has recently been extended to yield unbiased effect estimates using only statistically significant $p$-values.
 The principle of uniformly distributed $p$-values given the true effect size on which the Fisher method is based, also underlies newly developed methods of meta-analysis that adjust for publication bias, such as $p$-uniform \cite{Van_Assen2015-gg} and $p$-curve \cite{Simonsohn2014-dm}.
@@
 \section*{Appendix A}
+\label{apA}
 \subsection*{Examining statistical properties of the Fisher test}
@@
 \section*{Appendix B}
+\label{apB}
 \subsection*{Effect computation}
@@
 \bibliography{../bibliography/library}
-
-\section*{Author note}
-All research files, data, and analyses scripts are available for download at \url{https://github.com/chartgerink/2014tgtbf/archive/master.zip}. 
 \end{document}

### 2016-10-05 submission/manuscript.tex
Revisions after reading club

@@
 
-The analyses reported in this paper use the recalculated $p$-values to eliminate potential errors in the reported $p$-values.
+The analyses reported in this paper use the recalculated $p$-values to eliminate potential errors in the reported $p$-values \cite{Bakker2011-hg,Nuijten2015-od}.
 However, our recalculated $p$-values assumed that all other test statistics (degrees of freedom, test values of $t$, $F$, or $r$) are correctly reported.
-These errors,  may have affected the results of our analyses.
+These errors may have affected the results of our analyses.
 Since most $p$-values and corresponding test statistics were consistent in our dataset (90.7\%), we do not believe these typing errors substantially affected our results and conclusions based on them.
@@
 These differences indicate that larger nonsignificant effects are reported in papers than expected under a null effect.
-This indicates the presence of false negatives, which is confirmed by the Kolmogorov-Smirnov test, $D=0.25$, $p<.000000000000001$.
+This indicates the presence of false negatives, which is confirmed by the Kolmogorov-Smirnov test, $D=0.3$, $p<.000000000000001$.
 Results were similar when the nonsignificant effects were considered separately for the eight journals, although deviations were smaller for the Journal of Applied Psychology (see \href{../figures/S1Fig}{Figure S1} for results per journal).
@@
 This decreasing evidence over time cannot be explained by a decrease in sample size over time, as sample size in psychology articles has stayed stable across time (see Figure \ref{fig:fig5}).
-One (partial) explanation of this surprising result is that in the early days researchers primarily used to report more APA results with 'marginally significant' $p$-values (i.e., $p$-values slightly larger than .05), compared to nowadays.
+One (partial) explanation of this surprising result is that in the early days researchers primarily reported fewer APA results and used to report relatively more APA results with 'marginally significant' $p$-values (i.e., $p$-values slightly larger than .05), compared to nowadays.
 This explanation is supported by both a smaller number of reported APA results in the past and the smaller mean reported nonsignificant $p$-value (0.222 in 1985, 0.386 in 2013).

### 2016-10-23 submission/manuscript.Rnw
Updates to analyses

@@
 }
+
+iccSS <- Anova(lm(dat$Computed[nsig] ~ dat$Source[nsig]), type="III")
+
 @
@@
 
+gend <- gend[!is.na(gend$final_code),]
+sum(gend$Computed > .05 & gend$significance == 'significant')
+gend <- gend[!(gend$Computed > .05 & gend$significance == 'significant'),]
+
 # 1 = null expected
@@
 {
-
     ggplot(gend, aes(x = Computed, fill = significance)) + 
-    geom_density(alpha = .3) + 
+    geom_density(alpha = .3, trim = TRUE) + 
     xlab(TeX("$P$-value")) + 
@@
 For the 178 results, only 15 clearly stated whether their results were as expected, whereas the remaining 163 did not.
-Illustrative of the lack of clarity in expectations is the following quote: "\textit{As predicted, there was little gender difference [...] p < .06.}" As a result, the conditions significant-$H_0$ expected, nonsignificant-$H_0$ expected, and nonsignificant-$H_1$ expected contained too few results for meaningful investigation of evidential value (i.e., with sufficient statistical power).
+Illustrative of the lack of clarity in expectations is the following quote: "\textit{As predicted, there was little gender difference [...] p < .06.}" There were two results that were presented as significant but contained $p$-values larger than .05; these two were dropped (i.e., 176 results were analyzed).
+As a result, the conditions significant-$H_0$ expected, nonsignificant-$H_0$ expected, and nonsignificant-$H_1$ expected contained too few results for meaningful investigation of evidential value (i.e., with sufficient statistical power).
 
@@
 \hline
-Significant    & 0           & \textbf{12}          & \textbf{76}             \\
+Significant    & 0           & \textbf{11}          & \textbf{75}             \\
 Nonsignificant & 2           & 1           & \textbf{87}     \\
@@
 Figure \ref{fig:fig6} presents the distributions of both transformed significant and non-significant $p$-values.
-For significant results, applying the Fisher test to the $p$-values showed evidential value for a gender effect both when an effect was expected ($\chi^2(24)=358.725$, $p<.001$) and when no expectation was presented at all ($\chi^2(152)=1093.884$, $p<.001$).
+For significant results, applying the Fisher test to the $p$-values showed evidential value for a gender effect both when an effect was expected ($\chi^2(22)=358.904$, $p<.001$) and when no expectation was presented at all ($\chi^2(15)=1094.911$, $p<.001$).
 Similarly, applying the Fisher test to nonsignificant gender results without stated expectation yielded evidence of at least one false negative ($\chi^2(174)=324.374$, $p<.001$).

### 2016-10-23 submission/manuscript.Rnw
Submission commit.

@@
 &    & True negative                     & False negative {[}Type II error{]} \\
+& & & \\
 & '$H_1$' & $\alpha$                             & $1-\beta$                             \\
@@
 The Reproducibility Project Psychology (RPP), which replicated 100 effects reported in prominent psychology journals in 2008, found that only 36\% of these effects were statistically significant in the replication \cite{Open_Science_Collaboration2015-zs}.
-Besides psychology, reproducibility problems have also been indicated in economics \cite{Camerer2016-zz} and medicine \cite{Begley2012-uc}.
+Besides in psychology, reproducibility problems have also been indicated in economics \cite{Camerer2016-zz} and medicine \cite{Begley2012-uc}.
 Although these studies suggest substantial evidence of false positives in these fields, replications show considerable variability in resulting effect size estimates \cite{Klein2014-jb, Stanley2014-pd}.
@@
 The debate about false positives is driven by the current overemphasis on statistical significance of research results \cite{Giner-Sorolla2012-wn}.
-This overemphasis is substantiated by the finding that >90\% of results in the psychology literature are statistically significant \cite{Open_Science_Collaboration2015-zs,Sterling1995-fe,Sterling1959-pf} despite low statistical power due to small sample sizes \cite{Cohen1962-jc,Sedlmeier1989-yc,Marszalek2011-rf,Bakker2012-tf}.
-Consequently, publications have become biased by overrepresenting statistically significant results \cite{Greenwald1975-ck}, which generally results in effect size overestimation in individual studies \cite{Nuijten2015-od} and in meta-analyses \cite{Van_Assen2015-gg,Lane_1978,Rothstein2005-zg,Borenstein2009-vs}.
+This overemphasis is substantiated by the finding that more than 90\% of results in the psychological literature are statistically significant \cite{Open_Science_Collaboration2015-zs,Sterling1995-fe,Sterling1959-pf} despite low statistical power due to small sample sizes \cite{Cohen1962-jc,Sedlmeier1989-yc,Marszalek2011-rf,Bakker2012-tf}.
+Consequently, publications have become biased by overrepresenting statistically significant results \cite{Greenwald1975-ck}, which generally results in effect size overestimation in both individual studies \cite{Nuijten2015-od} and meta-analyses \cite{Van_Assen2015-gg,Lane_1978,Rothstein2005-zg,Borenstein2009-vs}.
 The overemphasis on statistically significant effects has been accompanied by questionable research practices (QRPs, \cite{John2012-uj}) such as erroneously rounding p-values towards significance, which for example occurred for 13.8\% of all $p$-values reported as "$p =.05$" in articles from eight major psychology journals in the period 1985-2013 \cite{Hartgerink2016-mm}.
@@
 Given that the complement of true positives (i.e., power) are false negatives, no evidence either exists that the problem of false negatives has been resolved in psychology.
-Moreover, Fiedler, Kutzner, and Krueger \cite{Fiedler2012-gx} worry that an increased focus on false positives is too shortsighted, arguing that false negatives are more difficult to detect than false positives.
-They also argue that, because of the focus on statistically significant results, negative results are less likely to be the subject of replications than positive results, decreasing the probability of detecting a false negative.
-Additionally, the Positive Predictive Value (PPV; the number of statistically significant effects that are true \cite{Ioannidis2005-am}) has been a major point of discussion in recent years, whereas the Negative Predictive Value (NPV) is rarely mentioned.
+Moreover, Fiedler, Kutzner, and Krueger \cite{Fiedler2012-gx} expressed the concern that an increased focus on false positives is too shortsighted because false negatives are more difficult to detect than false positives.
+They also argued that, because of the focus on statistically significant results, negative results are less likely to be the subject of replications than positive results, decreasing the probability of detecting a false negative.
+Additionally, the Positive Predictive Value (PPV; the number of statistically significant effects that are true \cite{Ioannidis2005-am}) has been a major point of discussion in recent years, whereas the Negative Predictive Value (NPV) has rarely been mentioned.
 
@@
 We begin by reviewing the probability density function of both an individual $p$-value and a set of independent $p$-values as a function of population effect size.
-Subsequently, we propose  a method to test whether a collection of nonsignificant results across papers deviates from what would be expected under the $H_0$.
-We also propose a method to test whether nonsignificant results deviate from $H_0$ within a paper.
+Subsequently, we apply the Kolmogorov-Smirnov test to inspect whether a collection of nonsignificant results across papers deviates from what would be expected under the $H_0$.
+We also propose an adapted Fisher method to test whether nonsignificant results deviate from $H_0$ within a paper.
 These methods will be used to test whether there is evidence for false negatives in the psychology literature.
@@
 \end{equation}
-where $p_i$ is the  reported nonsignificant $p$-value and $\alpha$ is the selected significance cutoff (i.e., $\alpha=.05$).
-Note this transformation retains the distributional properties of the original $p$-values for the selected nonsignificant results.
+where $p_i$ is the  reported nonsignificant $p$-value, $\alpha$ is the selected significance cutoff (i.e., $\alpha=.05$), and $p^*_i$ the transformed $p$-value.
+Note that this transformation retains the distributional properties of the original $p$-values for the selected nonsignificant results.
 Both one-tailed and two-tailed tests can be included in this way.
@@
 
-We estimated the power of detecting false negatives with the Fisher test as a function of sample size $N$, true correlation effect size $\eta$, and $k$ nonsignificant test results (procedure described in Appendix A).
+We estimated the power of detecting false negatives with the Fisher test as a function of sample size $N$, true correlation effect size $\eta$, and $k$ nonsignificant test results (the full procedure is described in Appendix A).
 The three levels of sample size used in our simulation study (33, 62, 119) correspond to the 25th, 50th (median) and 75th percentiles of the degrees of freedom of reported $t$, $F$, and $r$ statistics in eight flagship psychology journals (see Application 1 below).
@@
 For medium true effects ($\eta=.25$), three nonsignificant results from small samples ($N=33$) already provide 89\% power for detecting a false negative with the Fisher test.
-For large effects ($\eta=.4$), 2 nonsignificant results from small samples already almost always detects all false negatives.
+For large effects ($\eta=.4$), two nonsignificant results from small samples already almost always detects the existence of false negatives (not shown in Table \ref{tab:tab2}).
 
@@
 We inspected this possible dependency with the intra-class correlation ($ICC$), where $ICC=1$ indicates full dependency and $ICC=0$ indicates full independence.
-For the set of observed results, the ICC for $p$-values was .001, indicating independence of $p$-values within a paper.
+For the set of observed results, the ICC for nonsignificant $p$-values was \Sexpr{round(iccSS$Sum[2]/(iccSS$Sum[3]+iccSS$Sum[2]), 3)}, indicating independence of $p$-values within a paper.
 The resulting, expected effect size distribution was compared to the observed effect size distribution (i) across all journals and (ii) per journal.
@@
 
-Because effect sizes and their distribution overestimate population effect size, particularly when sample size is small \cite{Voelkle2007-at,Hedges1981-og}, we also compared the observed and expected adjusted nonsignificant effect sizes that correct for such overestimation of effect sizes (right panel of Figure \ref{fig:fig3}; see Appendix B).
+Because effect sizes and their distribution typically overestimate population effect size, particularly when sample size is small \cite{Voelkle2007-at,Hedges1981-og}, we also compared the observed and expected adjusted nonsignificant effect sizes that correct for such overestimation of effect sizes (right panel of Figure \ref{fig:fig3}; see Appendix B).
 The distribution of adjusted effect sizes of nonsignificant results tells the same story; observed effect sizes are larger than expected effect sizes.
@@
 Overall results (last row) indicate that 47.1\% of all articles show evidence of false negatives (i.e.
-6,951 articles), and 66.7\% of articles reporting at least one result.
+6,951 articles).
+Of articles reporting at least one nonsignificant result, 66.7\% show evidence of false negatives, which is much more than the 10\% predicted by chance alone.
 
@@
 All                 & Evidence FN       & 47.1\% & 46.5\% & 45.1\% & 29.9\% & 34.3\% & 59.1\% & 64.6\% & 38.4\% & 39.3\% \\
-& Evidence FN $k\geq1$ & 66.7\% & 69.6\% & 57.6\% & 49.4\% & 61.7\% & 70.2\% & 81.3\% & 51.9\% & 59.2\% \\
+& \pbox{1.5cm}{Evidence FN $k\geq1$} & 66.7\% & 69.6\% & 57.6\% & 49.4\% & 61.7\% & 70.2\% & 81.3\% & 51.9\% & 59.2\% \\
 & Count             & 6,951   & 1,061   & 277    & 371    & 699    & 456    & 2,641   & 831    & 615   \\
@@
 We also checked whether evidence of at least one false negative at the article level changed over time.
-Figure \ref{fig:fig4} depicts evidence across all articles per year, as a function of time (1985-2013); point size in the figure corresponds to the mean number of nonsignificant results per article (mean $k$) in that year.
-Interestingly, the proportion of articles with evidence for false negatives decreased from \Sexpr{round(mydf$y[1]*100, 0)}\% in 1985 to \Sexpr{round(mydf$y[29]*100, 0)}\% in 2013, despite the increase in mean $k$ (from \Sexpr{round(mydf$count[1], 2)} in 1985 to \Sexpr{round(mydf$y[29], 2)} in 2013).
-This decreasing evidence over time cannot be explained by a decrease in sample size over time, as sample size in psychology articles has stayed stable across time (see Figure \ref{fig:fig5}).
-One (partial) explanation of this surprising result is that in the early days researchers primarily reported fewer APA results and used to report relatively more APA results with 'marginally significant' $p$-values (i.e., $p$-values slightly larger than .05), compared to nowadays.
+Figure \ref{fig:fig4} depicts evidence across all articles per year, as a function of year (1985-2013); point size in the figure corresponds to the mean number of nonsignificant results per article (mean $k$) in that year.
+Interestingly, the proportion of articles with evidence for false negatives decreased from \Sexpr{round(mydf$y[1]*100, 0)}\% in 1985 to \Sexpr{round(mydf$y[29]*100, 0)}\% in 2013, despite the increase in mean $k$ (from \Sexpr{round(mydf$count[1], 2)} in 1985 to \Sexpr{round(mydf$count[29], 2)} in 2013).
+This decreasing proportion of papers with evidence over time cannot be explained by a decrease in sample size over time, as sample size in psychology articles has stayed stable across time (see Figure \ref{fig:fig5}).
+One (at least partial) explanation of this surprising result is that in the early days researchers primarily reported fewer APA results and used to report relatively more APA results with 'marginally significant' $p$-values (i.e., $p$-values slightly larger than .05), compared to nowadays.
 This explanation is supported by both a smaller number of reported APA results in the past and the smaller mean reported nonsignificant $p$-value (\Sexpr{round(mean(dat$Reported.P.Value[dat$Reported.Comparison == '=' & dat$years.y.
@@
 The Fisher test proved a powerful test to inspect for false negatives in our simulation study, where three nonsignificant results already results in high power to detect evidence of a false negative if sample size is at least 33 per result and the population effect is medium.
-Journals differed in the proportion of papers that showed evidence of false negatives, but this was largely due to differences in the amount of nonsignificant results reported.
+Journals differed in the proportion of papers that showed evidence of false negatives, but this was largely due to differences in the number of nonsignificant results reported in these papers.
 More generally, we observed that more nonsignificant results were reported in 2013 than in 1985.
@@
 Despite recommendations of increasing power by increasing sample size, we found no evidence for increased sample size (see Figure \ref{fig:fig5}).
-To the contrary, the data indicate that sample sizes have been remarkably stable since 1985, despite the improved ease of collecting participants with data collection tools such as online services.
+To the contrary, the data indicate that average sample sizes have been remarkably stable since 1985, despite the improved ease of collecting participants with data collection tools such as online services.
 
@@
 
-Upon reanalysis of the 63 statistically nonsignificant replications within RPP we determined that many of these "failed" replications say hardly anything about whether there are truly no effects.
+Upon reanalysis of the 63 statistically nonsignificant replications within RPP we determined that many of these "failed" replications say hardly anything about whether there are truly no effects when using the adapted Fisher method.
 The Fisher test of these 63 nonsignificant results indicated some evidence for the presence of at least one false negative finding ($\chi^2(126)=155.2382$, $p=0.039$).
@@
 The explanation of this finding is that most of the RPP replications, although often statistically more powerful than the original studies, still did not have enough statistical power to distinguish a true small effect from a true zero effect \cite{Maxwell2015-yb}.
-Interpreting results of replications should therefore also take the precision of the estimate of both the original and replication into account \cite{Cumming2014-fi}.
+Interpreting results of replications should therefore also take the precision of the estimate of both the original and replication into account \cite{Cumming2014-fi} and publication bias of the original studies \cite{10.1371/journal.pone.0149794}.
 
@@
 We examined evidence for false negatives in nonsignificant results in three different ways.
-To this end, we adapted the Fisher method to detect the presence of at least one false negative in a set of statistically nonsignificant results; simulations indicated it to be a powerful method for that purpose.
+To this end, we adapted the Fisher method to detect the presence of at least one false negative in a set of statistically nonsignificant results.
+Simulations indicated the adapted Fisher test to be a powerful method for that purpose.
 The three applications indicated that (i) approximately two out of three psychology articles reporting nonsignificant results contain evidence for at least one false negative, (ii) nonsignificant results on gender effects contain evidence of true nonzero effects, and (iii) the statistically nonsignificant replications from the Reproducibility Project Psychology (RPP) do not warrant conclusions about the absence or presence of true zero effects underlying these nonsignificant results (RPP does yield less biased estimates of the effect; the original studies severely overestimated the effects of interest).
@@
 Hence, the interpretation of a significant Fisher test result pertains to the evidence of at least one false negative in all reported results, not the evidence for at least one false negative in the main results.
-Nonetheless, even when we focused only on the main results in application 3, the Fisher test does not indicate specifically which result is false negative, only whether there is evidence for a false negative in a set of results.
+Nonetheless, even when we focused only on the main results in application 3, the Fisher test does not indicate specifically which result is false negative, rather it only provides evidence for a false negative in a set of results.
 As such, the Fisher test is primarily useful to test a set of potentially underpowered results in a more powerful manner, albeit that the result then applies to the complete set.
@@
 Previous concern about power \cite{Cohen1962-jc,Sedlmeier1989-yc,Bakker2012-tf,Marszalek2011-rf}, which was even addressed by an APA Statistical Task Force in 1999 that recommended increased statistical power \cite{Wilkinson_APA_Task_Force_on_Statistical_Inference1999-ht}, seems not to have resulted in actual change \cite{Marszalek2011-rf}.
-A potential explanation for this lack of change is that researchers overestimate statistical power when designing a study for small effects \cite{Bakker2016-nj}.
-
-Reducing the emphasis on binary decisions in individual studies and increasing the emphasis on the precision of a study might help reduce the problem of decision errors.
+Potential explanations for this lack of change is that researchers overestimate statistical power when designing a study for small effects \cite{Bakker2016-nj} and can act strategically by running multiple underpowered studies rather than one large powerful study \cite{Bakker2012-tf}.
+
+Reducing the emphasis on binary decisions in individual studies and increasing the emphasis on the precision of a study might help reduce the problem of decision errors \cite{Cumming2014-fi}.
 For example, a large but statistically nonsignificant study might yield a confidence interval (CI) of the effect size of [-0.01; 0.05], whereas a small but significant study might yield a CI of [0.01; 1.30].
@@
 Using meta-analyses to combine estimates obtained in studies on the same effect may further increase the overall estimate’s precision.
-Although the emphasis on precision and the meta-analytic approach is fruitful in theory, we should realize that publication bias will result in precise but biased (overestimated) effect size estimates of meta-analyses \cite{Nuijten2015-kh}.
+Although the emphasis on precision and the meta-analytic approach is fruitful in theory, we should realize that publication bias will result in precise but biased (overestimated) effect size estimation of meta-analyses \cite{Nuijten2015-kh}.
 
@@
 
-To conclude, the three applications that were presented indicate that false negatives remain a problem in the psychology literature, despite the decreased attention and that we should be wary to interpret statistically nonsignificant results as there being no effect in reality.
+To conclude, our three applications indicate that false negatives remain a problem in the psychology literature, despite the decreased attention and that we should be wary to interpret statistically nonsignificant results as there being no effect in reality.
 One way to combat this interpretation of statistically nonsignificant results is to incorporate testing for potential false negatives, which the Fisher method facilitates in a highly approachable manner (a spreadsheet for carrying out such a test is available at \url{https://osf.io/tk57v/}).
@@
 First, we determined the critical value under the null distribution.
-Second, we determined the alternative distribution by computing the non-centrality parameter ($\delta=(\eta^2/1-\eta^2)N$; \cite{Steiger1997-qq,Smithson2001-aw}).
-Third, we calculated the probability that a result under the alternative distribution was, in fact, nonsignificant (i.e., $\beta$).
+Second, we determined the distribution under the alternative hypothesis by computing the non-centrality parameter ($\delta=(\eta^2/1-\eta^2)N$; \cite{Steiger1997-qq,Smithson2001-aw}).
+Third, we calculated the probability that a result under the alternative hypothesis was, in fact, nonsignificant (i.e., $\beta$).
 Fourth, we randomly sampled, uniformly, a value between $0-\beta$.

### 2016-10-23 submission/manuscript.tex
Submission commit.

@@
 We inspected this possible dependency with the intra-class correlation ($ICC$), where $ICC=1$ indicates full dependency and $ICC=0$ indicates full independence.
-For the set of observed results, the ICC for $p$-values was .001, indicating independence of $p$-values within a paper.
+For the set of observed results, the ICC for nonsignificant $p$-values was 0.001, indicating independence of $p$-values within a paper.
 The resulting, expected effect size distribution was compared to the observed effect size distribution (i) across all journals and (ii) per journal.
@@
 We also checked whether evidence of at least one false negative at the article level changed over time.
-Figure \ref{fig:fig4} depicts evidence across all articles per year, as a function of time (1985-2013); point size in the figure corresponds to the mean number of nonsignificant results per article (mean $k$) in that year.
-Interestingly, the proportion of articles with evidence for false negatives decreased from 77\% in 1985 to 55\% in 2013, despite the increase in mean $k$ (from 2.11 in 1985 to 0.55 in 2013).
-This decreasing evidence over time cannot be explained by a decrease in sample size over time, as sample size in psychology articles has stayed stable across time (see Figure \ref{fig:fig5}).
-One (partial) explanation of this surprising result is that in the early days researchers primarily reported fewer APA results and used to report relatively more APA results with 'marginally significant' $p$-values (i.e., $p$-values slightly larger than .05), compared to nowadays.
+Figure \ref{fig:fig4} depicts evidence across all articles per year, as a function of year (1985-2013); point size in the figure corresponds to the mean number of nonsignificant results per article (mean $k$) in that year.
+Interestingly, the proportion of articles with evidence for false negatives decreased from 77\% in 1985 to 55\% in 2013, despite the increase in mean $k$ (from 2.11 in 1985 to 4.52 in 2013).
+This decreasing proportion of papers with evidence over time cannot be explained by a decrease in sample size over time, as sample size in psychology articles has stayed stable across time (see Figure \ref{fig:fig5}).
+One (at least partial) explanation of this surprising result is that in the early days researchers primarily reported fewer APA results and used to report relatively more APA results with 'marginally significant' $p$-values (i.e., $p$-values slightly larger than .05), compared to nowadays.
 This explanation is supported by both a smaller number of reported APA results in the past and the smaller mean reported nonsignificant $p$-value (0.222 in 1985, 0.386 in 2013).
@@
 Previous concern about power \cite{Cohen1962-jc,Sedlmeier1989-yc,Bakker2012-tf,Marszalek2011-rf}, which was even addressed by an APA Statistical Task Force in 1999 that recommended increased statistical power \cite{Wilkinson_APA_Task_Force_on_Statistical_Inference1999-ht}, seems not to have resulted in actual change \cite{Marszalek2011-rf}.
-A potential explanation for this lack of change is that researchers overestimate statistical power when designing a study for small effects \cite{Bakker2016-nj}.
+Potential explanations for this lack of change is that researchers overestimate statistical power when designing a study for small effects \cite{Bakker2016-nj} and can act strategically by running multiple underpowered studies rather than one large powerful study \cite{Bakker2012-tf}.
 
-Reducing the emphasis on binary decisions in individual studies and increasing the emphasis on the precision of a study might help reduce the problem of decision errors.
+Reducing the emphasis on binary decisions in individual studies and increasing the emphasis on the precision of a study might help reduce the problem of decision errors \cite{Cumming2014-fi}.
 For example, a large but statistically nonsignificant study might yield a confidence interval (CI) of the effect size of [-0.01; 0.05], whereas a small but significant study might yield a CI of [0.01; 1.30].

### 2016-10-23 submission/manuscript.Rnw
Update abstract

@@
 Due to its probabilistic nature, Null Hypothesis Significance Testing (NHST) is subject to decision errors.
-The concern for false positives has overshadowed the concern for false negatives in the recent debates in psychology, which seems unwarranted.
-Our study demonstrates the importance of paying attention to false negatives alongside those significant results that may be 'too good to be true'; nonsignificant results may be 'too good to be false'.
+The concern for false positives has overshadowed the concern for false negatives in the recent debates in psychology.
+This is unwarranted,  since  reported statistically nonsignificant findings may just be 'too good to be false'.
 We examined evidence for false negatives in nonsignificant results in three different ways.
-To this end, we adapted the Fisher method to detect the presence of at least one false negative in a set of statistically nonsignificant results; simulations indicated it to be a powerful method for that purpose.
-The three applications indicated that (i) approximately two out of three (66.7\%) psychology articles reporting nonsignificant results contain evidence for at least one false negative, (ii) nonsignificant results on gender effects contain evidence of true nonzero effects, and (iii) the statistically nonsignificant replications from the Reproducibility Project Psychology (RPP) do not warrant conclusions about the absence or presence of true zero effects underlying these nonsignificant results.
-False negatives deserve more attention in the debate among psychologists, because there is sufficient evidence in these three applications to indicate that false negatives are a threat to the scientific discovery process; it can be considered a waste of resources if effects are studied but results are neglected due to the lack of statistical power.
+We adapted the Fisher method to detect the presence of at least one false negative in a set of statistically nonsignificant results.
+Simulations show that the adapted Fisher method generally is a powerful method to detect false negatives.
+We examined evidence for false negatives in the psychology literature in three applications of the adapted Fisher method.
+These applications indicate that (i) the observed effect size distribution of nonsignificant effects exceeds the expected distribution assuming a null-effect, and approximately two out of three (66.7\%) psychology articles reporting nonsignificant results contain evidence for at least one false negative, (ii) nonsignificant results on gender effects contain evidence of true nonzero effects, and (iii) the statistically nonsignificant replications from the Reproducibility Project Psychology (RPP) do not warrant conclusions about the absence or presence of true zero effects underlying these nonsignificant results.
+We conclude that false negatives deserve more attention in the current debate on statistical practices in psychology.
+Neglecting effects due to a lack of statistical power can lead to a waste of research resources and stifle the scientific discovery process.
 \end{abstract}

### 2017-01-16 submission/review round 1/review-rebuttal.md
First draft review response

Dear Editor Vazire,

We would like to kindly thank you for organizing the review of our manuscript and your own extensive comments. We appreciate the constructive comments and provide a point-by-point reply to both below. We hereby submit our revised manuscript.

The main points of your comments seem to revolve around (1) the interpretation of (non)significance, (2) an overstatement of the RP:P reanalysis' findings, and (3) the effect of p-hacking in relation to false negatives. First, we do not regard the interpretation of significance explicitly in this paper, given that it has been inspected before by Hoekstra et al. (2008) and goes beyond the specific scope of inspecting evidence for false negatives in nonsignificant results. Second, the RP:P reanalysis indeed should be presented more nuanced, which we attempt. Third,

The main points of the reviewer's comments revolved around (1) the use of ICC for non-normal data, (2) some questions and remarks on how the results can and should be interpreted. The interdependency of p-values seems not to be a problem for p-values both theoretically and based on the data. We replied to the questions, and have made some revisions to explicate several of the underlying ideas in the revised manuscript.

Yours sincerely,

Chris Hartgerink, also on behalf of Jelte Wicherts and Marcel van Assen

# Editor comments

Dear Mr Chris H.J. Hartgerink,

Thank you for your submission to Collabra. I was able to get one reviewer
with expertise in quantitative methods, and this reviewer did an outstanding
job. I also independently read the manuscript before consulting this
review. Both of us found much to like in your manuscript, and identified
some issues that need to be addressed. Thus, I invite you to submit a
revised version of this paper for further consideration at Collabra.

The reviewer did an outstanding job of articulating their concerns with the
paper and I will not summarize all of their points in my letter. I would
like you to address all of their concerns in the letter of response and if
possible in the revised paper. Below I will add a few points of my own.

First, your arguments rest on the assumption that authors and/or readers are
interpreting the non-significant results in the papers as evidence for the
null. There are several alternative possibilities. One is that some of
these null results may actually be interpreted as evidence against the null,
particularly those that are marginally significant. Second, authors and
readers may sometimes acknowledge that their non-significant results are
inconclusive and may explicitly resist treating them as evidence for the
null. Third, they may be ignored altogether (though I admit this is less
likely since you are not using non-significant results that are only
reported in tables, and only using ones that are reported in APA style in
the text). This is not necessarily a problem for all of your points, but it
does matter for the more conceptual argument about the potential harm that
false negatives do to our field. Thus, I would caution you against assuming
that non-significant results are always interpreted as evidence for the
null. You may also consider excluding results with p-values between .05 and
.10 from your analyses, since these are especially likely to have been
interpreted as evidence against the null. I don’t have a strong feeling
about this last suggestion – what’s more important to me is that you
avoid making a strong assumption about how authors and readers are
interpreting these non-significant findings (except in cases where you coded
this, as perhaps in application 2).

## Reply to Editor Comment 1

As we noted in Application 2, determining the interpretation of a finding is rather difficult. Given previous investigation, it appears to be quite common that nonsignificant results are interpreted as that the null is true (see Hoekstra et al. 2008 reference in the manuscript). However, we do not regard the interpretation of the results themselves explicitly throughout Application 1, given that this falls outside the research question of "is there evidence for false negatives in nonsignificant results?". We tried to make this more explicit in the revised manuscript.

As such, we do not assume "that non-significant results are always interpreted as evidence for the null", but want to show to the reader that if they identify with doing so, they should beware because of these results.

We reran the analyses with alpha = .10 as suggested, and concluded that albeit different, the notion that there is evidence for >= 1 FN in the papers remains; the 66.7% changes to 42.7% after excluding 2009 papers that have no nonsignificant results when the alpha is shifted to .10. This is of course also the effect of lower power to detect FN by decreasing the amount of nonsignificant p-values analyzed. We do not present these results in the revised manuscript, but include the code in our OSF project to do so.

________

Regarding the analyses of RP:P, you make an important point about the fact
that many of the non-significant results are inconclusive, and you also
acknowledge that the authors of the RP:P themselves point this out.
However, I think it is somewhat of a straw man to criticize the RP:P for not
having enough power to differentiate between a null result and a true effect
of r = .10. I don’t think many people think that the RP:P was intended to
have that kind of power/precision. Moreover, your own test has very low
precision for testing this (since the confidence interval goes all the way
from 0 to 100% of non-significant findings being potential false negatives).
Thus, I would suggest focusing more on the analyses examining the
possibility that some of the RP:P non-significant findings are actually
false negatives of medium or large effects. Here, you can rule out more
possibilities (i.e., you can say that your analyses suggest there are fewer
than 21 medium effects that were non-significant in the RP:P replications,
etc.). Perhaps this is my bias showing through, but I also thought that a
few sentences in this section were overstatements. Specifically, you write
that the RP:P results “say hardly anything about whether there are truly
no effects” (p. 19) – I agree that this statement is correct, but I
think it places a lot of emphasis on distinguishing between null and very
small effects, so holds the RP:P to a very high standard. That’s fair
enough, but it may not be clear to readers that this is the standard you are
using. Similarly, you also write “any conclusions on the validity of
individual effects based on “failed” replications, as determined by
statistical significance, is unwarranted and irresponsible.” First, the
word “irresponsible” implies that this is a common interpretation (i.e.,
that people are doing this irresponsible thing) – is it? Second, I am not
familiar with every single result in the RP:P, but is it really the case
that none of the individual results were strong enough to warrant some kind
of conclusion on the validity of that individual effect? I could imagine
that some of the studies had sufficient precision to draw some conclusion
based on a non-significant result. I am nitpicking here, and I will admit
that I am probably more sensitive than the average reader to statements that
could easily be misinterpreted, so feel free to take these suggestions or
leave them.

## Reply to Editor Comment 2

Before responding, we would like to disclose that this analysis was done by CHJH and MvA, who both participated in the aggregate analyses of RP:P and actually conducted this analysis for a reply to an RP:P comment as part of the RP:P team (this comment remained unpublished).

We agree that the power of the Fisher test to detect false negatives in specific studies is low and our analysis only wants to provide a way of viewing the RP:P data a bit more nuanced than how many people have interpreted them ("only 36% of psych studies replicate!"). RP:P might also have false negatives, and this analysis shows it can be any combination of zero, small, medium, and large effects in the population that give rise to this rate of reproducibility.

Nonetheless, we agree that our analysis might be confounded with assessing individual studies. We have incorporated several references in the revised manuscript that do try to tackle this to clearly distance the analysis in this paper.

________

On page 21, you discuss “potential explanations” for the lack of change
in power/sample size in the field over time. One piece missing from your
explanation, in my opinion, is p-hacking. P-hacking lets us get significant
results at a high rate even when our sample sizes suggest that our studies
should be underpowered. Likewise, in the paragraph beginning “Reducing
the emphasis on binary”, you also do not mention reducing p-hacking as
another route to improving the situation. Transparency/disclosure
requirements would go a long way to preventing people from being able to
p-hack their way to significant results using small samples. If they were no
longer able to do that, they would be required to get larger samples in
order to detect the phenomena they’re studying. Again, feel free to take
or leave this suggestion, but it stood out to me as an important missing
piece of the puzzle in this section.

## Reply to Editor Comment 3

We agree with the reasoning of the editor that power goes towards 1 when researchers start to p-hack. However, to analyze the relation between p-hacking and power goes beyond the scope of the paper, given that there are many parameters that can vary (see also Hartgerink et al. 2016 for difficulties of modeling p-hacking behaviors and their effects on p-value distributions).

We tried to incorporate a constructive framing of the problem of false negatives, and we regard p-hacking primarily as the result of the emphasis on binary decisions instead of the other way around (just like publication bias). We incorporated a few sentences on this in the revision, given that this is one potential explanation as well.

________

Smaller points:
-On page 10, you write “because effect size […] are typically
overestimated population effect sizes” – is this true even for non-focal
tests?

## Reply to Editor Comment 4

Yes. It is similar to how Hedges' g corrects for small sample bias in Cohen's d, regardless of whether it is focal or not (one can also think of omega-squared in ANOVA's).

________

-On page 13, you write the mean effect is r = .257 in 1985 and r = .187 in
2013 – what are these numbers referring to?

## Reply to Editor Comment 5

These numbers refer to the correlation effect size.

________

-Figure 4 – I wonder if this would be more useful as a percentage of all
papers, not as a percentage of papers that report a non-significant result?
Both are interesting, I’m not sure which one readers will find more
interesting.

## Reply to Editor Comment 6

The results in Figure 4 only talk about the papers that report nonsignificant results, so for parsimony of interpretation we prefer to retain this format (we discussed this during the drafting as well).

________

-Figure 5 – how confident are you that degrees of freedom are a good proxy
for N?

## Reply to Editor Comment 7

Degrees of freedom is equal to the sample size minus a constant (e.g., sample size minus the number of groups in ANOVA/t-tests), so we are confident in using this as a proxy.

________

-What does the Fisher test mean for the significant results in the gender
analysis? Does the result just mean that at least one of those is a true
non-null effect? Is this interesting?

## Reply to Editor Comment 8

It indicates there is evidence for >= 1 true effect in the significant gender results. This is interesting, because apparently there is little variance in whether there is evidential value for significant and nonsignificant results, yet there are differences in how these results are interpreted (in Application 2 we did actually code this).

________

-It wasn’t clear to me why you didn’t report, in applications 2 and 3,
the percent of non-significant results that your analyses suggest are false
negatives, as you did in application 1. In application 3, I’m guessing
this is because the confidence interval around this point estimate is so
wide that the point estimate would be misleading – is this correct? Is
this also the explanation for why you didn’t report this statistic in
application 2?

## Reply to Editor Comment 9

In Applications 2 and 3 this is not possible. In Application 1 we analyze 6,951 sets of nonsignificant values (i.e., 6,951 papers), but in Applications 2 and 3 only one set of nonsignificant results.

________

I’ll end with one last general point that is more a reflection than a
suggestion for you. Please feel free to ignore it completely – I don’t
like it when editors act like they are a co-author on the paper, and this is
definitely a case where my disagreement is a matter of opinion rather than
fact, so you have no obligation whatsoever to take my advice. Instead,
consider it a sample of N = 1 of how some readers may interpret your
argument.

I found myself disagreeing with your overall conclusion that the emphasis on
false positives is “unwarranted” (abstract, p. 3). In my view, your
data do not show that false negatives are a big problem, because your data
do not speak to how non-significant results are interpreted in the papers
themselves, nor what impact they have on subsequent research (i.e., do they
deter others from pursuing the same question?). Many of the arguments that
we should pay more attention to false negatives rest on these assumptions.
Moreover, as you state yourself, the vast majority of focal tests in
published psychology papers are statistically significant, which suggests
that the negative results are likely non-focal tests. This puts more burden
on those who claim we should be paying more attention to false negatives to
demonstrate that these negative results actually have an impact on research
decisions. Moreover, it raises the possibility that researchers are not
“neglecting effects due to a lack of statistical significance”
(abstract), but neglecting them because they don’t care about them. If
they did care about those effects, they may very well have invested more
effort into getting them to reach the threshold for significance (either
through increasing sample size, reducing measurement error, or p-hacking).

## Reply to Editor Comment 10

Our wording was a bit too strong; we meant to say that there is an unbalanced emphasis on false positives (adjusted in revisions). We do think that regarding this as a problem in the published literature is too narrow; after all, the unpublished literature suffers from worse power problems most likely. However, we cannot inspect the problem of false negatives in the unpublished literature reliably (for Applications 1 and 2).

We try to show in this paper that there is a need to regard the potential of false negatives alongside (!) false positives, and provide a way to look for them. We hope that these findings will contribute to a shift away from binary decision making in one study, which has caused so many problems for the literature already.

________

In summary, the reviewer and I found much to like about your paper, and also
had suggestions for improving your manuscript. I look forward to receiving
your revision.

________

# Reviewer B

1) General comments and summary of recommendation
Describe your overall impressions and your recommendation, including changes
or revisions. Please note that you should pay attention to scientific,
methodological, and ethical soundness only, not novelty, topicality, or
scope. A checklist of things to you may want to consider is below:
 - Are the methodologies used appropriate?
 - Are any methodological weaknesses addressed?
 - Is all statistical analysis sound?
 - Does the conclusion (if present) reflect the argument, is it supported
by data/facts?
 - Is the article logically structured, succinct, and does the argument
flow coherently?
 - Are the references adequate and appropriate?:
This article attempts to estimate the proportion of False Negative (FN)
results in the published psychological literature. Overall, this is a well
written article.
A few minor comments/thoughts about the first analysis (since the methods in
the other two analyses were similar/the same).

In the first analysis, the
authors examined a very large number of non-significant results from eight
psychology journals. The results were automatically (using an R package
statcheck) extracted from over 14 thousand articles. There were multiple
results extracted per paper; in fact, it seems that on average 3.5
non-significant results per paper were extracted (Table 3). The assumption
of independence required for the application of the Fisher test (which
assumes the p-values values are uniformly distributed) is therefore
potentially violated. The authors deal with this by computing the ICC for
non-significant results, and report it to be .001, which they suggest
indicates independence of p-values within a paper. I would like to see a bit
more discussion here as to whether this test is sufficient to dismiss the
violation of the independence assumption as non-consequential in most/many
of these articles. Are there are other references that have applied the ICC
to p-values? I’m unfamiliar with this application. For instance, data on
which ICC is computed are typically normally distributed. From a more
practical standpoint, if one looked at a few articles at random, does the
assumption that the same data are not used for the non-focal test seem
reasonable? If an average number of studies per paper is 3, and each study
reports a gender analysis that comes out non-significant, I believe in the
independence of the resulting p-values. But I can imagine in many articles
other scenarios are at play and this is not the case. What would be the
impact on the analyses?

## Reply to Reviewer Comment 1

Due to the reviewer's comment, we went back to the data and inspected the ICC based on the log-odds of the transformed p-values, which are more normally distributed than the transformed p-values. The resulting ICC is 0.00002. We are unaware of any specific ICC applications based on p-values.

Anecdotally: our recollection is that in the RP:P project there was severe disagreement about experts trying to assess what the focal effects in a paper were. Additionally, how large would the articles inspected have to be to come to a reliable assessment of whether the results throughout the entire dataset are in fact independent? If only 10 papers out of 6,951 are inspected, making inferences for the entire set is still uncertain and does not provide any more certainty for the results than not manually inspecting them.

We also think that the impact of dependency is not a major problem due to the uniform distribution of p-values under H0 (independence) and the major variation in p-values that results even if H1 is true (see also Cumming's dance of the p-values to that respect).

________

The argument is that non-significant results reported in papers tend to be
non-focal, and therefore are not p-hacked. The focal results in each paper,
however, are either p-hacked or otherwise selected for significance
(publication bias). This may be a bit far fetched but I wondered about
whether selecting on main results can affect the distribution of the
non-focal results in some way. It may be an interesting thought exercise.
Related, is there any way in which publication bias/p-hacking can select for
non-significant non-focal results? For instance, perhaps some journals are
more likely to publish a “clean” set of results, where the main effects
are found but the interactions with gender etc. are not significant.

## Reply to Reviewer Comment 2

We discussed reverse p-hacking (or what we call q-hacking) as the reviewer describes. This was one of the reasons why we started Application 2. However, given the small cell sizes we were unable to actually say anything about this.

We do not feel confident to state anything about the focality of the nonsignificant results, because this requires direct interpretation and is rather unclear (see also reply above).

________

I need a clarification on the meaning of the k=1 line in Table 4. I can only
understand the test if more than one result per paper exists. Possibly I
missed something. If the results for k=1 are indeed meaningful, can these
values be related to an estimate of power to detect an average non-focal
result? (i.e., use a different denominator to get the percentage). It may
help the reader to place them in context. A comparison between average power
for non-focal effects and what we know about average power for focal effects
(e.g., Cohen) could be informative. A priori, as we expect many non-focal
effects to be small or zero (so I’m using the word “power” here more
loosely to refer to rates of non-rejection of H0), this number should be way
lower than the average power for focal effects, which is already dangerously
low in psychology, as we know.

## Reply to Reviewer Comment 3

When k=1, the Fisher method is another way of testing whether the result deviates from a null effect but with the prior information that we already know the result is nonsignificant. This gives more evidential weight to values just above alpha, given that if there is truly no effect the likelihood of them occurring is higher under H1 than H0.

________

The later rows in Table 4, as well as the average row, are a bit misleading
because it is unfair to expect a statistical test to perform
perfectly—when k>10, is it really reasonable to expect that not a single
non-significant p-value in any article would not be a false negative? It
makes it look like the problem with FNs is very bad (e.g., for JPSP, the
rate is 94% with k>20). I would caution the reader against a pessimistic
interpretation of the numbers in the high k rows, or in the average row
(which is almost too misleading to be computed).

## Reply to Reviewer Comment 4

When more nonsignificant results are reported and these are not uniformly distributed, the likelihood does increase that there is >= 1 false negative. Of course, the test itself can have meta-decision errors, but with larger k the power to detect also becomes higher. Combined with dichotomous interpretation of p-values, we consider this a realistic interpretation and not a pessimistic one. A paper reporting only significant results can be just as unbelievable as one reporting only nonsignificant results. Similarly, if (e.g.) a JPSP paper reports more than 20 nonsignificant results, it is very likely that there is a false negative (the opposite of Francis' 'too good to be true').

________

One could also ask, somewhat cynically, whether we really learn anything
from a paper that says that, on average when we examine false negative
results reported in a paper (with the average number of them being 3.5),
that at least one of them is wrong. This seems like something we know a
priori. What would be your response to this? Disclaimer: I do find the paper
worthwhile; I just wonder if the first analysis is over-stated.

## Reply to Reviewer Comment 5

We had this same feeling sometime from a theoretical perspective, but apparently this is not apparent when NHST is applied and results are interpreted dichotomously and as representative of the true effect (see Hoekstra et al, 2008). This (once again) indicates that we should not trust human understanding of probabilities to assess probabilistic processes such as inferences based on statistics, and we hope to contribute to this realization by providing these results and an easy-to-use method to analyze (nonsignificant) statistical results.

________

2) Figures/tables/data availability:
Please comment on the author’s use of tables, charts, figures, ifrelevant.
Please acknowledge that adequate underlying data is available to ensure
reproducibility (see open data policies per discipline of Collabra here).:
Yes

3) Ethical approval:
If humans or animals have been used as research subjects, and/or tissue or
field sampling, are the necessary statements of ethical approval by a
relevant authority present? Where humans have participated in research,
informed consent should also be declared.
If not, please detail where you think a further ethics
approval/statement/follow-up is required.:
Human ethics not relevant.

4) Language:
Is the text well written and jargon free? Please comment on the quality of
English and any need for improvement beyond the scope of this process.:
The article is well written. I would not call it "jargon free", and it
could be written more plainly. I'm not the best person to comment on this.

________

### 2017-01-16 submission/manuscript.Rnw
First draft review response

@@
 iccSS <- Anova(lm(dat$Computed[nsig] ~ dat$Source[nsig]), type="III")
+
+tmp <- log((dat$Computed[nsig] - .05) / (1 - .05)) / ((dat$Computed[nsig] - .05) / (1 - .05))
+
+iccSStmp <- Anova(lm(tmp ~ dat$Source[nsig]), type="III")
 
@@
   fishRes <- FisherMethod(dat$Computed, as.character(dat$Source))
+  # Uncomment below to rerun with alpha = .10
+  # fishRes <- FisherMethod(dat$Computed, as.character(dat$Source), alpha = .10)
   save(fishRes, file = sprintf('%sdata/fishRes', run))

### 2017-01-18 submission/manuscript.Rnw
Revisions for Collabra commit

@@
 The concern for false positives has overshadowed the concern for false negatives in the recent debates in psychology.
-This is unwarranted,  since  reported statistically nonsignificant findings may just be 'too good to be false'.
+This might be unwarranted,  since  reported statistically nonsignificant findings may just be 'too good to be false'.
 We examined evidence for false negatives in nonsignificant results in three different ways.
@@
 We examined evidence for false negatives in the psychology literature in three applications of the adapted Fisher method.
-These applications indicate that (i) the observed effect size distribution of nonsignificant effects exceeds the expected distribution assuming a null-effect, and approximately two out of three (66.7\%) psychology articles reporting nonsignificant results contain evidence for at least one false negative, (ii) nonsignificant results on gender effects contain evidence of true nonzero effects, and (iii) the statistically nonsignificant replications from the Reproducibility Project Psychology (RPP) do not warrant conclusions about the absence or presence of true zero effects underlying these nonsignificant results.
+These applications indicate that (i) the observed effect size distribution of nonsignificant effects exceeds the expected distribution assuming a null-effect, and approximately two out of three (66.7\%) psychology articles reporting nonsignificant results contain evidence for at least one false negative, (ii) nonsignificant results on gender effects contain evidence of true nonzero effects, and (iii) the statistically nonsignificant replications from the Reproducibility Project Psychology (RPP) do not warrant strong conclusions about the absence or presence of true zero effects underlying these nonsignificant results.
 We conclude that false negatives deserve more attention in the current debate on statistical practices in psychology.
-Neglecting effects due to a lack of statistical power can lead to a waste of research resources and stifle the scientific discovery process.
+Potentially neglecting effects due to a lack of statistical power can lead to a waste of research resources and stifle the scientific discovery process.
 \end{abstract}
 
-\keywords{nonsignificant, underpowered, effect size, Fisher test}
+\keywords{NHST, reproducibility project, nonsignificant, power, underpowered, effect size, Fisher test, gender}
 
@@
 
+Unfortunately, NHST has led to many misconceptions and misinterpretations (e.g., \cite{Goodman2008135,Bakan_1966}).
+The most serious mistake relevant to our paper is that many researchers accept the null-hypothesis and claim no effect in case of a statistically nonsignificant effect (about 60\%, see \cite{Hoekstra2006}).
+Hence, most researchers overlook that the outcome of hypothesis testing is probabilistic (if the null-hypothesis is true, or the alternative hypothesis is true and power is less than 1) and interpret outcomes of hypothesis testing as reflecting the absolute truth.
+At least partly because of mistakes like this, many researchers ignore the possibility of false negatives and false positives and they remain pervasive in the literature.
+
 Recent debate about false positives has received much attention in science and psychological science in particular.
@@
 The concern for false positives has overshadowed the concern for false negatives in the recent debate, which seems unwarranted.
-Cohen \cite{Cohen1962-jc} was the first to indicate that psychological science was (severely) underpowered, which is defined as the chance of finding a statistically significant effect in the sample lower than 50\% when there is truly an effect in the population.
+Cohen \cite{Cohen1962-jc} was the first to indicate that psychological science was (severely) underpowered, which is defined as the chance of finding a statistically significant effect in the sample being lower than 50\% when there is truly an effect in the population.
 This has not changed throughout the subsequent fifty years \cite{Bakker2012-tf,Fraley2014-xs}.
@@
 
-The research objective of the current paper is to examine evidence for false negative results in the published psychology literature.
+The research objective of the current paper is to examine evidence for false negative results in the psychology literature.
 To this end, we inspected a large number of nonsignificant results from eight flagship psychology journals.
@@
 For large effects ($\eta=.4$), two nonsignificant results from small samples already almost always detects the existence of false negatives (not shown in Table \ref{tab:tab2}).
+
+<<power, echo=FALSE, results=hide>>=
+tmp_power <- function(es, n, digits){
+  # cv
+  tCV <- qt(0.1, df=n-1,lower.tail=F)
+
+  # Step 2 - non-centrality parameter
+  f2 <- es^2/(1-es^2)
+  ncp <- f2*n
+
+  # Step 3 - power
+  power <- pt(q=tCV,df=n-1,ncp=ncp, lower.tail=F)
+
+  cbind(es,n,tCV,ncp,power)
+
+  return(round(power, digits))
+}
+@
+
+To put the power of the Fisher test into perspective, we can compare its power to reject the null based on one statistically nonsignificant result ($k=1$) with the power of a regular $t$-test to reject the null.
+If $\eta=.1$, the power of a regular $t$-test equals \Sexpr{tmp_power(.1, 33, 3)}, \Sexpr{tmp_power(.1, 62, 3)}, \Sexpr{tmp_power(.1, 119, 3)} for sample sizes of 33, 62, 119, respectively; if $\eta$ = .25, power values equal \Sexpr{tmp_power(.25, 33, 3)}, \Sexpr{tmp_power(.25, 62, 3)}, \Sexpr{tmp_power(.25, 119, 3)} for these sample sizes.
+The power values of the regular $t$-test are higher than that of the Fisher test, because the Fisher test does not make use of the more informative statistically significant findings.
 
@@
 Second, we investigate how many research articles report nonsignificant results and how many of those show evidence for at least one false negative using the Fisher test \cite{Fisher1925-jl}.
+Note that this application only investigates the evidence of false negatives in articles, not how authors might interpret these findings (i.e., we do not assume all these nonsignificant results are interpreted as evidence for the null).
 
@@
 
-tmp <- log((dat$Computed[nsig] - .05) / (1 - .05)) / ((dat$Computed[nsig] - .05) / (1 - .05))
-
-iccSStmp <- Anova(lm(tmp ~ dat$Source[nsig]), type="III")
+pstar <- ((dat$Computed[nsig & !(dat$Computed == 1)] - .05) / (1 - .05))
+
+tmp <- log(pstar / (1 - pstar))
+
+iccSStmp <- Anova(lm(tmp ~ dat$Source[nsig & !(dat$Computed == 1)]), type="III")
 
@@
 This procedure was repeated 163,785 times, which is three times the number of observed nonsignificant test results (54,595).
-The collection of simulated results approximates the expected effect size distribution under $H_0$, assuming independence of test results.
+The collection of simulated results approximates the expected effect size distribution under $H_0$, assuming independence of test results in the same paper.
 We inspected this possible dependency with the intra-class correlation ($ICC$), where $ICC=1$ indicates full dependency and $ICC=0$ indicates full independence.
-For the set of observed results, the ICC for nonsignificant $p$-values was \Sexpr{round(iccSS$Sum[2]/(iccSS$Sum[3]+iccSS$Sum[2]), 3)}, indicating independence of $p$-values within a paper.
+For the set of observed results, the ICC for nonsignificant $p$-values was \Sexpr{round(iccSS$Sum[2]/(iccSS$Sum[3]+iccSS$Sum[2]), 3)}, indicating independence of $p$-values within a paper (the ICC of the log odds transformed $p$-values was similar, with $ICC=\Sexpr{round(iccSStmp$Sum[2]/(iccSStmp$Sum[3]+iccSStmp$Sum[2]), 5)}$ after excluding $p$-values equal to 1 for computational reasons).
 The resulting, expected effect size distribution was compared to the observed effect size distribution (i) across all journals and (ii) per journal.
@@
 
-Because effect sizes and their distribution typically overestimate population effect size, particularly when sample size is small \cite{Voelkle2007-at,Hedges1981-og}, we also compared the observed and expected adjusted nonsignificant effect sizes that correct for such overestimation of effect sizes (right panel of Figure \ref{fig:fig3}; see Appendix B).
-The distribution of adjusted effect sizes of nonsignificant results tells the same story; observed effect sizes are larger than expected effect sizes.
+Because effect sizes and their distribution typically overestimate population effect size $\eta^2$, particularly when sample size is small \cite{Voelkle2007-at,Hedges1981-og}, we also compared the observed and expected adjusted nonsignificant effect sizes that correct for such overestimation of effect sizes (right panel of Figure \ref{fig:fig3}; see Appendix B).
+Such overestimation affects all effects in a model, both focal and non-focal.
+The distribution of adjusted effect sizes of nonsignificant results tells the same story as the unadjusted effect sizes; observed effect sizes are larger than expected effect sizes.
 For instance, the distribution of adjusted reported effect size suggests 49\% of effect sizes are at least small, whereas under the $H_0$ only 22\% is expected.
@@
 The first row indicates the number of papers that report no nonsignificant results.
+When $k=1$, the Fisher test is simply another way of testing whether the result deviates from a null effect, conditional on the result being statistically nonsignificant.
 Overall results (last row) indicate that 47.1\% of all articles show evidence of false negatives (i.e.
@@
 Of articles reporting at least one nonsignificant result, 66.7\% show evidence of false negatives, which is much more than the 10\% predicted by chance alone.
+Results did not substantially differ if nonsignificance is determined based on $\alpha=.10$ (the analyses can be rerun with any set of $p$-values larger than a certain value based on the code provided on OSF; \url{https://osf.io/qpfnw}).
 
@@
 Consequently, we observe that journals with articles containing a higher number of nonsignificant results, such as JPSP, have a higher proportion of articles with evidence of false negatives.
-This is the result of higher power of the Fisher method when there are more nonsignificant results.
+This is the result of higher power of the Fisher method when there are more nonsignificant results and does not necessarily reflect that a nonsignificant $p$-value in e.g.
+JPSP has a higher probability of being a false negative than one in another journal.
 
@@
 Interestingly, the proportion of articles with evidence for false negatives decreased from \Sexpr{round(mydf$y[1]*100, 0)}\% in 1985 to \Sexpr{round(mydf$y[29]*100, 0)}\% in 2013, despite the increase in mean $k$ (from \Sexpr{round(mydf$count[1], 2)} in 1985 to \Sexpr{round(mydf$count[29], 2)} in 2013).
-This decreasing proportion of papers with evidence over time cannot be explained by a decrease in sample size over time, as sample size in psychology articles has stayed stable across time (see Figure \ref{fig:fig5}).
+This decreasing proportion of papers with evidence over time cannot be explained by a decrease in sample size over time, as sample size in psychology articles has stayed stable across time (see Figure \ref{fig:fig5}; degrees of freedom is a direct proxy of sample size resulting from the sample size minus the number of parameters in the model).
 One (at least partial) explanation of this surprising result is that in the early days researchers primarily reported fewer APA results and used to report relatively more APA results with 'marginally significant' $p$-values (i.e., $p$-values slightly larger than .05), compared to nowadays.
@@
 We do not know whether these marginally significant $p$-values were interpreted as evidence in favor of a finding (or not) and how these interpretations changed over time.
-Another potential explanation is that the effect sizes being studied have become smaller over time (mean effect $r$ \Sexpr{round(mean(sqrt(dat$esComp[dat$Reported.Comparison == '=' & dat$years.y.
+Another potential explanation is that the effect sizes being studied have become smaller over time (mean correlation effect $r=$ \Sexpr{round(mean(sqrt(dat$esComp[dat$Reported.Comparison == '=' & dat$years.y.
 == 1985 & dat$Reported.P.Value > .05])), 3)} in 1985, \Sexpr{round(mean(sqrt(dat$esComp[dat$Reported.Comparison == '=' & dat$years.y.
@@
 We apply the Fisher test to significant and nonsignificant gender results to test for evidential value \cite{Van_Assen2015-gg,Simonsohn2014-dm}.
-More precisely, we investigate whether evidential value depends on whether the result is statistically significant or not, and whether the results were in line with expectations expressed in the paper, or not.
+More precisely, we investigate whether evidential value depends on whether or not the result is statistically significant, and whether or not the results were in line with expectations expressed in the paper.
 
@@
 Out of the 100 replicated studies in the RPP, 64 did not yield a statistically significant effect size, despite the fact that high replication power was one of the aims of the project \cite{Open_Science_Collaboration2015-zs}.
-Regardless, the authors suggest "\textit{… that at least one replication could be a false negative}" (p.
+Regardless, the authors suggested "\textit{… that at least one replication could be a false negative}" (p.
 aac4716-4).
@@
 
-The reanalysis of the nonsignificant RPP results using the Fisher method demonstrates that any conclusions on the validity of individual effects based on "failed" replications, as determined by statistical significance, is unwarranted and irresponsible.
+The reanalysis of the nonsignificant RPP results using the Fisher method demonstrates that any conclusions on the validity of individual effects based on "failed" replications, as determined by statistical significance, is unwarranted.
 This was also noted by both the original RPP team \cite{Open_Science_Collaboration2015-zs,Anderson2016-bv} and in a critique of the RPP \cite{Gilbert2016-mi}.
@@
 
+Very recently four statistical papers have re-analyzed the RPP results to either estimate the frequency of studies testing true zero hypotheses or to estimate the individual effects examined in the original and replication study.
+All four papers account for the possibility of publication bias in the original study.
+Johnson, Payne, Wang, Asher, and Mandal \cite{doi:10.1080/01621459.2016.1240079} estimated a Bayesian statistical model including a distribution of effect sizes among studies for which the null-hypothesis is false.
+On the basis of their analyses they conclude that at least 90\% of psychology experiments tested negligible true effects.
+Johnson et al.'s model as well as our Fisher's test are not useful for estimation and testing of individual effects examined in original and replication study.
+Interpreting results of individual effects should take the precision of the estimate of both the original and replication into account \cite{Cumming2014-fi}.
+Etz and Vandekerckhove \cite{10.1371/journal.pone.0149794} reanalyzed the RPP at the level of individual effects, using Bayesian models incorporating publication bias.
+They concluded that 64\% of individual studies did not provide strong evidence for either the null or the alternative hypothesis in either the original of the replication study.
+This agrees with our own and Maxwell's \cite{Maxwell2015-yb} interpretation of the RPP findings.
+As opposed to Etz and Vandekerckhove \cite{10.1371/journal.pone.0149794}, Van Aert and Van Assen \cite{rpp-hybrid,rpp-bayes} use a statistically significant original and a replication study to evaluate the common true underlying effect size, adjusting for publication bias.
+From their Bayesian analysis \cite{rpp-bayes} assuming equally likely zero, small, medium, large true effects, they conclude that only 13.4\% of individual effects contain substantial evidence (Bayes factor > 3) of a true zero effect.
+For a staggering 62.7\% of individual effects no substantial evidence in favor zero, small, medium, or large true effect size was obtained.
+All in all, conclusions of our analyses using the Fisher are in line with other statistical papers re-analyzing the RPP data (with the exception of Johnson et al.) suggesting that studies in psychology are typically not powerful enough to distinguish zero from nonzero true findings.
+
 \section*{General discussion}
@@
 Much attention has been paid to false positive results in recent years.
-Our study demonstrates the importance of focusing on false negatives as well.
+Our study demonstrates the importance of paying attention to false negatives alongside false positives.
 We examined evidence for false negatives in nonsignificant results in three different ways.
-To this end, we adapted the Fisher method to detect the presence of at least one false negative in a set of statistically nonsignificant results.
+Specifically, we adapted the Fisher method to detect the presence of at least one false negative in a set of statistically nonsignificant results.
 Simulations indicated the adapted Fisher test to be a powerful method for that purpose.
-The three applications indicated that (i) approximately two out of three psychology articles reporting nonsignificant results contain evidence for at least one false negative, (ii) nonsignificant results on gender effects contain evidence of true nonzero effects, and (iii) the statistically nonsignificant replications from the Reproducibility Project Psychology (RPP) do not warrant conclusions about the absence or presence of true zero effects underlying these nonsignificant results (RPP does yield less biased estimates of the effect; the original studies severely overestimated the effects of interest).
+The three applications indicated that (i) approximately two out of three psychology articles reporting nonsignificant results contain evidence for at least one false negative, (ii) nonsignificant results on gender effects contain evidence of true nonzero effects, and (iii) the statistically nonsignificant replications from the Reproducibility Project Psychology (RPP) do not warrant strong conclusions about the absence or presence of true zero effects underlying these nonsignificant results (RPP does yield less biased estimates of the effect; the original studies severely overestimated the effects of interest).
 
@@
 Previous concern about power \cite{Cohen1962-jc,Sedlmeier1989-yc,Bakker2012-tf,Marszalek2011-rf}, which was even addressed by an APA Statistical Task Force in 1999 that recommended increased statistical power \cite{Wilkinson_APA_Task_Force_on_Statistical_Inference1999-ht}, seems not to have resulted in actual change \cite{Marszalek2011-rf}.
-Potential explanations for this lack of change is that researchers overestimate statistical power when designing a study for small effects \cite{Bakker2016-nj} and can act strategically by running multiple underpowered studies rather than one large powerful study \cite{Bakker2012-tf}.
+Potential explanations for this lack of change is that researchers overestimate statistical power when designing a study for small effects \cite{Bakker2016-nj}, use $p$-hacking to artificially increase statistical power, and can act strategically by running multiple underpowered studies rather than one large powerful study \cite{Bakker2012-tf}.
+The effects of $p$-hacking are likely to be the most pervasive, with many people admitting to using such behaviors at some point \cite{John2012-uj} and publication bias pushing researchers to find statistically significant results.
+As such, the problems of false positives, publication bias, and false negatives are intertwined and mutually reinforcing.
 
@@
 In a precision mode, the large study provides a more certain estimate and therefore is deemed more informative and provides the best estimate.
-Using meta-analyses to combine estimates obtained in studies on the same effect may further increase the overall estimate’s precision.
+Using meta-analyses to combine estimates obtained in studies on the same effect may further increase the overall estimate's precision.
 Although the emphasis on precision and the meta-analytic approach is fruitful in theory, we should realize that publication bias will result in precise but biased (overestimated) effect size estimation of meta-analyses \cite{Nuijten2015-kh}.
@@
 Finally, the Fisher test may and is also used to meta-analyze effect sizes of different studies.
-Whereas Fisher used his method to test the null-hypothesis of an underlying true zero effect using several studies’ $p$-values, the method has recently been extended to yield unbiased effect estimates using only statistically significant $p$-values.
+Whereas Fisher used his method to test the null-hypothesis of an underlying true zero effect using several studies' $p$-values, the method has recently been extended to yield unbiased effect estimates using only statistically significant $p$-values.
 The principle of uniformly distributed $p$-values given the true effect size on which the Fisher method is based, also underlies newly developed methods of meta-analysis that adjust for publication bias, such as $p$-uniform \cite{Van_Assen2015-gg} and $p$-curve \cite{Simonsohn2014-dm}.

### 2017-01-18 submission/manuscript.Rnw
Update ZENODO DOI

@@
 \section*{Author note}
-All research files, data, and analyses scripts are preserved and made available for download at \url{http://doi.org/10.5281/zenodo.154514}.
+All research files, data, and analyses scripts are preserved and made available for download at \url{http://doi.org/10.5281/zenodo.250492}.
 \newpage

### 2017-01-18 submission/manuscript.tex
Update ZENODO DOI

@@
 We examined evidence for false negatives in the psychology literature in three applications of the adapted Fisher method.
-These applications indicate that (i) the observed effect size distribution of nonsignificant effects exceeds the expected distribution assuming a null-effect, and approximately two out of three (66.7\%) psychology articles reporting nonsignificant results contain evidence for at least one false negative, (ii) nonsignificant results on gender effects contain evidence of true nonzero effects, and (iii) the statistically nonsignificant replications from the Reproducibility Project Psychology (RPP) do not warrant conclusions about the absence or presence of true zero effects underlying these nonsignificant results.
+These applications indicate that (i) the observed effect size distribution of nonsignificant effects exceeds the expected distribution assuming a null-effect, and approximately two out of three (66.7\%) psychology articles reporting nonsignificant results contain evidence for at least one false negative, (ii) nonsignificant results on gender effects contain evidence of true nonzero effects, and (iii) the statistically nonsignificant replications from the Reproducibility Project Psychology (RPP) do not warrant strong conclusions about the absence or presence of true zero effects underlying these nonsignificant results.
 We conclude that false negatives deserve more attention in the current debate on statistical practices in psychology.
-Neglecting effects due to a lack of statistical power can lead to a waste of research resources and stifle the scientific discovery process.
+Potentially neglecting effects due to a lack of statistical power can lead to a waste of research resources and stifle the scientific discovery process.
 \end{abstract}
 
-\keywords{nonsignificant, underpowered, effect size, Fisher test}
+\keywords{NHST, reproducibility project, nonsignificant, power, underpowered, effect size, Fisher test, gender}
 
 \section*{Author note}
-All research files, data, and analyses scripts are preserved and made available for download at \url{http://doi.org/10.5281/zenodo.154514}.
+All research files, data, and analyses scripts are preserved and made available for download at \url{http://doi.org/10.5281/zenodo.250492}.
 \newpage
@@
 
+To put the power of the Fisher test into perspective, we can compare its power to reject the null based on one statistically nonsignificant result ($k=1$) with the power of a regular $t$-test to reject the null.
+If $\eta=.1$, the power of a regular $t$-test equals 0.17, 0.255, 0.467 for sample sizes of 33, 62, 119, respectively; if $\eta$ = .25, power values equal 0.813, 0.998, 1 for these sample sizes.
+The power values of the regular $t$-test are higher than that of the Fisher test, because the Fisher test does not make use of the more informative statistically significant findings.
+
 % IF YOU WANT TO RERUN SIMULATIONS, SEE CODE CHUNK "SIMULATIONS" IN APPLICATION 1
@@
 This procedure was repeated 163,785 times, which is three times the number of observed nonsignificant test results (54,595).
-The collection of simulated results approximates the expected effect size distribution under $H_0$, assuming independence of test results.
+The collection of simulated results approximates the expected effect size distribution under $H_0$, assuming independence of test results in the same paper.
 We inspected this possible dependency with the intra-class correlation ($ICC$), where $ICC=1$ indicates full dependency and $ICC=0$ indicates full independence.
-For the set of observed results, the ICC for nonsignificant $p$-values was 0.001, indicating independence of $p$-values within a paper.
+For the set of observed results, the ICC for nonsignificant $p$-values was 0.001, indicating independence of $p$-values within a paper (the ICC of the log odds transformed $p$-values was similar, with $ICC=0.00175$ after excluding $p$-values equal to 1 for computational reasons).
 The resulting, expected effect size distribution was compared to the observed effect size distribution (i) across all journals and (ii) per journal.
@@
 Interestingly, the proportion of articles with evidence for false negatives decreased from 77\% in 1985 to 55\% in 2013, despite the increase in mean $k$ (from 2.11 in 1985 to 4.52 in 2013).
-This decreasing proportion of papers with evidence over time cannot be explained by a decrease in sample size over time, as sample size in psychology articles has stayed stable across time (see Figure \ref{fig:fig5}).
+This decreasing proportion of papers with evidence over time cannot be explained by a decrease in sample size over time, as sample size in psychology articles has stayed stable across time (see Figure \ref{fig:fig5}; degrees of freedom is a direct proxy of sample size resulting from the sample size minus the number of parameters in the model).
 One (at least partial) explanation of this surprising result is that in the early days researchers primarily reported fewer APA results and used to report relatively more APA results with 'marginally significant' $p$-values (i.e., $p$-values slightly larger than .05), compared to nowadays.
@@
 We do not know whether these marginally significant $p$-values were interpreted as evidence in favor of a finding (or not) and how these interpretations changed over time.
-Another potential explanation is that the effect sizes being studied have become smaller over time (mean effect $r$ 0.257 in 1985, 0.187 in 2013), which results in both higher $p$-values over time and lower power of the Fisher test.
+Another potential explanation is that the effect sizes being studied have become smaller over time (mean correlation effect $r=$ 0.257 in 1985, 0.187 in 2013), which results in both higher $p$-values over time and lower power of the Fisher test.
 Using the data at hand, we cannot distinguish between the two explanations.
